### 2014-04-05 Paper/main.tex
Initial latex file for the main research paper

\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Achieving high quality self recovery images using a high capacity embedding algorihm}

\author{HJ Kolver}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Abstract of this paper and what I plan to write in it
\end{abstract}

\section{Introduction}

\section{Current self embedding and recovery schemes and algorithms}

This section compares current Content reconstruction algorithms using self embedding.
This serves to give an overview of what is currently available and to possibly highlight shortcommings of the current algorithms.
This would be usefull to determine if the proposed method does indeed improve on existing methods. 
It would also help highlight strenghts and shortcommings in the proposed method.

\subsection{Overview}

\end{document}

### 2014-04-05 Paper/main.tex
Bibliography and Embedding comparison update
Updated the references. Updated the comparison of image recovery
algorithms by adding another algorithm

@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage[T1]{fontenc}
 
-\title{Achieving high quality self recovery images using a high capacity embedding algorihm}
+\title{High quality content reconstruction in images using a high capacity self-embedding algorihm}
 
-\author{HJ Kolver}
+\author{Hendrik J Kolver}
 
@@
 
+The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content recostruction problem.
+The method uses LSB embedding to embed the refernce data into the image itself.
+The method also uses a global spreading technique to spead the reference data across the image.
+They also propose that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after recovery.
+
+\hspace{0pt} \\
+The method proposed in \cite {korus2013efficient} achieves good quality cover images with a PSNR \textgreater 35dB. 
+The method also achives an image recovery quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with taper rates of 50\% and 33\% respectively.
+The method does not let the restoration quality of the image deteriorate much if the tampering rate is increased up to a value of 50\%.
+They do however note that they can only achieve minimal reconstruction performace increases by decreasing the amount of information in the reconstruction reference.
+By using only 50\% of the available capacity the maximal tampering rate increases form 50\% to 59\%.
+
+\hspace{0pt} \\
+This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered wiht before recovery starts to deteriorate.
+The security for this method is also very good since the quality of the cover image is not very suceptible to visual checks.
+The authors did not do any statistical analysis on the image.
+The embedding capacity of this method is also acceptable, but because the method uses some of the authentic image data to aid in the recovery the quality of the image, before and after recovery, is still very good even without a very high embedding capacity.
+
+\hspace{0pt} \\
+\cite {tian2003high} Proposed a method that is really quite interesting
+
+\bibliography{main}
+\bibliographystyle{plain}
+
 \end{document}

### 2014-04-05 Paper/main.tex
Short analysis of another content restoration method

@@
 \usepackage[T1]{fontenc}
+\usepackage[margin=0.5in]{geometry}
 
@@
 \begin{abstract}
-Abstract of this paper and what I plan to write in it
+
+\noindent Abstract of this paper and what I plan to write in it.
+This will explain the whole bit about there being a tradeoff in content recovery and self embedding and that I will attempt to make that tradeoff smaller by trying to apply a well researched high capacity embedding algorithm to this problem etc.
+
 \end{abstract}
@@
 \section{Introduction}
+A short introduction into the wonderfull world of fragile watermarking, self embedding and image recovery. Attempt to make this interesting...
+It whould also probably be beneficial to mention how the paper will be structured. 
+That I will first research the current self embedding and content recovery methods. 
+Then mention that I will also research the high capacity embedding algorithms and evaluate their aplicability to my current problem. 
+I will then start with my experiment and all the things that will contain. 
+I will finally analyse my findings and draw conclusions based on my research and my experimental findings. 
+This will involve evaluating if the proposed mehtod does indeed increase quality and wasn't just a waste of time. 
+Although that would tecnically be a finding as well.
 
@@
 \hspace{0pt} \\
-\cite {tian2003high} Proposed a method that is really quite interesting
+\cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
+The method uses these two techniques in combination to achieve a high embedding capacity while keeping destortion relatively low.
+The method achieves a PSNR \textgreater 35dB after embedding.
+The method achieves a embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit greyscale version of the Lena image.
+
+\hspace{0pt} \\
+The method's restoration quality is acceptable at roughly 50\%. 
+The difference expansion this method uses provides extra space for embedding.
+The authors did thus not impliment compression on the image data because of the extra space the differece expansion provides.
+The embedding capacity of this method could thus be further improved by compressing the embedded data.
+This could possibly lead to better quality than what their experimental results achieved at the expense of complexity.
+
+The authors do not mention the image tamper rate that this method allows.
 

### 2014-04-07 Paper/main.tex
Spelling errors & gitignore

--- 2014-04-05 Paper/main.tex
@@
-\documentclass[a4paper]{article}
+\documentclass[11pt]{article}
 
@@
 \usepackage[T1]{fontenc}
+\usepackage[margin=0.5in]{geometry}
 
-\title{High quality content reconstruction in images using a high capacity self-embedding algorihm}
+\title{High quality content reconstruction in images using a high capacity self-embedding algorithm}
 
@@
 \begin{abstract}
-Abstract of this paper and what I plan to write in it
+
+\noindent Abstract of this paper and what I plan to write in it.
+This will explain the whole bit about there being a trade off in content recovery and self embedding and that I will attempt to make that trade off smaller by trying to apply a well researched high capacity embedding algorithm to this problem etc.
+
 \end{abstract}
@@
 \section{Introduction}
+A short introduction into the wonderful world of fragile watermarking, self embedding and image recovery. Attempt to make this interesting...
+It would also probably be beneficial to mention how the paper will be structured. 
+That I will first research the current self embedding and content recovery methods. 
+Then mention that I will also research the high capacity embedding algorithms and evaluate their applicability to my current problem. 
+I will then start with my experiment and all the things that will contain. 
+I will finally analyze my findings and draw conclusions based on my research and my experimental findings. 
+This will involve evaluating if the proposed method does indeed increase quality and wasn't just a waste of time. 
+Although that would technically be a finding as well.
 
@@
 This section compares current Content reconstruction algorithms using self embedding.
-This serves to give an overview of what is currently available and to possibly highlight shortcommings of the current algorithms.
-This would be usefull to determine if the proposed method does indeed improve on existing methods. 
-It would also help highlight strenghts and shortcommings in the proposed method.
+This serves to give an overview of what is currently available and to possibly highlight shortcomings of the current algorithms.
+This would be useful to determine if the proposed method does indeed improve on existing methods. 
+It would also help highlight strengths and shortcomings in the proposed method.
 
@@
 
-The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content recostruction problem.
-The method uses LSB embedding to embed the refernce data into the image itself.
-The method also uses a global spreading technique to spead the reference data across the image.
+The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
+The method uses LSB embedding to embed the reference data into the image itself.
+The method also uses a global spreading technique to spread the reference data across the image.
 They also propose that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after recovery.
@@
 The method proposed in \cite {korus2013efficient} achieves good quality cover images with a PSNR \textgreater 35dB. 
-The method also achives an image recovery quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with taper rates of 50\% and 33\% respectively.
+The method also achieves an image recovery quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with taper rates of 50\% and 33\% respectively.
 The method does not let the restoration quality of the image deteriorate much if the tampering rate is increased up to a value of 50\%.
-They do however note that they can only achieve minimal reconstruction performace increases by decreasing the amount of information in the reconstruction reference.
+They do however note that they can only achieve minimal reconstruction performance increases by decreasing the amount of information in the reconstruction reference.
 By using only 50\% of the available capacity the maximal tampering rate increases form 50\% to 59\%.
@@
 \hspace{0pt} \\
-This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered wiht before recovery starts to deteriorate.
-The security for this method is also very good since the quality of the cover image is not very suceptible to visual checks.
+This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered with before recovery starts to deteriorate.
+The security for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
 The authors did not do any statistical analysis on the image.
@@
 \hspace{0pt} \\
-\cite {tian2003high} Proposed a method that is really quite interesting
+\cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
+The method uses these two techniques in combination to achieve a high embedding capacity while keeping distortion relatively low.
+The method achieves a PSNR \textgreater 35dB after embedding.
+The method achieves an embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
+
+\hspace{0pt} \\
+The method's restoration quality is acceptable at roughly 50\%. 
+The difference expansion this method uses provides extra space for embedding.
+The authors did thus not implement compression on the image data because of the extra space the difference expansion provides.
+The embedding capacity of this method could thus be further improved by compressing the embedded data.
+This could possibly lead to better quality than what their experimental results achieved at the expense of complexity.
+
+The authors do not mention the image tamper rate that this method allows.
 

### 2014-04-07 Paper/main.tex
Added difference expansion description
Added a description for difference expansion as well as a research paper
on it. I have also updated my research .txt file and added another paper
on reversible watermarks that I still need to read

@@
 \cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
+Difference expansion works by exploiting the high redundancy that are present in images.
+With difference expansion the payload is embedded in the difference of pixel values. 
+For a pair of pixel values (x,y). \cite {tian2002reversible}
+It should however be noted that image quality reduces rapidly as the payload size is increased when using difference expansion. 
 The method uses these two techniques in combination to achieve a high embedding capacity while keeping distortion relatively low.

### 2014-04-21 Paper/main.tex
Current method overview update

@@
 \usepackage[T1]{fontenc}
-\usepackage[margin=0.5in]{geometry}
+\usepackage[margin=1.0in]{geometry}
 
@@
 
+\tableofcontents
+
 \section{Introduction}
@@
 It would also help highlight strengths and shortcomings in the proposed method.
+The methods analyzed were chosen because they all provide good quality cover and reconstructed images.
+They also each offer an unique approach or aspect to the image recovery problem and would thus provide a good idea of the different approaches that have already been tested.
 
@@
 
+\subsubsection{Erasure channel model utilizing the remaining authentic content}
+\label{ErasureChannelOverview}
 The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
@@
 
-\hspace{0pt} \\
+\subsubsection{Method using difference expansion}
+\label{differenceExpansionOverview}
 \cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
@@
 \hspace{0pt} \\
-The method's restoration quality is acceptable at roughly 50\%. 
+The method's \cite {tian2003high} restoration quality is acceptable at roughly 50\%. 
 The difference expansion this method uses provides extra space for embedding.
@@
 This could possibly lead to better quality than what their experimental results achieved at the expense of complexity.
+Difference expansion thus seems a good solution to increase the embedding capacity while still keeping the distortion low.
 
-The authors do not mention the image tamper rate that this method allows.
+\hspace{0pt} \\ 
+The authors do not mention the image tamper rate that this method \cite {tian2003high} allows.
+
+\subsubsection{Dynamic block allocation for self embedding}
+\label{DynamicBlockOverview}
+(Qian et al) \cite{qian2011image} proposes a method for fragile watermarking with good restoration capabilities using self embedding.
+The proposed method differs from the other methods mention in \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} due to the fact that the proposed method does not embed the information into all blocks uniformly.
+The proposed method classifies different blocks of the image according to the block smoothness.
+The less smooth the block is the more information will be embedded into it.
+The authors argue that the current methods that use a fixed embedding size for each block are inadequate since less information should be embedded into the very smooth blocks and more should be embedded into the rough blocks \cite{qian2011image}.
+
+\hspace{0pt} \\
+The advantage of using this dynamic scheme is that there would be less visual distortion to the cover image. 
+This is because if the specific block is already very rough (very busy visually) the human eye would not notice small changes.
+If however the specific block is very smooth (very uniform visually) the human eye is more likely to notice small changes.
+The proposed method thus creates less distortion in the cover image than fixed size methods while still retaining good restoration quality \cite{qian2011image}.
+
+\hspace{0pt} \\
+The method proposed by (Qian et al) \cite{qian2011image} uses the 3 LSB bit planes to embed the needed information in.
+The method achieves good results in experimentation with a cover image PSNR \textgreater 37dB as well as a reconstructed image PSNR = 35dB.
+The method also allows for a tamper rate \textless 35\%.
+The authors do not analyze the security of the algorithm.
+
+\subsection{Comparison}
+Each of the methods described in \ref{DynamicBlockOverview}, \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} provide good quality cover images as well as good quality reconstructed images.
+There are however important differences.
+The method described in \ref{ErasureChannelOverview} offers a very good tamper rate of 50\% compared to the method described in \ref{DynamicBlockOverview} which has a tamper rate of 35\%.
+This means that a larger of the cove image can be tampered with while still being able to restore the image with good quality.
+
+\hspace{0pt} \\
+The method described in \ref{differenceExpansionOverview} achieves a cover image with a PSNR \textgreater 35dB, the method described in \ref{ErasureChannelOverview} achieves similar results, however the method described in \ref{DynamicBlockOverview} achieves a cover image PSNR \textgreater 37dB.
+This means that the method described in \ref{DynamicBlockOverview} would have less noise in the cover images after embedding and would thus have better overall quality of the cover images.
+
+\hspace{0pt} \\
+At almost equal tamper rates of around 33\%-35\% the method described in \ref{ErasureChannelOverview} achieves a restoration PSNR \textgreater 40dB whereas the method described in \ref{DynamicBlockOverview} only achieves a restoration PSNR = 35dB.
+The method described in \ref{differenceExpansionOverview} only achieves a restoration quality of about 50\% the original image.
+This means that the method described in \ref{ErasureChannelOverview} would generally produce better quality restored images than the methods described in \ref{DynamicBlockOverview} and \ref{differenceExpansionOverview}.
+
+\hspace{0pt} \\
+This means that the method described in \ref{ErasureChannelOverview} provides the best tamper rate and the best restored image quality, and the method described in \ref{DynamicBlockOverview} provides the best cover image quality.
+The method described in \ref{differenceExpansionOverview} provides decent quality of the cover image as well as the restored image.
+
+\hspace{0pt} \\
+All three methods thus provide good results and would serve as a good benchmark for comparing the method described later in this paper.
 

### 2014-04-22 Paper/main.tex
Intro sections and some content

@@
 \section{Introduction}
-A short introduction into the wonderful world of fragile watermarking, self embedding and image recovery. Attempt to make this interesting...
-It would also probably be beneficial to mention how the paper will be structured. 
-That I will first research the current self embedding and content recovery methods. 
-Then mention that I will also research the high capacity embedding algorithms and evaluate their applicability to my current problem. 
-I will then start with my experiment and all the things that will contain. 
-I will finally analyze my findings and draw conclusions based on my research and my experimental findings. 
-This will involve evaluating if the proposed method does indeed increase quality and wasn't just a waste of time. 
-Although that would technically be a finding as well.
+This section gives a brief description of the concepts used in this report.
+The reasoning behind the proposed method will also be explained in \ref{introQualityIncrease} and \ref{introHighCap}.
+This will serve to to show the applicability of the proposed method as well as the shortcomings it attempts to address.
+
+\subsection{Overview}
+Self recovering images (described in \ref{introSelfEmbedRecovery}) poses an interesting problem.
+There is an inherent trade-off (described in \ref{introQualityTrade}) between the quality of the image after embedding and the quality of the image after recovery.
+This report proposes a method in which a high capacity embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.
+
+\subsection{Steganography}
+\label{introSteganography}
+Steganography is the process of hiding information in such a way that it does not get detected \cite{johnson1998exploring}.
+Steganography, derived from Greek means "covered writing".
+This means it differs from cryptography which does not attempt to hide information but merely scrambles it so it cannot be understood.
+Steganography does not scramble the information but rather relies on the information to remain hidden.
+
+\subsection{Fragile Watermarking}
+\label{introFragWatermarking}
+
+\subsection{Self embedding and recovery}
+\label{introSelfEmbedRecovery}
+
+\subsection{Quality Trade-off}
+\label{introQualityTrade}
+
+\subsubsection{Increasing quality with capacity}
+\label{introQualityIncrease}
+
+\subsubsection{High capacity embedding algorithms}
+\label{introHighCap}
 

### 2014-04-26 Paper/main.tex
completed introduction section

@@
 
-\noindent Abstract of this paper and what I plan to write in it.
-This will explain the whole bit about there being a trade off in content recovery and self embedding and that I will attempt to make that trade off smaller by trying to apply a well researched high capacity embedding algorithm to this problem etc.
+\noindent Abstract of this paper and what I wrote in it.
+This will give the reader a short overview of what they can expect to find in this paper.
 
@@
 \label{introFragWatermarking}
+Fragile watermarking is a variation of traditional watermarking where a watermark is embedded into an image such that subsequent alterations to the watermarked image can be detected with high probability \cite{lin1999review}.
+This means that if modifications are made to the watermarked image it would be possible to detect that modifications were made as well as what parts of the image were modified.
+This is a necessary component in self recovering images because in order to be able to recover image data it first needs to be determined what data needs to be recovered.
+It thus needs to be know what data was modified.
+A fragile watermark is used for this purpose.
 
@@
 \label{introSelfEmbedRecovery}
+Self embedding is a scheme where image content is embedded into the image itself.
+This embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself \cite{fridrich1999images}.
+A self embedding and recovery scheme such as the proposed method contains a couple of high level steps.
+Firstly the authentic image content is embedded into the original image along with a fragile watermark.
+This watermark will help determine later on which parts of the image was modified if any (see \ref{introFragWatermarking}).
+When the authentic image needs to be recovered, after modification, the fragile watermark is used to determine which content was modified.
+An attempt is then made to extract the original content for the areas that were modified from the modified image.
+If this process is successful the user is left with a high quality reconstruction of the original image.
 
@@
 \label{introQualityTrade}
+There is an inherent quality trade-off present within self embedding schemes.
+The trade-off exists between the image after embedding and the image after recovery.
+If an embedding algorith such as LSB(Least significan bit) embedding is used (as in \ref{ErasureChannelOverview}) the actual bit values of the original image are overwritten.
+Naturally the more bit values are overwritten the more noise is introduced into the image.
+This effectively reduces the quality of the image after embedding.
+
+\hspace{0pt} \\
+The solution to this would be to simply embed a small amount of information into the image to keep the noise low.
+However this presents another problem.
+The quality of the image after recovery is dependent on the amount of authentic image data embedded into the image.
+
+\hspace{0pt} \\
+To achieve maximum quality after embedding the embedded information must be as little as possible.
+To achieve maximum quality after recover the embedded information must be as large as possible to be as close as possible to the original image.
+There exists then a trade-off between the two.
 
@@
 \label{introQualityIncrease}
+It might be possible to increase the quality of the image after recovery while still keeping the quality after embedding high.
+It is proposed that applying an embedding algorithm designed for high capacity while retaining quality (as discussed in \ref{introHighCap}) to the problem of self embedding could possibly increase the quality of the image after embedding as well as after recovery.
+This is because such an algorithm should provide higher embedding capacity while producing less noise in the image.
 
@@
 \label{introHighCap}
+The proposed method in this paper attempts to apply the algorithm for BPCS Steganography \cite{beaullieubpcs} to the problem of self recovering images, specifically to increase overall quality.
+
+\hspace{0pt} \\
+The goal of the BPCS algorithm is to embed as much data as possible into a cover image without detection \cite{beaullieubpcs}.
+This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this paper.
+The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding (similar to \ref{DynamicBlockOverview}).
+BPCS steg differs however in the fact that the blocks can be conjugated in a checker board pattern to increase complexity and decrease detectability if needs be.
+
+\hspace{0pt} \\
+The BPCS algorithm can achieve a very high capacity while still remaining undetectable through human perception.
+This makes the BPCS algorithm a possible good choice to increase the capacity of a self recovering image scheme and possible increase the quality through this process.
 

### 2014-07-10 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java
Added the changeable bits to the watermark embedding
Changeable bit can now be used to embed the watermark location map. need
to look into the compression of the bit stream

@@ -1,7 +1,6 @@
 package embedding;
 
-import static extraction.Extract.couldThisbeOutOfBounds;
-import static extraction.Extract.ultimateEmbeddingCheck;
+
 import java.awt.Color;
 import java.awt.List;
 import java.awt.image.BufferedImage;
@@ -21,7 +20,7 @@ public class SelfEmbed {
     private static int cornerRow =0;
     private static int cornerCol=0;
     //0.636
-    private static final double embeddingRate = 0.9;
+    private static final double embeddingRate = 0.65;
     
     public static MyImage selfEmbed(MyImage image) throws IOException, NoSuchAlgorithmException{
         ArrayList<Block> blockList = getBlocks(image);
@@ -71,9 +70,10 @@ public class SelfEmbed {
             
             //get hash for block
             blockBinaryHash = ShaHashHelper.getBlockHash(blockContentString);
-            
+            int[][][] biLevelLocationMap = new int[3][8][8];
+            String changableBitString ="";
             int binaryCount = 0;
-            //embed hash into block
+            //embed hash into block and get changable bits and location map
             for (int i = rowCorner; i < rowCorner+8; i++) {
                 for (int j = colCorner; j < colCorner+8; j+=2){
                     int redLeft = imageGrid[i][j].getRed();
@@ -84,26 +84,107 @@ public class SelfEmbed {
                     int greenRight = imageGrid[i][j+1].getGreen();
                     int blueRight = imageGrid[i][j+1].getBlue();
                     
+                    
                     //System.out.println("["+redLeft+","+redRight+"]");
                     WatermarkHelper newRed = embedFragileWatermark(redLeft,redRight,blockBinaryHash.charAt(binaryCount));
-                    if(newRed.isEmbedded)
+                    if(newRed.isEmbedded){
+                        biLevelLocationMap[0][(i-rowCorner)][(j-colCorner)] = 1;
+                        biLevelLocationMap[0][(i-rowCorner)][(j-colCorner)+1] = 1;
                         binaryCount++;
+                    }else{
+                        biLevelLocationMap[0][(i-rowCorner)][(j-colCorner)] = 0;
+                        biLevelLocationMap[0][(i-rowCorner)][(j-colCorner)+1] = 0; 
+                    }
                     
                     WatermarkHelper newGreen = embedFragileWatermark(greenLeft,greenRight,blockBinaryHash.charAt(binaryCount));
[…]

### 2014-07-10 Experiments/HonoursResearchApplication/src/embedding/WatermarkHelper.java

@@ -15,4 +15,5 @@ public class WatermarkHelper {
     public int num2 =0;
     public int embeddedBit = 0;
     public boolean isEmbedded = false;
+    public boolean confusion = false;
 }

### 2014-07-10 Experiments/HonoursResearchApplication/src/extraction/Extract.java

@@ -2,11 +2,12 @@ package extraction;
 
 import embedding.Block;
 import embedding.SelfEmbed;
-import static embedding.SelfEmbed.getBinary;
+import static embedding.SelfEmbed.*;
 import static embedding.SelfEmbed.getBinary;
 import embedding.ShaHashHelper;
 import embedding.WatermarkHelper;
 import java.awt.Color;
+import java.io.FileNotFoundException;
 import java.io.IOException;
 import java.security.NoSuchAlgorithmException;
 import java.util.ArrayList;
@@ -37,11 +38,13 @@ public class Extract {
     
     public static Color[][] removeWaterMarkFromImage(Color[][] imageGrid) throws NoSuchAlgorithmException, IOException{
         String blockBinaryHash ="";
+        int confusionCount = 0;
+        int notAuthenticCount = 0;
         //calculate hash for each 8x8 block
         int rowCorner = 0;
         int colCorner = 0;
         while(rowCorner <512 && colCorner <512){
-
+            ArrayList<WatermarkHelper> helperList = new ArrayList<>();
             String blockContentString = "";
             String extractedWatermark = "";
 
@@ -69,12 +72,21 @@ public class Extract {
                     if(newBlue.isEmbedded)
                         extractedWatermark += ""+newBlue.embeddedBit; 
                     
+                    if (newRed.confusion)
+                        confusionCount++;
+                    if (newGreen.confusion)
+                        confusionCount++;
+                    if (newBlue.confusion)
+                        confusionCount++;
                     //restoring the image
                     Color newFirstColor = new Color(newRed.num1,newGreen.num1,newBlue.num1);
                     imageGrid[i][j] =newFirstColor;
                     Color newSecondColor = new Color(newRed.num2,newGreen.num2,newBlue.num2);
                     imageGrid[i][j+1] =newSecondColor;
                     
+                    helperList.add(newRed);
+                    helperList.add(newGreen);
+                    helperList.add(newBlue);
                 }  
             }
             
@@ -88,18 +100,17 @@ public class Extract {
             }
             
             //get hash for block
-            
+            boolean blockNotAuthentic = false;
             blockBinaryHash = ShaHashHelper.getBlockHash(blockContentString);
-            //System.out.println("1: "+ blockBinaryHash);
-           // System.out.println("2: "+ extractedWatermark);
+
[…]

### 2014-07-10 Experiments/HonoursResearchApplication/src/honoursresearchapplication/HonoursResearchApplication.java

@@ -22,7 +22,7 @@ public class HonoursResearchApplication {
        
        SelfEmbed.selfEmbed(holder.getImage());
        System.out.println("Exiting After Successfull execution: "+ ((System.currentTimeMillis()-start)/1000.0)+"s");
-       Extract.ExtractImage("finalImage.bmp");
+       //Extract.ExtractImage("finalImage.bmp");
     }
     
 }

### 2014-07-11 Paper/main.tex
Many changes
Either I have to find a way to get really good compression on bit
streams or I need to find a new way to authenticate image blocks.

@@
 
+\section{Implementation}
+\label{Implementation}
+
+\subsection{Embedding}
+
+\subsubsection{BPCS Steg}
+In order to be able to recover the image after it has been tampered with the image needs to be embedded into itself. 
+For this embedding the proposed method used BPCS Steganography \cite{beaullieubpcs}.
+\hspace{0pt} \\
+//TODO explain algorithm briefly
+
+\hspace{0pt} \\
+BPCS Steg has an inherent property that if any part of the image is modified the embedded message will be lost.
+This would obviously be a problem for the proposed method since the image will definitely be modified.
+
+\hspace{0pt} \\
+As a solution to this problem each block used for embedding is treated as a separate embedding entity.
+The is thus not overlap between two different blocks used for embedding.
+With the compression method used (\ref{ImageCompression}) this means that effectively 7 pixels are embedded in each embedding block.
+Along with these 7 pixels the location of the first pixel is also embedded using two integers.
+This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
+
+\hspace{0pt} \\
+Total space available for embedding per block = (8*8)*3 = 64*3 = 192
+\hspace{0pt} \\
+Total embedded bits = (7*24) + (2*9) = 186
+
+\hspace{0pt} \\
+This means that there is an excess of 6 bits per block that are not used for embedding. This is effectively means there are 6 bits of embedding space being wasted with each block.
+This is caused by the need to be able to identify blocks even after the image has been modified.
+
+\paragraph{Image Compression}
+\label{ImageCompression}
+The image that is embedded into the cover image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
+Compression however is not the focus of this study.
+The embedded image is thus just a resized version of the original image.
+A higher quality reconstruction could be achieved if a better compression algorithm is used.
+
+\paragraph{Block Spread}
+//TODO
+\hspace{0pt} \\
+It is very important how the embedded content is spread across the image because this affects the tamper rate
+\hspace{0pt} \\
+//put reference here
+\hspace{0pt} \\
+And explain further
+
+\subsubsection{Fragile Watermark}
+In order to be able to detect which parts of the image have been tampered with a fragile watermark can be used.
+
+\hspace{0pt} \\
+An initial attempt was made to apply the method proposed in \cite{tian2002wavelet}.
+This method is a reversible fragile watermark which means that the watermark can be removed to restore the original content bit by bit before watermarking if the image was found to be authentic.
+
+\hspace{0pt} \\
+The method needed to be adapted to authenticate the image on a block level, the image is divided into 8x8 blocks.
+The method requires compression of bit streams in order to embed the watermark and to be able to extract the watermark again.
+The bit streams are rather small in the proposed method because they are only applicable to a specific 8x8 pixel block.
+This results in the fact that there is not always enough redundancy to be able to compress the bit streams enough for embedding.
+
+\hspace{0pt} \\
+Another problem with this method was the large amount of noise that this method of watermarking introduces into the cover image since it also uses difference expansion as mentioned in \cite{tian2002reversible}.
+
 \bibliography{main}

### 2014-07-11 Experiments/HonoursResearchApplication/src/embedding/Compression.java

@@ -1,0 +1,15 @@
+package embedding;
+
+/**
+ *
+ * @author Hendrik
+ */
+public class Compression {
+    public static String compress(String text){
+       return RLE(text); 
+    }
+    
+    public static String RLE(String text){
+        return text;
+    }
+}

### 2014-07-11 Experiments/HonoursResearchApplication/src/embedding/FragileWatermark.java

@@ -1,0 +1,183 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+package embedding;
+
+import static embedding.SelfEmbed.embedFragileWatermark;
+import static embedding.SelfEmbed.getBinary;
+import static embedding.SelfEmbed.getChangableBits;
+import static embedding.SelfEmbed.getChangableBitsCount;
+import static embedding.SelfEmbed.getDifference;
+import static embedding.SelfEmbed.getNewValuePair;
+import static embedding.SelfEmbed.getStringForLocationMap;
+import java.awt.Color;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.security.NoSuchAlgorithmException;
+
+/**
+ *
+ * @author Hendrik
+ */
+public class FragileWatermark {
+     public static Color[][] embedWaterMark(Color[][] imageGrid) throws NoSuchAlgorithmException, IOException{
+         return WavletBased(imageGrid);
+     }
+     
+     public static Color[][] WavletBased(Color[][] imageGrid) throws FileNotFoundException, NoSuchAlgorithmException{
+         String blockBinaryHash;
+        //calculate hash for each 8x8 block
+        int rowCorner = 0;
+        int colCorner = 0;
+        while(rowCorner <512 && colCorner <512){
+
+            String blockContentString = "";
+
+            
+            //get hash for block
+            for (int i = rowCorner; i < rowCorner+8; i++) {
+                for (int j = colCorner; j < colCorner+8; j++){
+                    blockContentString+= imageGrid[i][j].getRed();
+                    blockContentString+= imageGrid[i][j].getGreen();
+                    blockContentString+= imageGrid[i][j].getBlue();
+                } 
+            }
+            
+            //get hash for block
+            blockBinaryHash = ShaHashHelper.getBlockHash(blockContentString);
+            int[][][] biLevelLocationMap = new int[3][8][8];
+            String changableBitString ="";
+            int binaryCount = 0;
+            //embed hash into block and get changable bits and location map
+            for (int i = rowCorner; i < rowCorner+8; i++) {
+                for (int j = colCorner; j < colCorner+8; j+=2){
+                    int redLeft = imageGrid[i][j].getRed();
+                    int greenLeft = imageGrid[i][j].getGreen();
+                    int blueLeft = imageGrid[i][j].getBlue();
+                    
[…]

### 2014-07-11 Experiments/HonoursResearchApplication/src/embedding/ImageContentExtractionAndCompression.java

@@ -58,8 +58,8 @@ public class ImageContentExtractionAndCompression {
                     binary = "";
                     //binary += binaryImageSize;
                     
-                    binary += "0"+getBinary(i,9);
-                    binary += "1"+getBinary(j,9);
+                    binary += getBinary(i,9);
+                    binary += getBinary(j,9);
                 }
                     
                 Color pixelColor = new Color(scaledBuf.getRGB(i, j));

### 2014-07-11 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java

@@ -43,161 +43,22 @@ public class SelfEmbed {
         ArrayList<Block> messageBlocks = ImageContentExtractionAndCompression.getCompressedImageContent(image, embeddingCapacity);
         ArrayList<Block> embeddedImageList = embedMessage(blockList,messageBlocks);
         Color[][] reAssembleImageColours = reAssembleImage(embeddedImageList);
-        Color[][] imageColors = embedWaterMark(reAssembleImageColours);
-        saveImageFromColor(imageColors,"finalImage.bmp");
+        //Color[][] imageColors = FragileWatermark.embedWaterMark(reAssembleImageColours);
+        //saveImageFromColor(imageColors,"finalImage.bmp");
         
         return null;
     }
     
-    public static Color[][] embedWaterMark(Color[][] imageGrid) throws NoSuchAlgorithmException, IOException{
-        String blockBinaryHash;
-        //calculate hash for each 8x8 block
-        int rowCorner = 0;
-        int colCorner = 0;
-        while(rowCorner <512 && colCorner <512){
-
-            String blockContentString = "";
-
-            
-            //get hash for block
-            for (int i = rowCorner; i < rowCorner+8; i++) {
-                for (int j = colCorner; j < colCorner+8; j++){
-                    blockContentString+= imageGrid[i][j].getRed();
-                    blockContentString+= imageGrid[i][j].getGreen();
-                    blockContentString+= imageGrid[i][j].getBlue();
-                } 
+    public static String getStringForLocationMap(int[][][] locationMap){
+        String locationMapString = "";
+        for (int i = 0; i < 8; i++) {
+            for (int j = 0; j < 8; j++) {
+                locationMapString  += locationMap[0][i][j];
+                locationMapString  += locationMap[1][i][j];
+                locationMapString  += locationMap[2][i][j];
             }
-            
-            //get hash for block
-            blockBinaryHash = ShaHashHelper.getBlockHash(blockContentString);
-            int[][][] biLevelLocationMap = new int[3][8][8];
-            String changableBitString ="";
-            int binaryCount = 0;
-            //embed hash into block and get changable bits and location map
-            for (int i = rowCorner; i < rowCorner+8; i++) {
-                for (int j = colCorner; j < colCorner+8; j+=2){
-                    int redLeft = imageGrid[i][j].getRed();
-                    int greenLeft = imageGrid[i][j].getGreen();
-                    int blueLeft = imageGrid[i][j].getBlue();
-                    
-                    int redRight = imageGrid[i][j+1].getRed();
[…]

### 2014-07-11 Experiments/HonoursResearchApplication/src/extraction/Extract.java

@@ -25,8 +25,40 @@ public class Extract {
         
         //blocks of image
         ArrayList<Block> blocks = SelfEmbed.getBlocks(holder.getImage());
-        extractWatermark(holder.getImage());
+        checkAllBlockAuthenticity(blocks);
+        //extractWatermark(holder.getImage());
         
+    }
+    
+    public static void checkAllBlockAuthenticity(ArrayList<Block> blocks) throws FileNotFoundException, NoSuchAlgorithmException{
+        for(Block block: blocks){
+            if(checkBlockAuthenticity(block)){
+                System.out.println("dammit"); 
+            }else
+            {
+                //System.out.println("whoo");
+            }
+        }
+    }
+    
+    public static boolean checkBlockAuthenticity(Block block) throws FileNotFoundException, NoSuchAlgorithmException{
+        char[][][] blockBits = block.getBlock();
+        String blockBinary = "";
+        for (int i = 0; i < 8; i++) {
+            for (int j = 0; j < 8; j++) {
+                blockBinary+= blockBits[0][i][j];
+                blockBinary+= blockBits[1][i][j];
+                blockBinary+= blockBits[2][i][j];
+            }  
+        }
+        
+        String testHash = blockBinary.substring(blockBinary.length()-30,blockBinary.length());
+        blockBinary = blockBinary.substring(0,blockBinary.length()-30);
+        
+        String calculatedHash = ShaHashHelper.getBlockHash(blockBinary);
+        calculatedHash = calculatedHash.substring(0,30);
+        
+        return calculatedHash.equals(testHash);
     }
     
     //

### 2014-07-11 Experiments/HonoursResearchApplication/src/honoursresearchapplication/HonoursResearchApplication.java

@@ -22,7 +22,7 @@ public class HonoursResearchApplication {
        
        SelfEmbed.selfEmbed(holder.getImage());
        System.out.println("Exiting After Successfull execution: "+ ((System.currentTimeMillis()-start)/1000.0)+"s");
-       //Extract.ExtractImage("finalImage.bmp");
+       Extract.ExtractImage("reAssembledAndSavedImageBeforeWatermark.bmp");
     }
     
 }

### 2014-07-11 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java
Not embedding into lsb layer
I will attempt next to embed the block hash into the lsb layer of the
block  for authentication purposes. Thorough testing will need to be
done to see the impact this has

@@ -27,7 +27,7 @@ public class SelfEmbed {
         int suitableBlockCount = 0;
         int lsbPlane = 0;
         for(Block block : blockList){
-            if(block.getComplexity()>embeddingRate){
+            if(block.getComplexity()>embeddingRate && block.lsbLayer !=7){
                 suitableBlockCount++;
             }
         }
@@ -88,7 +88,7 @@ public class SelfEmbed {
         //remember the message is not in grey code
         int messageBlockCount =0;
         for (int i = 0; i < imageBlocks.size(); i++) {
-            if(imageBlocks.get(i).getComplexity()>embeddingRate){
+            if(imageBlocks.get(i).getComplexity()>embeddingRate  && imageBlocks.get(i).lsbLayer !=7){
                 Block imageBlock = imageBlocks.get(i);
                 Block messageBlock = messageBlocks.get(messageBlockCount);
                 if(messageBlock.getComplexity()<embeddingRate){

### 2014-07-14 Experiments/HonoursResearchApplication/src/embedding/Block.java
embedded watermark, started extraction
Embedded the fragile watermark into the image, can extract the pixel
locations from the recovered blocks. Need to conjugate since there are
now false negatives

@@ -10,6 +10,7 @@ public class Block {
     private double complexity = 0;
     public int lsbLayer = 0;
     public boolean message = false;
+    public boolean authentic = true;
 
     public Block() {
         this.block = new char[3][blockSize][blockSize];

### 2014-07-14 Experiments/HonoursResearchApplication/src/embedding/FragileWatermark.java

@@ -8,6 +8,7 @@ package embedding;
 
 import static embedding.SelfEmbed.embedFragileWatermark;
 import static embedding.SelfEmbed.getBinary;
+import static embedding.SelfEmbed.getBinary;
 import static embedding.SelfEmbed.getChangableBits;
 import static embedding.SelfEmbed.getChangableBitsCount;
 import static embedding.SelfEmbed.getDifference;
@@ -17,12 +18,62 @@ import java.awt.Color;
 import java.io.FileNotFoundException;
 import java.io.IOException;
 import java.security.NoSuchAlgorithmException;
+import java.util.ArrayList;
 
 /**
  *
  * @author Hendrik
  */
 public class FragileWatermark {
+    public static ArrayList<Block> embedWaterMark(ArrayList<Block> imageBlocks) throws NoSuchAlgorithmException, IOException{
+        return embedWaterMarkInLSBLayer(imageBlocks);
+    }
+    
+    public static ArrayList<Block> embedWaterMarkInLSBLayer(ArrayList<Block> imageBlocks) throws NoSuchAlgorithmException, IOException{
+        String blockBinary = "";
+        ArrayList<Block> newBlocks = new ArrayList();
+        for(Block block: imageBlocks){
+            if(block.lsbLayer!=7){
+                blockBinary+=getBlockBinary(block);
+                newBlocks.add(block);
+            }
+            else{
+                //192 = 8x8x3
+                String hashString = ShaHashHelper.getBlockHash(blockBinary,192);
+                char[][][] newLsbContent;
+                newLsbContent = block.getBlock();
+                int hashBitCounter = 0;
+                for (int i = 0; i < 8; i++) {
+                    for (int j = 0; j < 8; j++) {
+                        newLsbContent[0][i][j] = hashString.charAt(hashBitCounter);
+                        hashBitCounter++;
+                        newLsbContent[1][i][j] = hashString.charAt(hashBitCounter);
+                        hashBitCounter++;
+                        newLsbContent[2][i][j] = hashString.charAt(hashBitCounter);
+                        hashBitCounter++;
+                    }
+                }
+                block.setBlock(newLsbContent);
+                newBlocks.add(block);
+                blockBinary="";
+            }
+        }
+
+        return newBlocks;
+    }
+    
+    public static String getBlockBinary(Block block){
+        String blockBinary = "";
+        for (int i = 0; i < 8; i++) {
+            for (int j = 0; j < 8; j++) {
[…]

### 2014-07-14 Experiments/HonoursResearchApplication/src/embedding/ImageContentExtractionAndCompression.java

@@ -48,16 +48,21 @@ public class ImageContentExtractionAndCompression {
         for (int i = 0; i < scaledBuf.getHeight(); i++) {
             for (int j = 0; j < scaledBuf.getWidth(); j++) {
                 //7 is used because that is the amount of pixels that will be stored per block
-                if(perBlockCheck%7==0)
+                if(perBlockCheck==7)
                 {
                     //System.out.println("binarysize:" + binary.length());
                     if(perBlockCheck!=0 && !binary.equals("")){
-                        blockList.add(makeBlock(binary));
+//                        System.out.println("binary: "+ binary);
+//                        System.out.println("ImediateBinary: "+ FragileWatermark.getBlockBinary(makeBlockRGBTogether(binary)));
+                        Block tmpBlock = makeBlockRGBTogether(binary);
+                        tmpBlock.calculateComplexity();
+                        blockList.add(tmpBlock);
+                        
                     }
                     perBlockCheck = 0;
                     binary = "";
                     //binary += binaryImageSize;
-                    
+                    //System.out.println(getBinary(i,9)+" \\ "+getBinary(j,9));
                     binary += getBinary(i,9);
                     binary += getBinary(j,9);
                 }
@@ -75,27 +80,58 @@ public class ImageContentExtractionAndCompression {
         }
         scaledBuf = getScaledImage(scaledBuf,512,512);
         ImageIO.write(scaledBuf, "BMP", new File("scaledBlockNew.bmp"));
+        
         return blockList;
         
         //System.out.println("MessageBlocks: "+blockList.size());
 //        scaledBuf = getScaledImage(scaledBuf,512,512);
 //        System.out.println(ImageIO.write(bufImage, "BMP", new File("originalBlock.bmp")));
 //        ImageIO.write(scaledBuf, "BMP", new File("scaledBlock.bmp"));
-        
-        
-        
-        
+
     }
     
+    public static Block makeBlockRGBTogether(String binary){
+        char[][][] grid = new char[3][8][8];
+        int binaryCount = 0;
+        Block block = new Block();
+        for (int i = 0; i < 8; i++) {
+            for (int j = 0; j < 8; j++) {
+                if(binaryCount>=binary.length()){
+                    grid[0][i][j] = '0'; 
+                }else{
+                    grid[0][i][j] = binary.charAt(binaryCount);
+                    binaryCount++;
+                }
+                if(binaryCount>=binary.length()){
+                    grid[1][i][j] = '0'; 
[…]

### 2014-07-14 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java

@@ -20,7 +20,7 @@ public class SelfEmbed {
     private static int cornerRow =0;
     private static int cornerCol=0;
     //0.636
-    private static final double embeddingRate = 0.65;
+    public static final double embeddingRate = 0.65;
     
     public static MyImage selfEmbed(MyImage image) throws IOException, NoSuchAlgorithmException{
         ArrayList<Block> blockList = getBlocks(image);
@@ -83,7 +83,7 @@ public class SelfEmbed {
         return calculateValuesUsingNewDifference(num1,num2,newH);
     }
     
-    public static ArrayList<Block> embedMessage(ArrayList<Block> imageBlocks,ArrayList<Block> messageBlocks){
+    public static ArrayList<Block> embedMessage(ArrayList<Block> imageBlocks,ArrayList<Block> messageBlocks) throws NoSuchAlgorithmException, IOException{
         //TODO
         //remember the message is not in grey code
         int messageBlockCount =0;
@@ -97,11 +97,14 @@ public class SelfEmbed {
                 }
                 messageBlock.lsbLayer = imageBlock.lsbLayer;
                 imageBlocks.set(i, messageBlock);
+                //System.out.println(FragileWatermark.getBlockBinary(imageBlocks.get(i)));
                 messageBlockCount++;
             }
             if(messageBlockCount==messageBlocks.size())
                 break;
         }
+        //embed the fragile watermark
+        FragileWatermark.embedWaterMark(imageBlocks);
         return imageBlocks;
     }
          
@@ -172,7 +175,7 @@ public class SelfEmbed {
                 
             }
         }
-        saveImageFromColor(imageColors,"reAssembledAndSavedImageBeforeWatermark.bmp");
+        saveImageFromColor(imageColors,"finalImage.bmp");
         return imageColors;
     }
     

### 2014-07-14 Experiments/HonoursResearchApplication/src/embedding/ShaHashHelper.java

@@ -14,7 +14,7 @@ import java.util.ArrayList;
  * @author Hendrik
  */
 public class ShaHashHelper {
-    public static String getBlockHash(String binaryString) throws FileNotFoundException, NoSuchAlgorithmException
+    public static String getBlockHash(String binaryString, int size) throws FileNotFoundException, NoSuchAlgorithmException
     {
         MessageDigest md = MessageDigest.getInstance("SHA-256");
 
@@ -23,7 +23,7 @@ public class ShaHashHelper {
         md.update(array, 0, array.length);
         
         String binaryStringFinal = toBinary(md.digest());
-        binaryStringFinal = binaryStringFinal.substring(0,96);
+        binaryStringFinal = binaryStringFinal.substring(0,size);
         return  binaryStringFinal;
     }
     

### 2014-07-14 Experiments/HonoursResearchApplication/src/extraction/ColorHelperObject.java

@@ -1,0 +1,13 @@
+package extraction;
+
+import java.awt.Color;
+
+/**
+ *
+ * @author Hendrik
+ */
+public class ColorHelperObject {
+    public static Color pixelColor;
+    public static int row =0;
+    public static int col = 0;
+}

### 2014-07-14 Experiments/HonoursResearchApplication/src/extraction/Extract.java

@@ -1,6 +1,7 @@
 package extraction;
 
 import embedding.Block;
+import static embedding.FragileWatermark.getBlockBinary;
 import embedding.SelfEmbed;
 import static embedding.SelfEmbed.*;
 import static embedding.SelfEmbed.getBinary;
@@ -25,18 +26,51 @@ public class Extract {
         
         //blocks of image
         ArrayList<Block> blocks = SelfEmbed.getBlocks(holder.getImage());
-        checkAllBlockAuthenticity(blocks);
+        extractImageContent(blocks);
         //extractWatermark(holder.getImage());
         
     }
     
-    public static void checkAllBlockAuthenticity(ArrayList<Block> blocks) throws FileNotFoundException, NoSuchAlgorithmException{
+    public static void extractImageContent(ArrayList<Block> blocks) throws FileNotFoundException, NoSuchAlgorithmException{
+        String blockBinary = "";
+        for(int x=0 ; x<blocks.size();x++){
+            Block block = blocks.get(x);
+            if(block.lsbLayer!=7){
+                blockBinary+=getBlockBinary(block);
+            }
+            else{
+                //192 = 8x8x3
+                String hashString = ShaHashHelper.getBlockHash(blockBinary,192);
+                String extractedHash = getBlockBinary(block);
+                if(!hashString.equals(extractedHash)){
+                    block.authentic = false;
+                    for (int i = 1; i <= 7; i++) {
+                        Block tempBlock = blocks.get(x-i);
+                        tempBlock.authentic = false;
+                        blocks.set(x-i, tempBlock);
+                        
+                    }
+                    System.out.println("Tampered");
+                }
+                blockBinary="";
+            }
+            block.calculateComplexity();
+        }
+       Color[][] reconColor = new Color[512][512];
         for(Block block: blocks){
-            if(checkBlockAuthenticity(block)){
-                System.out.println("dammit"); 
-            }else
-            {
-                //System.out.println("whoo");
+            if(block.getComplexity()>SelfEmbed.embeddingRate && block.authentic && block.lsbLayer!=7){
+//                System.out.println("block lsb: "+ block.lsbLayer);
+                String blockBinaryString = getBlockBinary(block);
+                if(blockBinaryString.substring(blockBinaryString.length()-6, blockBinaryString.length()).equals("000000")){
+                    
+                
+                    String indexRowBinary = blockBinaryString.substring(0,9);
[…]

### 2014-07-14 Experiments/HonoursResearchApplication/src/honoursresearchapplication/HonoursResearchApplication.java

@@ -12,9 +12,6 @@ import loadImage.ImageHolder;
  */
 public class HonoursResearchApplication {
 
-    /**
-     * @param args the command line arguments
-     */
     public static void main(String[] args) throws IOException, NoSuchAlgorithmException {
        long start = System.currentTimeMillis();
        ImageHolder holder = new ImageHolder();
@@ -22,7 +19,7 @@ public class HonoursResearchApplication {
        
        SelfEmbed.selfEmbed(holder.getImage());
        System.out.println("Exiting After Successfull execution: "+ ((System.currentTimeMillis()-start)/1000.0)+"s");
-       Extract.ExtractImage("reAssembledAndSavedImageBeforeWatermark.bmp");
+       Extract.ExtractImage("tamperImage.bmp");
     }
     
 }

### 2014-07-15 Experiments/HonoursResearchApplication/src/embedding/Block.java
Basic image restoration complete

@@ -11,6 +11,8 @@ public class Block {
     public int lsbLayer = 0;
     public boolean message = false;
     public boolean authentic = true;
+    public boolean conjugated = false;
+    public boolean isComplex = false;
 
     public Block() {
         this.block = new char[3][blockSize][blockSize];

### 2014-07-15 Experiments/HonoursResearchApplication/src/embedding/FragileWatermark.java

@@ -31,15 +31,22 @@ public class FragileWatermark {
     
     public static ArrayList<Block> embedWaterMarkInLSBLayer(ArrayList<Block> imageBlocks) throws NoSuchAlgorithmException, IOException{
         String blockBinary = "";
+        String conjugationMap = "";
         ArrayList<Block> newBlocks = new ArrayList();
         for(Block block: imageBlocks){
             if(block.lsbLayer!=7){
                 blockBinary+=getBlockBinary(block);
                 newBlocks.add(block);
+                if(block.conjugated)
+                    conjugationMap+='1';
+                else
+                    conjugationMap+='0';
             }
             else{
                 //192 = 8x8x3
-                String hashString = ShaHashHelper.getBlockHash(blockBinary,192);
+
+                String hashString = ShaHashHelper.getBlockHash(blockBinary,185);
+                hashString += conjugationMap;
                 char[][][] newLsbContent;
                 newLsbContent = block.getBlock();
                 int hashBitCounter = 0;
@@ -51,8 +58,11 @@ public class FragileWatermark {
                         hashBitCounter++;
                         newLsbContent[2][i][j] = hashString.charAt(hashBitCounter);
                         hashBitCounter++;
+                        
                     }
                 }
+                
+                conjugationMap="";
                 block.setBlock(newLsbContent);
                 newBlocks.add(block);
                 blockBinary="";

### 2014-07-15 Experiments/HonoursResearchApplication/src/embedding/ImageContentExtractionAndCompression.java

@@ -29,7 +29,7 @@ public class ImageContentExtractionAndCompression {
         int newWidth = (int) Math.sqrt(newPixelAmount);
         
         System.out.println("New Width: "+ newWidth);
-        
+        SelfEmbed.imageWidth = newWidth;
         
         BufferedImage bufImage = new BufferedImage(512, 512,
                     BufferedImage.TYPE_INT_RGB);

### 2014-07-15 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java

@@ -1,6 +1,7 @@
 package embedding;
 
 
+import static embedding.FragileWatermark.getBlockBinary;
 import java.awt.Color;
 import java.awt.List;
 import java.awt.image.BufferedImage;
@@ -8,6 +9,8 @@ import java.io.File;
 import java.io.IOException;
 import java.security.NoSuchAlgorithmException;
 import java.util.ArrayList;
+import java.util.Collections;
+import java.util.Random;
 import javax.imageio.ImageIO;
 import static loadImage.ImageHolder.encodeGray;
 import loadImage.MyImage;
@@ -19,6 +22,7 @@ import loadImage.MyImage;
 public class SelfEmbed {
     private static int cornerRow =0;
     private static int cornerCol=0;
+    public static int imageWidth = 0;
     //0.636
     public static final double embeddingRate = 0.65;
     
@@ -42,11 +46,17 @@ public class SelfEmbed {
         System.out.println("Available embedding capacity (bits): "+embeddingCapacity );
         ArrayList<Block> messageBlocks = ImageContentExtractionAndCompression.getCompressedImageContent(image, embeddingCapacity);
         ArrayList<Block> embeddedImageList = embedMessage(blockList,messageBlocks);
-        Color[][] reAssembleImageColours = reAssembleImage(embeddedImageList);
+        Color[][] reAssembleImageColours = reAssembleImage(embeddedImageList,"finalImage.bmp");
         //Color[][] imageColors = FragileWatermark.embedWaterMark(reAssembleImageColours);
         //saveImageFromColor(imageColors,"finalImage.bmp");
         
         return null;
+    }
+    
+    public static ArrayList<Block> shuffelList(ArrayList<Block>  blockList){
+        long seed = System.nanoTime();
+        Collections.shuffle(blockList, new Random(seed));
+        return blockList;
     }
     
     public static String getStringForLocationMap(int[][][] locationMap){
@@ -93,8 +103,17 @@ public class SelfEmbed {
                 Block messageBlock = messageBlocks.get(messageBlockCount);
                 if(messageBlock.getComplexity()<embeddingRate){
                     //TODO should conjugate here and save record of this in conjugation map
-                   // messageBlock = conjugateBlock(messageBlock);
+                    //System.out.println("messageBlock binary before: "+getBlockBinary(messageBlock));
+                    messageBlock = conjugateBlock(messageBlock);
+                    //System.out.println("messageBlock binary after: "+getBlockBinary(messageBlock));
+                    messageBlock.conjugated = true;
[…]

### 2014-07-15 Experiments/HonoursResearchApplication/src/extraction/Extract.java

@@ -2,16 +2,20 @@ package extraction;
 
 import embedding.Block;
 import static embedding.FragileWatermark.getBlockBinary;
+import static embedding.ImageContentExtractionAndCompression.getScaledImage;
 import embedding.SelfEmbed;
 import static embedding.SelfEmbed.*;
 import static embedding.SelfEmbed.getBinary;
 import embedding.ShaHashHelper;
 import embedding.WatermarkHelper;
 import java.awt.Color;
+import java.awt.image.BufferedImage;
+import java.io.File;
 import java.io.FileNotFoundException;
 import java.io.IOException;
 import java.security.NoSuchAlgorithmException;
 import java.util.ArrayList;
+import javax.imageio.ImageIO;
 import loadImage.ImageHolder;
 import loadImage.MyImage;
 
@@ -31,7 +35,7 @@ public class Extract {
         
     }
     
-    public static void extractImageContent(ArrayList<Block> blocks) throws FileNotFoundException, NoSuchAlgorithmException{
+    public static void extractImageContent(ArrayList<Block> blocks) throws FileNotFoundException, NoSuchAlgorithmException, IOException{
         String blockBinary = "";
         for(int x=0 ; x<blocks.size();x++){
             Block block = blocks.get(x);
@@ -40,8 +44,12 @@ public class Extract {
             }
             else{
                 //192 = 8x8x3
-                String hashString = ShaHashHelper.getBlockHash(blockBinary,192);
+                String hashString = ShaHashHelper.getBlockHash(blockBinary,185);
                 String extractedHash = getBlockBinary(block);
+                extractedHash = extractedHash.substring(0,extractedHash.length()-7);
+                
+                String blockConjugationMap = getBlockBinary(block);
+                blockConjugationMap = blockConjugationMap.substring(blockConjugationMap.length()-7,blockConjugationMap.length());
                 if(!hashString.equals(extractedHash)){
                     block.authentic = false;
                     for (int i = 1; i <= 7; i++) {
@@ -51,28 +59,105 @@ public class Extract {
                         
                     }
                     System.out.println("Tampered");
+                }else{
+                    //block is authentic check if there was conjugation
+                    int charCount = 6;
+                    
+                    for (int i = 1; i <= 7; i++) {
+                        
+                        if(blockConjugationMap.charAt(charCount)=='1'){
+                            //block has been conjugated
+                            Block tempBlock = blocks.get(x-i);
[…]

### 2014-07-15 Experiments/HonoursResearchApplication/src/honoursresearchapplication/HonoursResearchApplication.java

@@ -19,7 +19,7 @@ public class HonoursResearchApplication {
        
        SelfEmbed.selfEmbed(holder.getImage());
        System.out.println("Exiting After Successfull execution: "+ ((System.currentTimeMillis()-start)/1000.0)+"s");
-       Extract.ExtractImage("tamperImage.bmp");
+       Extract.ExtractImage("tamper.bmp");
     }
     
 }

### 2014-07-15 Experiments/HonoursResearchApplication/src/loadImage/ImageHolder.java

@@ -21,6 +21,11 @@ public class ImageHolder {
         //extract the normal image colours
         File img = new File(path);
         BufferedImage bufferedImage = ImageIO.read(img);
+        extractData(bufferedImage);
+        
+    }
+    
+    public void extractData(BufferedImage bufferedImage){
         Color colorArray[][] = new Color[bufferedImage.getHeight()][bufferedImage.getWidth()];
         char[][][][] bitPlanesPixels = new char[8][3][bufferedImage.getHeight()][bufferedImage.getWidth()];
        

### 2014-07-17 Paper/main.tex
Edited paper. Added Implementation description

@@
 \subsubsection{BPCS Steg}
+\label{bpcsSteg}
 In order to be able to recover the image after it has been tampered with the image needs to be embedded into itself. 
 For this embedding the proposed method used BPCS Steganography \cite{beaullieubpcs}.
+
 \hspace{0pt} \\
-//TODO explain algorithm briefly
+This method works with the following steps:
+\begin{enumerate}
+  \item Get the binary representation of the image
+  \item Convert the binary representation into Gray code
+  \item Divide the image into bit planes
+  \item Divide the bit planes into 8x8 blocks
+  \item Calculate the complexity for each block //TODO find reference for how this is done
+  \item Divide the message to be embedded into similar binary 8x8 blocks
+  \item Calculate the complexity for each message block and conjugate if not complex enough
+  \item for each image block that is complex enough, replace that block with the next message block
+  \item Convert the blocks back to binary representation
+  \item reconstruct the image from the processed blocks 
+\end{enumerate}
+The proposed method works with colour images which means that for each pixel there is a red, green and blue value. This means that each block effectively store 3 bits for each pixel.
 
@@
 As a solution to this problem each block used for embedding is treated as a separate embedding entity.
-The is thus not overlap between two different blocks used for embedding.
+There is thus no overlap between two different blocks used for embedding.
 With the compression method used (\ref{ImageCompression}) this means that effectively 7 pixels are embedded in each embedding block.
@@
 \subsubsection{Fragile Watermark}
+\label{impFragileWatermark}
 In order to be able to detect which parts of the image have been tampered with a fragile watermark can be used.
@@
 
+\hspace{0pt} \\
+The fragile watermark used in the proposed method embeds a calculated hash into the image that is used to authenticate the content when the image is processed on the receiving end.
+
+\hspace{0pt} \\
+For each of the 8x8 pixel blocks in the image a hash is calculated by combining the binary of each of the 7 Most significant bit layers of that block.
+This binary stream is then used as the input to the SHA-256 hash function the output is a 256 bit hash string for that image block.
+This hash string is then truncated to a length of 185 bits.
+This is done to enable the conjugation map that was generated when embedding the image content (\ref{bpcsSteg}) to be stored at the end of the stream.
+
+\hspace{0pt} \\
+//TODO - Find reference for truncation of hash security
+\hspace{0pt} \\
+
+The conjugation map is appended to the truncated hash string to create a binary string of 192 bits.
+These 192 bits are finally embedded into the least significant bit plane of that specific block effectively replacing all the bits in that bit plane with the generated bit stream.
+
+\subsection{Extraction and Restoration}
+
+\subsubsection{Image authentication}
+The first step for the image extraction and restoration process is to determine which, if any, parts of the image has been tampered with.
+This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
+for each block (block refers here to 8x8 pixel blocks, thus a block here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
+The embedded hash is then extracted from the Least significant bit plane of that block.
+The extracted hash is then compared with the calculated hash and if they match the block is authentic.
+
+\hspace{0pt} \\
+For each authentic block the 7 most significant bit planes have their complexity calculated.
+If a bit plane block is found to be complex enough it is assumed that there is image information embedded into it.
+The embedded conjugation map is extracted at this point and if it is found that any of the complex enough bit planes were conjugated the conjugation algorithm is applied again to reverse the conjugation.
+
+\hspace{0pt} \\
+//TODO Explain the conjugation in more detail
+\hspace{0pt} \\
+
+The embedded image content is extracted at this point from the processed bit planes and the embedded image is reconstructed.
+The reconstructed image is then also split into pixel blocks.
+The original pixel blocks now get iterated and each block that was found not to be authentic is replaced by the corresponding reconstructed pixel block.
+
+\hspace{0pt} \\
+This process restores the tampered areas of the image if their matching pixel blocks could be extracted from the image.
+That is if the embedded blocks were not destroyed in the image modification.
+Obviously if too large a part of the image has been modified it would not be possible to accurately reconstruct the image because too much of the embedded image content would be lost.
+
 \bibliography{main}

### 2014-07-28 Experiments/HonoursResearchApplication/src/embedding/Block.java
8 bit per block embedding and randomization
Randomization still needs some work

@@ -13,6 +13,8 @@ public class Block {
     public boolean authentic = true;
     public boolean conjugated = false;
     public boolean isComplex = false;
+    public int row = 0;
+    public int col = 0;
 
     public Block() {
         this.block = new char[3][blockSize][blockSize];

### 2014-07-28 Experiments/HonoursResearchApplication/src/embedding/FragileWatermark.java

@@ -1,13 +1,6 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-
 package embedding;
 
 import static embedding.SelfEmbed.embedFragileWatermark;
-import static embedding.SelfEmbed.getBinary;
 import static embedding.SelfEmbed.getBinary;
 import static embedding.SelfEmbed.getChangableBits;
 import static embedding.SelfEmbed.getChangableBitsCount;
@@ -32,6 +25,7 @@ public class FragileWatermark {
     public static ArrayList<Block> embedWaterMarkInLSBLayer(ArrayList<Block> imageBlocks) throws NoSuchAlgorithmException, IOException{
         String blockBinary = "";
         String conjugationMap = "";
+        String embeddingLocationMap = "";
         ArrayList<Block> newBlocks = new ArrayList();
         for(Block block: imageBlocks){
             if(block.lsbLayer!=7){
@@ -41,11 +35,15 @@ public class FragileWatermark {
                     conjugationMap+='1';
                 else
                     conjugationMap+='0';
+                
+                embeddingLocationMap+= ImageContentExtractionAndCompression.getBinary(block.row, 9);
+                embeddingLocationMap+= ImageContentExtractionAndCompression.getBinary(block.col, 9);
             }
             else{
                 //192 = 8x8x3
 
-                String hashString = ShaHashHelper.getBlockHash(blockBinary,185);
+                String hashString = ShaHashHelper.getBlockHash(blockBinary,59);
+                hashString += embeddingLocationMap;
                 hashString += conjugationMap;
                 char[][][] newLsbContent;
                 newLsbContent = block.getBlock();
@@ -63,6 +61,7 @@ public class FragileWatermark {
                 }
                 
                 conjugationMap="";
+                embeddingLocationMap = "";
                 block.setBlock(newLsbContent);
                 newBlocks.add(block);
                 blockBinary="";

### 2014-07-28 Experiments/HonoursResearchApplication/src/embedding/ImageContentExtractionAndCompression.java

@@ -23,7 +23,7 @@ public class ImageContentExtractionAndCompression {
         *18 = the two position integers that get embedded
         *7 the two position integers only get embedded once for every 7 pixels
         */
-        double newPixelAmount = embeddingCapacity/(24.0+(18/7.0));
+        double newPixelAmount = embeddingCapacity/(24.0);
         double percentageLoss = (newPixelAmount/(512*512)*100);
         System.out.println("Size of embedded image: "+percentageLoss);
         int newWidth = (int) Math.sqrt(newPixelAmount);
@@ -42,29 +42,33 @@ public class ImageContentExtractionAndCompression {
         }
 
         BufferedImage scaledBuf = getScaledImage(bufImage,newWidth,newWidth);
-        int perBlockCheck = 7;
+        int perBlockCheck = 8;
         String binary = "";
         ArrayList<Block> blockList = new ArrayList<>();
+        int rowIndex = 0;
+        int colIndex = 0;
         for (int i = 0; i < scaledBuf.getHeight(); i++) {
             for (int j = 0; j < scaledBuf.getWidth(); j++) {
                 //7 is used because that is the amount of pixels that will be stored per block
-                if(perBlockCheck==7)
+                if(perBlockCheck==8)
                 {
                     //System.out.println("binarysize:" + binary.length());
                     if(perBlockCheck!=0 && !binary.equals("")){
 //                        System.out.println("binary: "+ binary);
 //                        System.out.println("ImediateBinary: "+ FragileWatermark.getBlockBinary(makeBlockRGBTogether(binary)));
                         Block tmpBlock = makeBlockRGBTogether(binary);
+                        //setting the index of the embedded pixels that will be added to the embedding map in the lsb layer
+                        tmpBlock.row = rowIndex;
+                        tmpBlock.col = colIndex;
                         tmpBlock.calculateComplexity();
                         blockList.add(tmpBlock);
                         
                     }
+                    rowIndex = i;
+                    colIndex = j;
                     perBlockCheck = 0;
                     binary = "";
-                    //binary += binaryImageSize;
-                    //System.out.println(getBinary(i,9)+" \\ "+getBinary(j,9));
-                    binary += getBinary(i,9);
-                    binary += getBinary(j,9);
+                    
                 }
                     
                 Color pixelColor = new Color(scaledBuf.getRGB(i, j));
[…]

### 2014-07-28 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java

@@ -1,9 +1,7 @@
 package embedding;
 
 
-import static embedding.FragileWatermark.getBlockBinary;
 import java.awt.Color;
-import java.awt.List;
 import java.awt.image.BufferedImage;
 import java.io.File;
 import java.io.IOException;
@@ -12,7 +10,6 @@ import java.util.ArrayList;
 import java.util.Collections;
 import java.util.Random;
 import javax.imageio.ImageIO;
-import static loadImage.ImageHolder.encodeGray;
 import loadImage.MyImage;
 
 /**
@@ -24,7 +21,7 @@ public class SelfEmbed {
     private static int cornerCol=0;
     public static int imageWidth = 0;
     //0.636
-    public static final double embeddingRate = 0.65;
+    public static final double embeddingRate = 0.7;
     
     public static MyImage selfEmbed(MyImage image) throws IOException, NoSuchAlgorithmException{
         ArrayList<Block> blockList = getBlocks(image);
@@ -45,12 +42,19 @@ public class SelfEmbed {
         embeddingCapacity = (suitableBlockCount *186);
         System.out.println("Available embedding capacity (bits): "+embeddingCapacity );
         ArrayList<Block> messageBlocks = ImageContentExtractionAndCompression.getCompressedImageContent(image, embeddingCapacity);
+        messageBlocks = shuffleList(messageBlocks);
         ArrayList<Block> embeddedImageList = embedMessage(blockList,messageBlocks);
         Color[][] reAssembleImageColours = reAssembleImage(embeddedImageList,"finalImage.bmp");
         //Color[][] imageColors = FragileWatermark.embedWaterMark(reAssembleImageColours);
         //saveImageFromColor(imageColors,"finalImage.bmp");
         
         return null;
+    }
+    
+    public static ArrayList<Block> shuffleList(ArrayList<Block> list){
+        long seed = System.nanoTime();
+        Collections.shuffle(list, new Random(seed));
+        return list;
     }
     
     public static ArrayList<Block> shuffelList(ArrayList<Block>  blockList){
@@ -102,21 +106,15 @@ public class SelfEmbed {
                 Block imageBlock = imageBlocks.get(i);
                 Block messageBlock = messageBlocks.get(messageBlockCount);
                 if(messageBlock.getComplexity()<embeddingRate){
-                    //TODO should conjugate here and save record of this in conjugation map
-                    //System.out.println("messageBlock binary before: "+getBlockBinary(messageBlock));
+                    //conjugate here and save record of this in conjugation map
[…]

### 2014-07-28 Experiments/HonoursResearchApplication/src/extraction/Extract.java

@@ -31,7 +31,6 @@ public class Extract {
         //blocks of image
         ArrayList<Block> blocks = SelfEmbed.getBlocks(holder.getImage());
         extractImageContent(blocks);
-        //extractWatermark(holder.getImage());
         
     }
     
@@ -44,9 +43,32 @@ public class Extract {
             }
             else{
                 //192 = 8x8x3
-                String hashString = ShaHashHelper.getBlockHash(blockBinary,185);
+                String hashString = ShaHashHelper.getBlockHash(blockBinary,59);
+                
                 String extractedHash = getBlockBinary(block);
-                extractedHash = extractedHash.substring(0,extractedHash.length()-7);
+                extractedHash = extractedHash.substring(0,extractedHash.length()-133);
+                
+                String embeddingMap = getBlockBinary(block);
+                embeddingMap = embeddingMap.substring(embeddingMap.length()-133,embeddingMap.length()-7);
+                
+                int[][] embeddingMapIntegers = new int[7][2];
+                String indexNumber = embeddingMap;
+                int blockStartIndex = x-7;
+                for (int i = 0; i < 7; i++) {
+                    String numberRow = indexNumber.substring(0,9);
+                    embeddingMapIntegers[i][0] = getIntFromBinary(numberRow);
+                    indexNumber = indexNumber.substring(9,indexNumber.length());
+                    
+                    String numberCol = indexNumber.substring(0,9);
+                    embeddingMapIntegers[i][1] = getIntFromBinary(numberCol);
+                    indexNumber = indexNumber.substring(9,indexNumber.length());
+                    
+                    Block tempBlock = blocks.get(blockStartIndex+i);
+                    tempBlock.row = embeddingMapIntegers[i][0];
+                    tempBlock.col = embeddingMapIntegers[i][1];
+                    
+                    blocks.set(blockStartIndex+i, tempBlock);
+                }
                 
                 String blockConjugationMap = getBlockBinary(block);
                 blockConjugationMap = blockConjugationMap.substring(blockConjugationMap.length()-7,blockConjugationMap.length());
@@ -82,48 +104,51 @@ public class Extract {
             block.calculateComplexity();
         }
        Color[][] reconColor = new Color[SelfEmbed.imageWidth][SelfEmbed.imageWidth];
+       boolean nullAlreadyUsed = false;
         for(Block block: blocks){
[…]

### 2014-07-28 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java
Changed the way blocks are randomized

@@ -51,10 +51,44 @@ public class SelfEmbed {
         return null;
     }
     
+    //method used to get the embedded blocks as far as possible from their original location
     public static ArrayList<Block> shuffleList(ArrayList<Block> list){
-        long seed = System.nanoTime();
-        Collections.shuffle(list, new Random(seed));
-        return list;
+        //long seed = System.nanoTime();
+        //Collections.shuffle(list, new Random(seed));
+        int quater = list.size()/8;
+        ArrayList<Block> newList = new ArrayList<Block>();
+        for (int i = quater*7; i < list.size(); i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = quater*2; i < quater*3; i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = quater*5; i < quater*6; i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = 0; i < quater; i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = quater*4; i < quater*5; i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = quater; i < quater*2; i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = quater*6; i < quater*7; i++) {
+            newList.add(list.get(i)); 
+        }
+        
+        for (int i = quater*3; i < quater*4; i++) {
+            newList.add(list.get(i)); 
+        }
+        return newList;
     }
     
     public static ArrayList<Block> shuffelList(ArrayList<Block>  blockList){

### 2014-08-15 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java
added the tree

@@ -19,7 +19,7 @@ public class SelfEmbed {
     private static int cornerCol=0;
     public static int imageWidth = 0;
     //0.636
-    public static final double embeddingRate = 0.7;
+    public static final double embeddingRate = 0.8;
     
     public static MyImage selfEmbed(MyImage image) throws IOException, NoSuchAlgorithmException{
         ArrayList<Block> blockList = getBlocks(image);

### 2014-08-15 Experiments/HonoursResearchApplication/src/honoursresearchapplication/HonoursResearchApplication.java

@@ -15,7 +15,7 @@ public class HonoursResearchApplication {
     public static void main(String[] args) throws IOException, NoSuchAlgorithmException {
        long start = System.currentTimeMillis();
        ImageHolder holder = new ImageHolder();
-       holder.extractImageData("lena.bmp");
+       holder.extractImageData("tree.bmp");
        
        SelfEmbed.selfEmbed(holder.getImage());
        System.out.println("Exiting After Successfull execution: "+ ((System.currentTimeMillis()-start)/1000.0)+"s");

### 2014-08-15 Experiments/HonoursResearchApplication/src/embedding/SelfEmbed.java
Reran test with lena image

@@ -19,7 +19,7 @@ public class SelfEmbed {
     private static int cornerCol=0;
     public static int imageWidth = 0;
     //0.636
-    public static final double embeddingRate = 0.8;
+    public static final double embeddingRate = 0.7;
     
     public static MyImage selfEmbed(MyImage image) throws IOException, NoSuchAlgorithmException{
         ArrayList<Block> blockList = getBlocks(image);

### 2014-08-15 Experiments/HonoursResearchApplication/src/honoursresearchapplication/HonoursResearchApplication.java

@@ -15,7 +15,7 @@ public class HonoursResearchApplication {
     public static void main(String[] args) throws IOException, NoSuchAlgorithmException {
        long start = System.currentTimeMillis();
        ImageHolder holder = new ImageHolder();
-       holder.extractImageData("tree.bmp");
+       holder.extractImageData("lena.bmp");
        
        SelfEmbed.selfEmbed(holder.getImage());
        System.out.println("Exiting After Successfull execution: "+ ((System.currentTimeMillis()-start)/1000.0)+"s");

### 2014-08-15 Experiments/PSNRCalculate/src/psnrcalculate/PSNR.java
Used the psnr test class to test

@@ -7,8 +7,8 @@ import java.io.IOException;
 import javax.imageio.ImageIO;
 
 public class PSNR {
-    final static String originalName = "lena.bmp";
-    final static String modifiedName = "ReconstructedImageAfterScaleUp.bmp";
+    final static String originalName = "tree.bmp";
+    final static String modifiedName = "finalImage.bmp";
     public static void calculate() throws IOException{
     int     nrows, ncols;
     int     img1[][], img2[][];

### 2014-08-16 Paper/main.tex
Added a small reference
Version 1.0
Version1.0 before branch for new features
Extended implementation in paper

@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
   \item Calculate the complexity for each block //TODO find reference for how this is done
-  \item Divide the message to be embedded into similar binary 8x8 blocks
-  \item Calculate the complexity for each message block and conjugate if not complex enough
-  \item for each image block that is complex enough, replace that block with the next message block
+  \item Divide the image content reference to be embedded into similar binary 8x8 blocks
+  \item Calculate the complexity for each image reference block and conjugate if not complex enough
+  \item for each image block that is complex enough, replace that block with the next image reference block
   \item Convert the blocks back to binary representation
@@
 There is thus no overlap between two different blocks used for embedding.
-With the compression method used (\ref{ImageCompression}) this means that effectively 7 pixels are embedded in each embedding block.
-Along with these 7 pixels the location of the first pixel is also embedded using two integers.
+The image reference is first process using the method explained later in this section.
+Each block has 12 pixels (with a bit depth of 16 bits) of the reference image embedded into it.
+An embedding map containing the location of the first pixel to be embedded in the block is also created.
+Since the reference image pixels are embedded in order it is only necessary to know the location of the first pixel.
+This embedding map is then embedded into the LSB layer of that specific 8x8 block of pixels 
 This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
+This serves to give random access to the embedded content which is an essential property of self embedding as defined by (Korus et al. \cite{korus2013efficient})
 
@@
 \hspace{0pt} \\
-Total embedded bits = (7*24) + (2*9) = 186
+Total embedded bits = 12*16 = 192
+
+\paragraph{Image resizing}
+\label{ImageCompression}
+The image that is embedded into the cover image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
+The proposed method however does not utilize compression as it is beyond the scope of this paper.
+The proposed method rather reduces the bit rate of the image from 24 bits to 16 which reduces the size of each pixel by 6 bits.
+The image's size is also reduced according to the space available for embedding.
+When extracting the image reference data again the image is scaled up to it's original size of 512x512 pixels before restoration
+
+\paragraph{Block Spread}
+It is very important how the embedded content is spread across the image because this affects the tamper rate
+\hspace{0pt} \\
+//TODO put reference here
+\hspace{0pt} \\
+The proposed method uses a simple method for spreading the image reference content across the image.
+The image reference content to be embedded is first divided into blocks as per the BPCS steg algorithm.
+These blocks are subsequently stored in a list. 
+The created list is then reversed before embedding.
+Reversing the list means that the image reference content that contains the bottom right part of the original image will now be embedded into the top left part of the cover image.
+This creates an effect where the embedded reference content is far away from the content that it is referencing.
+This is important because if a piece of the cover image is destroyed it would not be able to recover it if that destroyed piece's reference content was destroyed with it.
+
+\paragraph{Conjugation}
+//TODO Look into references for this 
+\hspace{0pt} \\
+If a image content reference block is found to not be complex enough that block needs to be conjugated before embedding.
+This is important because if a block is not complex enough it cannot be detected when extracting and it may cause visual distortions to the image since it is replacing a complex block.
 
 \hspace{0pt} \\
-This means that there is an excess of 6 bits per block that are not used for embedding. This is effectively means there are 6 bits of embedding space being wasted with each block.
-This is caused by the need to be able to identify blocks even after the image has been modified.
+The block complexity is calculated by using a border complexity method.
+That is for each binary bit that has an adjacent binary bit that is different that it the border count is increased. 
+The final border count is then divided with the theoretical maximum border count, which would be a grid with a checkerboard pattern of 1's and 0's.
 
-\paragraph{Image Compression}
-\label{ImageCompression}
-The image that is embedded into the cover image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
-Compression however is not the focus of this study.
-The embedded image is thus just a resized version of the original image.
-A higher quality reconstruction could be achieved if a better compression algorithm is used.
+\hspace{0pt} \\
+To conjugate a block each value in the grid needs to be changed to the XOR value of the original grid value and the corresponding value in a checkerboard grid (starting with a 1 in the top left hand corner).
+To reverse the conjugation this process simply needs to be repeated.
 
-\paragraph{Block Spread}
-//TODO
 \hspace{0pt} \\
-It is very important how the embedded content is spread across the image because this affects the tamper rate
-\hspace{0pt} \\
-//put reference here
-\hspace{0pt} \\
-And explain further
+This method of conjugation is a simple method that makes a block more complex while still allowing the original values of the block to be retrieved.
 
@@
 \hspace{0pt} \\
-For each of the 8x8 pixel blocks in the image a hash is calculated by combining the binary of each of the 7 Most significant bit layers of that block.
+For each of the 8x8 pixel section in the image a hash is calculated by combining the binary of each of the 7 Most significant bit layers of that section.
 This binary stream is then used as the input to the SHA-256 hash function the output is a 256 bit hash string for that image block.
-This hash string is then truncated to a length of 185 bits.
-This is done to enable the conjugation map that was generated when embedding the image content (\ref{bpcsSteg}) to be stored at the end of the stream.
+This hash string is then truncated to a length of 57 bits.
+This is done to enable the conjugation map as well as the embedding map that was generated when embedding the image content (\ref{bpcsSteg}) to be stored at the end of the stream.
 
 \hspace{0pt} \\
-//TODO - Find reference for truncation of hash security
+//TODO - Find reference for truncation of hash security, also explain why a 57 bit hash is sufficient
 \hspace{0pt} \\
@@
 The conjugation map is appended to the truncated hash string to create a binary string of 192 bits.
-These 192 bits are finally embedded into the least significant bit plane of that specific block effectively replacing all the bits in that bit plane with the generated bit stream.
+These 192 bits are finally embedded into the least significant bit plane of that specific section of the cover image effectively replacing all the bits in that bit plane with the generated bit stream.
 
@@
 
+\subsubsection{Image restoration}
 \hspace{0pt} \\
@@
 \hspace{0pt} \\
-//TODO Explain the conjugation in more detail
-\hspace{0pt} \\
-
 The embedded image content is extracted at this point from the processed bit planes and the embedded image is reconstructed.
+In order to know the location of the extracted pixels the embedding map that was embedded into the LSB bit plane of that image section is consulted \ref{bpcsSteg}.
+The reconstructed image is then scaled up back to it's original size of 512x512 pixels.
 The reconstructed image is then also split into pixel blocks.
@@
 
+\section{Results}
+
 \bibliography{main}

### 2014-08-17 Paper/main.tex
Results
Updated the research paper adding the results

@@
 
-\title{High quality content reconstruction in images using a high capacity self-embedding algorithm}
+\usepackage{graphicx}
+\graphicspath{ {images/}}
+
+\title{High quality content reconstruction in images using the BPCS Steganography algorithm}
 
@@
 
+\iffalse 
 \tableofcontents 
+\fi
 
 \section{Introduction}
+
 This section gives a brief description of the concepts used in this report.
@@
 \subsection{Embedding}
+\label{embedding}
 
@@
 \subsection{Extraction and Restoration}
-
+\label{extractRestore}
 \subsubsection{Image authentication}
@@
 \section{Results} 
+In testing the proposed method a simple experiment was set up in which the image was processed using the embedding process described in \ref{embedding}.
+The results of that process can be seen in the following two images, showing the original Image and the image after the embedding process.
+Note that in this case the Image Reference content was only embedded once
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"lena"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage"}%
+}%
+\caption{Embedding Once. Left: Original Image, Right: Image After embedding}
+\label{fig:lenaEmbedOnceEmbedding}
+\end{figure}
+
+//TODO get reference for PSNR
+\hspace{0pt} \\
+After the image after embedding was generated the PSNR of the embedded image in relation to the original image was calculated.
+In this instance the PSNR after embedding was: 34.92dB
+
+\hspace{0pt} \\
+The next step in the experiment conducted was to modify the Image after embedding (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+After the Image was modified it was processed using the method described in \ref{extractRestore}.
+The results of this process can be seen in the following two images, showing the Image after Tampering and the Image after Restoration.
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage - Copy"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImageAfterRestoration"}%
+}%
+\caption{Embedding Once. Left: Image After Tampering, Right: Image After Restoration}
+\label{fig:lenaEmbedOnceRestoration}
+\end{figure}
+
+\hspace{0pt} \\
+After the image (shown in figure \ref{fig:lenaEmbedOnceRestoration}) was restored the PSNR of the Image After Restoration was calculated in relation to the Original Image (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+In this instance the PSNR after restoration was: 34.89dB.
+
+\hspace{0pt} \\
+It was found in the experimentation process that if the Image reference content is only embedded once that the quality of the Image after embedding as well as the quality of the Image after restoration was relatively high.
+It was however found that the tamper rate possible was quite low at \textless 3\%.
+To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the Image reference content now being embedded twice.
+The results can be seen below
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"lena"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage"}%
+}%
+\caption{Embedding Twice. Left: Original Image, Right: Image After embedding}
+\label{fig:lenaEmbedTwiceEmbedding}
+\end{figure}
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage - Copy"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImageAfterRestoration"}%
+}%
+\caption{Embedding Twice. Left: Image After Tampering, Right: Image After Restoration}
+\label{fig:lenaEmbedTwiceRestoration}
+\end{figure}
+
+\hspace{0pt} \\
+In order to embed the Image reference content twice the content needs to be half the size that is used when embedding once.
+This reduces the quality of the Image after Restoration from the previous 34.89dB to 32.52 dB.
+The tamper rate however is now increased from \textless 3\% to \textless 35\%
+
+\hspace{0pt} \\
+This experiment was also completed on the following image.
+First Embedding the Image reference content once:
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.3375]{"tree"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage"}%
+}%
+\caption{Embedding Once. Left: Original Image, Right: Image After embedding}
+\label{fig:treeEmbedOnceEmbedding}
+\end{figure}
+
+\hspace{0pt} \\
+The PSNR of the Image after embedding (show in figure \ref{fig:treeEmbedOnceEmbedding}) was 27.94dB.
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage - Copy"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImageAfterRestoration"}%
+}%
+\caption{Embedding Once. Left: Image After Tampering, Right: Image After Restoration}
+\label{fig:treeEmbedOnceRestoration}
+\end{figure}
+
+\hspace{0pt} \\
+The PSNR of the Image after restoration (show in figure \ref{fig:treeEmbedOnceRestoration}) was 27.72dB.
+The tamper rate, as was the case with the lena image, was also \textless 3\%.
+The experiment was also conducted by embedding the Image reference content twice.
+As is shown below.
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.3375]{"tree"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage"}%
+}%
+\caption{Embedding Twice. Left: Original Image, Right: Image After embedding}
+\label{fig:treeEmbedTwiceEmbedding}
+\end{figure}
+
+\hspace{0pt} \\
+The PSNR of the Image after embedding (show in figure \ref{fig:treeEmbedTwiceEmbedding}) was 27.93dB.
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage - Copy"}%
+\hspace{0.1cm}
+\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImageAfterRestoration"}%
+}%
+\caption{Embedding Twice. Left: Image After Tampering, Right: Image After Restoration}
+\label{fig:treeEmbedTwiceRestoration}
+\end{figure}
+
+\hspace{0pt} \\
+The PSNR of the Image after restoration (show in figure \ref{fig:treeEmbedOnceRestoration}) was 26.05dB.
+The tamper rate, as was the case with the lena image, was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
+
+\hspace{0pt} \\
+The second image used thus behaved in a similiar manner to the first image with the only significant difference being the much lower PSNR values produced
+
+\section{Conclusion}
+//TODO Write the conclusion
 

### 2014-08-17 Paper/main.tex
Added references for PSNR and HASH length

@@
 \usepackage[margin=1.0in]{geometry}
+\usepackage{mathtools}
 
@@
   \item Divide the bit planes into 8x8 blocks
-  \item Calculate the complexity for each block //TODO find reference for how this is done
+  \item Calculate the complexity for each block
   \item Divide the image content reference to be embedded into similar binary 8x8 blocks
@@
 \hspace{0pt} \\
-//TODO - Find reference for truncation of hash security, also explain why a 57 bit hash is sufficient
+The SHA-256 hash used is truncated to a 57 bit hash. 
+This means that the hash has y possible unique values 
+\[ y = 57^2 = 3249 \]
+The image has 512x512 pixels that are divided into 8x8 sections.
+This means that there are k amount of unique sections in the image
+\[x = \frac{512}{8} = 64 \]
+\[k = x^2 =64^2 = 4096 \]
+Since k \textgreater y the proposed solution is subject to the pigeonhole principle \cite{cook1976short}.
+The pigeonhole principle states that since the input for the hash function (k) is greater than the amount of unique outputs of the hash function (y) there will be duplicate hash values produced.
+However since the generated hash values are calculated from each section and then compared to the bits stored in the LSB layer of that section it is highly unlikely, but not impossible, that a false positive for tampering will occur.
+Extensive testing was conducted on a number of images and no situation was found where such a collision occurred within normal operation.
+However should this case arise, the proposed method would simple restore that section as well.
+Thus not having a major impact on the final result of the restoration.
+
 \hspace{0pt} \\
-
 The conjugation map is appended to the truncated hash string to create a binary string of 192 bits.
@@
 
-//TODO get reference for PSNR
 \hspace{0pt} \\
+All images will be evaluated using Peak Signal to Noise Ratio (PSNR) because it is the most widely used measurement for objective image quality and is easily comparable with previous research.
+\cite{wang2002image}
 After the image after embedding was generated the PSNR of the embedded image in relation to the original image was calculated.

### 2014-08-21 Paper/main.tex
Finished adding needed references for findings

@@
 \hspace{0pt} \\
-//TODO put reference here
-\hspace{0pt} \\
+\cite{korus2013efficient} Has found that it is important that the image reference content should be uniformly distributed across the cover image and that each part of the cover image should contain equal information about the image reference content.
+Due to the fact that the proposed method uses an adaptive embedding algorithm it is not possible for each part of the cover image to contain equal information about the image content reference.
+The proposed method does however distribute the embedded image reference content evenly among the blocks that were identified as suitable for embedding.
 The proposed method uses a simple method for spreading the image reference content across the image.
@@
 \paragraph{Conjugation}
-//TODO Look into references for this 
-\hspace{0pt} \\
 If a image content reference block is found to not be complex enough that block needs to be conjugated before embedding.
@@
 \hspace{0pt} \\
-The block complexity is calculated by using a border complexity method.
-That is for each binary bit that has an adjacent binary bit that is different that it the border count is increased. 
-The final border count is then divided with the theoretical maximum border count, which would be a grid with a checkerboard pattern of 1's and 0's.
+The block complexity is calculated by using a border complexity method. \cite{beaullieubpcs}
+That is for each binary bit that has an adjacent binary bit that is different than it the border count is increased. 
+The final border count is then divided with the theoretical maximum border count, which would be the same a the border count for a grid with a checkerboard pattern.
 

### 2014-08-22 Paper/main.tex
Added interpretation and conclusion

@@
 
-\title{High quality content reconstruction in images using the BPCS Steganography algorithm}
+\title{Self recovering capabilities in images using the BPCS Steganography algorithm}
 
@@
 \iffalse
+
+\fi
 \tableofcontents
-\fi
 
@@
 \[k = x^2 =64^2 = 4096 \]
-Since k \textgreater y the proposed solution is subject to the pigeonhole principle \cite{cook1976short}.
+Since k \textgreater y the proposed method is subject to the pigeonhole principle \cite{cook1976short}.
 The pigeonhole principle states that since the input for the hash function (k) is greater than the amount of unique outputs of the hash function (y) there will be duplicate hash values produced.
@@
 \hspace{0pt} \\
-The second image used thus behaved in a similiar manner to the first image with the only significant difference being the much lower PSNR values produced
+The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced
+
+\section{Interpretation of results}
+The proposed method for self-recovering images using the BPCS Steg embedding algorithm described in the preceding sections was shown to be effective.
+According to Appendix B in \cite{korus2013efficient} the proposed method achieved Average to High quality restoration in the case of figure \ref{fig:lenaEmbedTwiceRestoration} and figure \ref{fig:lenaEmbedOnceRestoration} respectively.
+The proposed method achieved Low quality restoration in the case of figure \ref{fig:treeEmbedOnceRestoration} and figure \ref{fig:treeEmbedTwiceRestoration} according to \cite{korus2013efficient}.
+
+\hspace{0pt} \\
+The quality measures mentioned were measured using the PSNR method. \cite{huynh2008scope} However determined that the validity of PSNR is limited to modifications within the same image.
+It is thus not reliable to compare PSNR values between two different images.
+With that in mind the image from figures \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} was specifically chosen because it is well used in the literature and can serve to compare to proposed method to other methods available in the literature.
+Such comparisons follow below
+
+\hspace{0pt} \\
+The proposed method does not perform as well as the method described in \ref{ErasureChannelOverview}.
+The proposed method achieves PSNR values that are about 5dB worse than the method described in \ref{ErasureChannelOverview}.
+Compared to the method described in \ref{differenceExpansionOverview} the proposed method performs in a similar manner.
+The PSNR values achieved are worse than that of the method in \ref{differenceExpansionOverview} but the difference is around 1-2dB and is thus almost negligible.
+It should also be mentioned that the proposed method uses no compression on the image reference content, similar to the method in \ref{differenceExpansionOverview}.
+This method thus serves as a more equal comparison.
+
+\hspace{0pt} \\
+\cite{wang2002image} Points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
+PSNR is a useful measure for objective image quality assessment to a certain degree however there are other important factors to consider.
+The one important factor is how a person would perceive the image quality.
+Another important factor is if the meaning of the image is still clear even after reconstruction.
+This would typically mean being able to identify key features of the image easily. 
+The proposed method performs well under this form a visual analysis.
+
+\hspace{0pt} \\
+It was found during experimenting that Image quality can vary greatly among different image using the proposed method.
+This can be attributed to the fact that an adaptive embedding method is used and the embedding thus differs depending on the chosen cover image.
+The embedding rate and effects of the embedding rate seemed consistent across the different images used.
 
 \section{Conclusion}
-//TODO Write the conclusion
+The proposed method described used an adaptive embedding algorithm described in \ref{bpcsSteg}.
+The proposed method was shown to provide good quality as well as a good tamper rate.
+It was also shown that the quality of the cover image after embedding the image reference content and the image quality after restoration differs depending on the cover image chosen.
+This was attributed to the adaptive embedding algorithm used.
+It was also mentioned that no compression was used on the image reference content that was embedded into the cover image.
+If compression is used it may result in higher quality of the image after restoration as well as the cover image due to fewer modifications that will be made during embedding.
 

### 2014-08-26 Paper/main.tex
Started with a proof read and modification of paper

@@
 There is an inherent trade-off (described in \ref{introQualityTrade}) between the quality of the image after embedding and the quality of the image after recovery.
-This report proposes a method in which a high capacity embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.
+This report proposes a method in which a high capacity image steganography embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.
 
@@
 This means that if modifications are made to the watermarked image it would be possible to detect that modifications were made as well as what parts of the image were modified.
-This is a necessary component in self recovering images because in order to be able to recover image data it first needs to be determined what data needs to be recovered.
-It thus needs to be know what data was modified.
+This is a necessary component in self recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so what parts of the image was modified.
+The proposed method will use this information to determine which parts of the image should be recovered from the image reference content.
 A fragile watermark is used for this purpose.
@@
 This embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself \cite{fridrich1999images}.
-A self embedding and recovery scheme such as the proposed method contains a couple of high level steps.
+A self embedding and recovery scheme (Further referred to as reconstruction) such as the proposed method contains a couple of high level steps.
 Firstly the authentic image content is embedded into the original image along with a fragile watermark.
-This watermark will help determine later on which parts of the image was modified if any (see \ref{introFragWatermarking}).
-When the authentic image needs to be recovered, after modification, the fragile watermark is used to determine which content was modified.
-An attempt is then made to extract the original content for the areas that were modified from the modified image.
+The resulting image is referred to as the image after embedding
+This watermark will help determine later on which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
+When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which content was modified.
+An attempt is then made to extract the original content for the areas that were modified in the image after embedding.
 If this process is successful the user is left with a high quality reconstruction of the original image.
@@
 There is an inherent quality trade-off present within self embedding schemes.
-The trade-off exists between the image after embedding and the image after recovery.
+The trade-off exists between the image after embedding and the image after reconstruction.
 If an embedding algorith such as LSB(Least significan bit) embedding is used (as in \ref{ErasureChannelOverview}) the actual bit values of the original image are overwritten.
@@
 However this presents another problem.
-The quality of the image after recovery is dependent on the amount of authentic image data embedded into the image.
+The quality of the image after reconstruction is dependent on the amount of authentic image data (further referred to as the image reference content) embedded into the image.
 
@@
 To achieve maximum quality after embedding the embedded information must be as little as possible.
-To achieve maximum quality after recover the embedded information must be as large as possible to be as close as possible to the original image.
+To achieve maximum quality after reconstruction the embedded image reference content must be as large as possible to be as close as possible to the original image.
 There exists then a trade-off between the two.
@@
 \label{introQualityIncrease}
-It might be possible to increase the quality of the image after recovery while still keeping the quality after embedding high.
-It is proposed that applying an embedding algorithm designed for high capacity while retaining quality (as discussed in \ref{introHighCap}) to the problem of self embedding could possibly increase the quality of the image after embedding as well as after recovery.
+It might be possible to increase the quality of the image after reconstruction while still keeping the quality after embedding high.
+It is proposed that applying an embedding algorithm designed for high capacity while retaining quality (as discussed in \ref{introHighCap}) to the problem of self recovering could possibly increase the quality of the image after embedding as well as after reconstruction.
 This is because such an algorithm should provide higher embedding capacity while producing less noise in the image.
@@
 \label{introHighCap}
-The proposed method in this paper attempts to apply the algorithm for BPCS Steganography \cite{beaullieubpcs} to the problem of self recovering images, specifically to increase overall quality.
+The proposed method in this paper attempts to apply the algorithm for BPCS Steganography (Bit-Plane Complexity Segmentation Steganography) \cite{beaullieubpcs} to the problem of self recovering images, specifically to increase overall quality.
 
@@
 BPCS steg differs however in the fact that the blocks can be conjugated in a checker board pattern to increase complexity and decrease detectability if needs be.
+BPCS steg also differs in the way in which embedding takes place.
+Instead of always embedding into the 3-LSB planes as in \ref{DynamicBlockOverview}.
+Bit planes are dynamically allocated for embedding.
+One section may thus only embed into one bit plane while another may use all 7 available bit planes.
 
@@
 
-\section{Current self embedding and recovery schemes and algorithms}
+\section{Current self recovering image schemes and algorithms}
 
@@
 It would also help highlight strengths and shortcomings in the proposed method.
-The methods analyzed were chosen because they all provide good quality cover and reconstructed images.
-They also each offer an unique approach or aspect to the image recovery problem and would thus provide a good idea of the different approaches that have already been tested.
+The methods analyzed were chosen because they all provide good quality images after embedding as well as good quality images after reconstructed.
+They also each offer an unique approach or aspect to the self recovering image problem and would thus provide a good overview of the different approaches that have already been tested.
 
@@
 The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
-The method uses LSB embedding to embed the reference data into the image itself.
-The method also uses a global spreading technique to spread the reference data across the image.
-They also propose that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after recovery.
+The method uses LSB embedding to embed the image reference content into the image itself.
+The method also uses a global spreading technique to spread the image reference content across the image.
+They also propose that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after reconstruction.
 
 \hspace{0pt} \\
-The method proposed in \cite {korus2013efficient} achieves good quality cover images with a PSNR \textgreater 35dB. 
-The method also achieves an image recovery quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with taper rates of 50\% and 33\% respectively.
-The method does not let the restoration quality of the image deteriorate much if the tampering rate is increased up to a value of 50\%.
-They do however note that they can only achieve minimal reconstruction performance increases by decreasing the amount of information in the reconstruction reference.
+The method proposed in \cite {korus2013efficient} achieves good quality images after embedding with a PSNR \textgreater 35dB. 
+The method also achieves an image after reconstruction quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with tamper rates of 50\% and 33\% respectively.
+The method does not let the quality of the image after reconstruction deteriorate much if the tampering rate is increased up to a value of 50\%.
+They do however note that they can only achieve minimal reconstruction performance increases by decreasing the amount of information in the image reference content.
 By using only 50\% of the available capacity the maximal tampering rate increases form 50\% to 59\%.
@@
 \hspace{0pt} \\
-This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered with before recovery starts to deteriorate.
+This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered with before reconstruction ability starts to deteriorate.
 The security for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
 The authors did not do any statistical analysis on the image.
-The embedding capacity of this method is also acceptable, but because the method uses some of the authentic image data to aid in the recovery the quality of the image, before and after recovery, is still very good even without a very high embedding capacity.
+The embedding capacity of this method is also acceptable, but because the method uses some of the authentic image data to aid in the reconstruction process the quality of the image, before and after reconstruction, is still very good even without a very high embedding capacity.
 
@@
 \hspace{0pt} \\
-The method's \cite {tian2003high} restoration quality is acceptable at roughly 50\%. 
+The method's \cite {tian2003high} quality regarding the image after reconstruction is acceptable at roughly 50\%. 
 The difference expansion this method uses provides extra space for embedding.
@@
 \hspace{0pt} \\ 
-The authors do not mention the image tamper rate that this method \cite {tian2003high} allows.
+The authors do not mention the image tamper rate that this method \cite {tian2003high} achieves.
 
@@
 \label{DynamicBlockOverview}
-(Qian et al) \cite{qian2011image} proposes a method for fragile watermarking with good restoration capabilities using self embedding.
-The proposed method differs from the other methods mention in \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} due to the fact that the proposed method does not embed the information into all blocks uniformly.
-The proposed method classifies different blocks of the image according to the block smoothness.
+(Qian et al) \cite{qian2011image} proposes a method for fragile watermarking with good image restoration capabilities.
+The proposed method differs from the other methods mentioned in \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} due to the fact that the method does not embed the information into all blocks uniformly.
+The method classifies different blocks of the image according to the block smoothness.
 The less smooth the block is the more information will be embedded into it.
@@
 \hspace{0pt} \\
-The advantage of using this dynamic scheme is that there would be less visual distortion to the cover image. 
+The advantage of using this dynamic scheme is that there would be less visual distortion to the image after embedding. 
 This is because if the specific block is already very rough (very busy visually) the human eye would not notice small changes.
 If however the specific block is very smooth (very uniform visually) the human eye is more likely to notice small changes.
-The proposed method thus creates less distortion in the cover image than fixed size methods while still retaining good restoration quality \cite{qian2011image}.
+The method thus creates less distortion in the image after embedding than fixed size methods while still retaining good image after reconstruction quality \cite{qian2011image}.
 
@@
 The method proposed by (Qian et al) \cite{qian2011image} uses the 3 LSB bit planes to embed the needed information in.
-The method achieves good results in experimentation with a cover image PSNR \textgreater 37dB as well as a reconstructed image PSNR = 35dB.
+The method achieves good results in experimentation with a image after embedding PSNR \textgreater 37dB as well as a image after reconstruction PSNR = 35dB.
 The method also allows for a tamper rate \textless 35\%.
@@
 \subsection{Comparison}
-Each of the methods described in \ref{DynamicBlockOverview}, \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} provide good quality cover images as well as good quality reconstructed images.
+Each of the methods described in \ref{DynamicBlockOverview}, \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} provide good quality images after embedding as well as good quality images after reconstruction.
 There are however important differences.
 The method described in \ref{ErasureChannelOverview} offers a very good tamper rate of 50\% compared to the method described in \ref{DynamicBlockOverview} which has a tamper rate of 35\%.
-This means that a larger of the cove image can be tampered with while still being able to restore the image with good quality.
+This means that a larger part of the image after embedding can be tampered with while still being able to reconstruct the image.
 
 \hspace{0pt} \\
-The method described in \ref{differenceExpansionOverview} achieves a cover image with a PSNR \textgreater 35dB, the method described in \ref{ErasureChannelOverview} achieves similar results, however the method described in \ref{DynamicBlockOverview} achieves a cover image PSNR \textgreater 37dB.
-This means that the method described in \ref{DynamicBlockOverview} would have less noise in the cover images after embedding and would thus have better overall quality of the cover images.
+The method described in \ref{differenceExpansionOverview} achieves an image after embedding with a PSNR \textgreater 35dB, the method described in \ref{ErasureChannelOverview} achieves similar results, however the method described in \ref{DynamicBlockOverview} achieves an image after embedding PSNR \textgreater 37dB.
+This means that the method described in \ref{DynamicBlockOverview} would have less noise in the image after embedding and would thus have better overall quality of the image after embedding.
 
 \hspace{0pt} \\
-At almost equal tamper rates of around 33\%-35\% the method described in \ref{ErasureChannelOverview} achieves a restoration PSNR \textgreater 40dB whereas the method described in \ref{DynamicBlockOverview} only achieves a restoration PSNR = 35dB.
-The method described in \ref{differenceExpansionOverview} only achieves a restoration quality of about 50\% the original image.
-This means that the method described in \ref{ErasureChannelOverview} would generally produce better quality restored images than the methods described in \ref{DynamicBlockOverview} and \ref{differenceExpansionOverview}.
+At almost equal tamper rates of around 33\%-35\% the method described in \ref{ErasureChannelOverview} achieves an image after reconstruction PSNR \textgreater 40dB whereas the method described in \ref{DynamicBlockOverview} only achieves an image after reconstruction PSNR = 35dB.
+The method described in \ref{differenceExpansionOverview} only achieves an image after reconstruction quality of about 50\% the original image.
+This means that the method described in \ref{ErasureChannelOverview} would generally produce better quality reconstructed images than the methods described in \ref{DynamicBlockOverview} and \ref{differenceExpansionOverview}.
 
 \hspace{0pt} \\
-This means that the method described in \ref{ErasureChannelOverview} provides the best tamper rate and the best restored image quality, and the method described in \ref{DynamicBlockOverview} provides the best cover image quality.
-The method described in \ref{differenceExpansionOverview} provides decent quality of the cover image as well as the restored image.
+This means that the method described in \ref{ErasureChannelOverview} provides the best tamper rate and the best reconstructed image quality, and the method described in \ref{DynamicBlockOverview} provides the best image after embedding quality.
+The method described in \ref{differenceExpansionOverview} provides decent quality of the image after embedding as well as the image after reconstruction.
 
 \hspace{0pt} \\
-All three methods thus provide good results and would serve as a good benchmark for comparing the method described later in this paper.
+All three methods thus provide good results and would serve as a good benchmark for comparing the method proposed in this paper.
 
@@
 \label{bpcsSteg}
-In order to be able to recover the image after it has been tampered with the image needs to be embedded into itself. 
+In order to be able to reconstruct the image after it has been tampered with the image needs to be embedded into itself. 
 For this embedding the proposed method used BPCS Steganography \cite{beaullieubpcs}.
@@
   \item Divide the image into bit planes
-  \item Divide the bit planes into 8x8 blocks
+  \item Divide the bit planes into 8x8 pixel blocks
   \item Calculate the complexity for each block
-  \item Divide the image content reference to be embedded into similar binary 8x8 blocks
+  \item Divide the image reference content to be embedded into similar binary 8x8 blocks
   \item Calculate the complexity for each image reference block and conjugate if not complex enough
-  \item for each image block that is complex enough, replace that block with the next image reference block
+  \item for each image block that is complex enough, replace that block with the next image reference content block
   \item Convert the blocks back to binary representation
@@
 \end{enumerate}
-The proposed method works with colour images which means that for each pixel there is a red, green and blue value. This means that each block effectively store 3 bits for each pixel.
+The proposed method works with colour images which means that for each pixel there is a red, green and blue value. This means that each block effectively stores 3 bits for each pixel.
 
@@
 \hspace{0pt} \\
-As a solution to this problem each block used for embedding is treated as a separate embedding entity.
+As a solution to this problem each bit plane block used for embedding is treated as a separate embedding entity.
 There is thus no overlap between two different blocks used for embedding.
-The image reference is first process using the method explained later in this section.
-Each block has 12 pixels (with a bit depth of 16 bits) of the reference image embedded into it.
+The image reference content is first processed using the method explained later in this section.
+Each block has 12 pixels (with a bit depth of 16 bits) of the image reference content embedded into it.
 An embedding map containing the location of the first pixel to be embedded in the block is also created.
-Since the reference image pixels are embedded in order it is only necessary to know the location of the first pixel.
-This embedding map is then embedded into the LSB layer of that specific 8x8 block of pixels 
+Since the individual image reference content pixels are embedded in order it is only necessary to know the location of the first pixel.
+This embedding map is then embedded into the LSB (Least significant bit) layer of that specific 8x8 block of pixels 
 This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
-This serves to give random access to the embedded content which is an essential property of self embedding as defined by (Korus et al. \cite{korus2013efficient})
+This serves to give random access to the embedded content which is an essential property of self embedding as defined by (Korus et al. \cite{korus2013efficient}).
+This is essential in order for the reconstruction process to function properly.
 
@@
 \label{ImageCompression}
-The image that is embedded into the cover image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
+The image reference content that is embedded into the original image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
 The proposed method however does not utilize compression as it is beyond the scope of this paper.
@@
 The image's size is also reduced according to the space available for embedding.
-When extracting the image reference data again the image is scaled up to it's original size of 512x512 pixels before restoration
+When extracting the image reference content again the assembled image reference content is scaled up to it's original size of 512x512 pixels before completing the reconstruction.
+This is done to ensure that the pixels contained in the image reference content matches up (location wise) with the pixels in the original image.
 
 \paragraph{Block Spread}
-It is very important how the embedded content is spread across the image because this affects the tamper rate
+It is very important how the image reference content is spread across the image because this affects the tamper rate
 \hspace{0pt} \\
-\cite{korus2013efficient} Has found that it is important that the image reference content should be uniformly distributed across the cover image and that each part of the cover image should contain equal information about the image reference content.
-Due to the fact that the proposed method uses an adaptive embedding algorithm it is not possible for each part of the cover image to contain equal information about the image content reference.
+\cite{korus2013efficient} Has found that it is important that the image reference content should be uniformly distributed across the image during embedding and that each part of the image after should contain equal information about the image reference content.
+Due to the fact that the proposed method uses an adaptive embedding algorithm it is not possible for each part of the image after embedding to contain equal information about the image reference content.
 The proposed method does however distribute the embedded image reference content evenly among the blocks that were identified as suitable for embedding.
@@
 The created list is then reversed before embedding.
-Reversing the list means that the image reference content that contains the bottom right part of the original image will now be embedded into the top left part of the cover image.
-This creates an effect where the embedded reference content is far away from the content that it is referencing.
-This is important because if a piece of the cover image is destroyed it would not be able to recover it if that destroyed piece's reference content was destroyed with it.
+Reversing the list means that each corner of the image in the image reference content is embedded into the opposing corner diagonally in the original image.
+For example image reference content that contains the bottom right part of the original image will now be embedded into the top left part of the original image during embedding.
+
+This creates an effect where the embedded image reference content is far away from the content that it is referencing.
+This is important because if a piece of the image after embedding is destroyed it would not be able to reconstruct itself if that destroyed piece's reference content was destroyed with it.
+
+\hspace{0pt} \\
+An attempt was initially made to embed the image reference content blocks randomly into the original image.
+This process however produced a much lower tamper rate due to the fact that the image reference content was often embedded very close to the original image content that it was referencing.
+The result was a lowered tamper rate.
+The proposed method thus rather used the more successful method describe above.
 
 \paragraph{Conjugation}
-If a image content reference block is found to not be complex enough that block needs to be conjugated before embedding.
-This is important because if a block is not complex enough it cannot be detected when extracting and it may cause visual distortions to the image since it is replacing a complex block.
+If an image reference content block is found to not be complex enough that block needs to be conjugated before embedding.
+This is important because if a block is not complex enough it cannot be detected when extracting and it may cause visual distortions to the image since it is replacing a complex block in the original image.
 
@@
 The block complexity is calculated by using a border complexity method. \cite{beaullieubpcs}
-That is for each binary bit that has an adjacent binary bit that is different than it the border count is increased. 
-The final border count is then divided with the theoretical maximum border count, which would be the same a the border count for a grid with a checkerboard pattern.
+That is for each binary bit that has an adjacent binary bit that is different than itself the border count is increased. 
+The final border count is then divided with the theoretical maximum border count, which would be the border count for a grid of the same size with a checkerboard pattern.
 
@@
 
-\subsection{Extraction and Restoration}
+\subsection{Extraction and Reconstruction}
 \label{extractRestore}
@@
 
-\subsubsection{Image restoration}
+\subsubsection{Image reconstruction}
 \hspace{0pt} \\

### 2014-08-27 Paper/main.tex
Did a proof read and made terms more consistent

@@
 An initial attempt was made to apply the method proposed in \cite{tian2002wavelet}.
-This method is a reversible fragile watermark which means that the watermark can be removed to restore the original content bit by bit before watermarking if the image was found to be authentic.
+This method is a reversible fragile watermark which means that the watermark can be removed, during the extraction and reconstruction process, to restore the original content bit by bit to what it was before watermarking, if the image was found to be authentic.
 
 \hspace{0pt} \\
-The method needed to be adapted to authenticate the image on a block level, the image is divided into 8x8 blocks.
+The method needed to be adapted to authenticate the image on a block level, because the image is divided into 8x8 blocks.
 The method requires compression of bit streams in order to embed the watermark and to be able to extract the watermark again.
+These bit streams are used to store the embedding locations of watermark.
 The bit streams are rather small in the proposed method because they are only applicable to a specific 8x8 pixel block. 
-This results in the fact that there is not always enough redundancy to be able to compress the bit streams enough for embedding.
+This is because each block is treated as a separate embedding entity.
+This results in the fact that there is not always enough redundancy to be able to compress the bit streams for embedding.
 
@@
 \hspace{0pt} \\
-The fragile watermark used in the proposed method embeds a calculated hash into the image that is used to authenticate the content when the image is processed on the receiving end.
+The fragile watermark used in the proposed method embeds a calculated hash into the image that is used to authenticate the content when the image is reconstructed on the receiving end.
 
 \hspace{0pt} \\
-For each of the 8x8 pixel section in the image a hash is calculated by combining the binary of each of the 7 Most significant bit layers of that section.
-This binary stream is then used as the input to the SHA-256 hash function the output is a 256 bit hash string for that image block.
+For each of the 8x8 pixel section in the image after embedding a hash is calculated by combining the binary of each of the 7 Most significant bit planes of that section.
+This binary hash stream is then used as the input to the SHA-256 hash function.
+The output is a 256 bit hash string for that image section.
 This hash string is then truncated to a length of 57 bits.
@@
 The pigeonhole principle states that since the input for the hash function (k) is greater than the amount of unique outputs of the hash function (y) there will be duplicate hash values produced.
-However since the generated hash values are calculated from each section and then compared to the bits stored in the LSB layer of that section it is highly unlikely, but not impossible, that a false positive for tampering will occur.
+However since the generated hash values are calculated from the 7 MSB planes of each section and then compared to the bits stored in the LSB plane of that section it is highly unlikely, but not impossible, that a false positive for tampering will occur.
 Extensive testing was conducted on a number of images and no situation was found where such a collision occurred within normal operation.
-However should this case arise, the proposed method would simple restore that section as well.
-Thus not having a major impact on the final result of the restoration.
+However should this case arise, the proposed method would simply restore that section as well.
+Thus not having a major impact on the final result of the reconstruction.
 
@@
 The conjugation map is appended to the truncated hash string to create a binary string of 192 bits.
-These 192 bits are finally embedded into the least significant bit plane of that specific section of the cover image effectively replacing all the bits in that bit plane with the generated bit stream.
+These 192 bits are finally embedded into the LSB plane of that specific section of the image after embedding effectively replacing all the bits in that bit plane with the generated bit stream.
 
@@
 \subsubsection{Image authentication}
-The first step for the image extraction and restoration process is to determine which, if any, parts of the image has been tampered with.
+The first step for the image extraction and reconstruction process is to determine which, if any, parts of the image after embedding has been tampered with.
 This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
-for each block (block refers here to 8x8 pixel blocks, thus a block here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
-The embedded hash is then extracted from the Least significant bit plane of that block.
-The extracted hash is then compared with the calculated hash and if they match the block is authentic.
+for each section (section refers here to 8x8 pixel section, thus a section here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
+The embedded hash is then extracted from the LSB plane of that block.
+The extracted hash is then compared with the calculated hash and if they match the section is authentic.
+If they do not match then that section has been tampered with.
 
@@
 \hspace{0pt} \\
-For each authentic block the 7 most significant bit planes have their complexity calculated.
+For each authentic block the 7 MSB planes have their complexity calculated.
 If a bit plane block is found to be complex enough it is assumed that there is image information embedded into it.
-The embedded conjugation map is extracted at this point and if it is found that any of the complex enough bit planes were conjugated the conjugation algorithm is applied again to reverse the conjugation.
+The embedded conjugation map is extracted at this point and if it is found that any of the complex enough bit plane blocks were conjugated the conjugation algorithm is applied again to reverse the conjugation.
 
 \hspace{0pt} \\
-The embedded image content is extracted at this point from the processed bit planes and the embedded image is reconstructed.
+The embedded image content is extracted at this point from the processed bit plane blocks and the embedded image is reconstructed.
 In order to know the location of the extracted pixels the embedding map that was embedded into the LSB bit plane of that image section is consulted \ref{bpcsSteg}.
 The reconstructed image is then scaled up back to it's original size of 512x512 pixels.
-The reconstructed image is then also split into pixel blocks.
-The original pixel blocks now get iterated and each block that was found not to be authentic is replaced by the corresponding reconstructed pixel block.
+The reconstructed image is then also split into bit plane blocks.
+This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
+The bit plane blocks generated from the image after embedding now get iterated and each block that was found not to be authentic is replaced by the corresponding reconstructed bit plane block.
 
 \hspace{0pt} \\
-This process restores the tampered areas of the image if their matching pixel blocks could be extracted from the image.
+This process restores the tampered areas of the image if their matching bit plane blocks could be extracted from the image.
 That is if the embedded blocks were not destroyed in the image modification.
@@
 \section{Results} 
-In testing the proposed method a simple experiment was set up in which the image was processed using the embedding process described in \ref{embedding}.
-The results of that process can be seen in the following two images, showing the original Image and the image after the embedding process.
+In testing the proposed method a simple experiment was set up in which the original image was processed using the embedding process described in \ref{embedding}.
+The results of that process can be seen in figure \ref{fig:lenaEmbedOnceEmbedding}, showing the original image and the image after the embedding process.
 Note that in this case the Image Reference content was only embedded once
@@
 \cite{wang2002image}
-After the image after embedding was generated the PSNR of the embedded image in relation to the original image was calculated.
+After the image after embedding was generated the PSNR of the image after embedding in relation to the original image was calculated.
 In this instance the PSNR after embedding was: 34.92dB
@@
 \hspace{0pt} \\
-The next step in the experiment conducted was to modify the Image after embedding (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
-After the Image was modified it was processed using the method described in \ref{extractRestore}.
-The results of this process can be seen in the following two images, showing the Image after Tampering and the Image after Restoration.
+The next step in the experiment conducted was to modify the image after embedding (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+After the image was modified it was reconstructed using the method described in \ref{extractRestore}.
+The results of this reconstruction can be seen in figure \ref{fig:lenaEmbedOnceRestoration}, showing the image after tampering and the image after reconstruction.
 
@@
 \hspace{0pt} \\
-After the image (shown in figure \ref{fig:lenaEmbedOnceRestoration}) was restored the PSNR of the Image After Restoration was calculated in relation to the Original Image (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+After the image (shown in figure \ref{fig:lenaEmbedOnceRestoration}) was reconstructed the PSNR of the image after reconstruction (figure \ref{fig:lenaEmbedOnceRestoration}) was calculated in relation to the Original Image (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
 In this instance the PSNR after restoration was: 34.89dB.
@@
 \hspace{0pt} \\
-It was found in the experimentation process that if the Image reference content is only embedded once that the quality of the Image after embedding as well as the quality of the Image after restoration was relatively high.
+It was found in the experimentation process that if the image reference content is only embedded once into the original image that the quality of the Image after embedding as well as the quality of the image after reconstruction was relatively high.
 It was however found that the tamper rate possible was quite low at \textless 3\%.
-To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the Image reference content now being embedded twice.
-The results can be seen below
+To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the Image reference content was now being embedded twice.
+The results can be seen in figure \ref{fig:lenaEmbedTwiceEmbedding} and figure \ref{fig:lenaEmbedTwiceRestoration}
 
@@
 \hspace{0pt} \\
-In order to embed the Image reference content twice the content needs to be half the size that is used when embedding once.
-This reduces the quality of the Image after Restoration from the previous 34.89dB to 32.52 dB.
+In order to embed the image reference content twice the image reference content needs to be half the size that is used when embedding once.
+This reduces the quality of the image after reconstruction from the previous 34.89dB to 32.52 dB.
 The tamper rate however is now increased from \textless 3\% to \textless 35\%
@@
 This experiment was also completed on the following image.
-First Embedding the Image reference content once:
+First Embedding the Image reference content once (figure \ref{fig:treeEmbedOnceEmbedding} and figure \ref{fig:treeEmbedOnceRestoration}):
 
@@
 \hspace{0pt} \\
-The PSNR of the Image after embedding (show in figure \ref{fig:treeEmbedOnceEmbedding}) was 27.94dB.
+The PSNR of the image after embedding (show in figure \ref{fig:treeEmbedOnceEmbedding}) was 27.94dB.
 
@@
 \hspace{0pt} \\
-The PSNR of the Image after restoration (show in figure \ref{fig:treeEmbedOnceRestoration}) was 27.72dB.
-The tamper rate, as was the case with the lena image, was also \textless 3\%.
-The experiment was also conducted by embedding the Image reference content twice.
-As is shown below.
+The PSNR of the image after reconstruction (show in figure \ref{fig:treeEmbedOnceRestoration}) was 27.72dB.
+The tamper rate, as was the case with the first image (figure \ref{fig:lenaEmbedOnceRestoration}), was also \textless 3\%.
+The experiment was also conducted by embedding the Image reference content twice (figure \ref{fig:treeEmbedTwiceEmbedding} and figure \ref{fig:treeEmbedTwiceRestoration}).
 
@@
 \hspace{0pt} \\
-The PSNR of the Image after embedding (show in figure \ref{fig:treeEmbedTwiceEmbedding}) was 27.93dB.
+The PSNR of the image after embedding (show in figure \ref{fig:treeEmbedTwiceEmbedding}) was 27.93dB.
 
@@
 \hspace{0pt} \\
-The PSNR of the Image after restoration (show in figure \ref{fig:treeEmbedOnceRestoration}) was 26.05dB.
-The tamper rate, as was the case with the lena image, was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
+The PSNR of the image after reconstruction (show in figure \ref{fig:treeEmbedOnceRestoration}) was 26.05dB.
+The tamper rate, as was the case with the first image image (figure \ref{fig:lenaEmbedTwiceRestoration}), was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
 
 \hspace{0pt} \\
-The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced
+The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced.
+
+As an experimental control the results from the experiment in the proposed method will be compared to other current methods for images with self recovering capabilities.
+This is discussed further in  section \ref{interpretation}.
 
 \section{Interpretation of results}
+\label{interpretation}
 The proposed method for self-recovering images using the BPCS Steg embedding algorithm described in the preceding sections was shown to be effective.
-According to Appendix B in \cite{korus2013efficient} the proposed method achieved Average to High quality restoration in the case of figure \ref{fig:lenaEmbedTwiceRestoration} and figure \ref{fig:lenaEmbedOnceRestoration} respectively.
-The proposed method achieved Low quality restoration in the case of figure \ref{fig:treeEmbedOnceRestoration} and figure \ref{fig:treeEmbedTwiceRestoration} according to \cite{korus2013efficient}.
+According to Appendix B in \cite{korus2013efficient} the proposed method achieved Average to High quality reconstruction in the case of figure \ref{fig:lenaEmbedTwiceRestoration} and figure \ref{fig:lenaEmbedOnceRestoration} respectively.
+The proposed method achieved Low quality reconstruction in the case of figure \ref{fig:treeEmbedOnceRestoration} and figure \ref{fig:treeEmbedTwiceRestoration} according to \cite{korus2013efficient}.
 
@@
 With that in mind the image from figures \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} was specifically chosen because it is well used in the literature and can serve to compare to proposed method to other methods available in the literature.
-Such comparisons follow below
+Such comparisons follow below.
 
@@
 Compared to the method described in \ref{differenceExpansionOverview} the proposed method performs in a similar manner.
-The PSNR values achieved are worse than that of the method in \ref{differenceExpansionOverview} but the difference is around 1-2dB and is thus almost negligible.
+The PSNR values achieved are worse than that of the method in \ref{differenceExpansionOverview} but the difference is around 1-2dB and is thus almost not noticeable to the human eye.
 It should also be mentioned that the proposed method uses no compression on the image reference content, similar to the method in \ref{differenceExpansionOverview}.
@@
 \hspace{0pt} \\
-It was found during experimenting that Image quality can vary greatly among different image using the proposed method.
-This can be attributed to the fact that an adaptive embedding method is used and the embedding thus differs depending on the chosen cover image.
+It was found during experimentation that image quality can vary greatly among different image using the proposed method.
+This can be attributed to the fact that an adaptive embedding method is used and where the image reference content is embedded thus differs depending on the chosen original image.
+
+\hspace{0pt} \\
 The embedding rate and effects of the embedding rate seemed consistent across the different images used.
+The embedding rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the one described in \ref{DynamicBlockOverview}.
+However it was found that if the image reference content is embedded twice into the original image that the tamper rate compares equally to that of methods such as the one described in \ref{DynamicBlockOverview}.
 
@@
 The proposed method was shown to provide good quality as well as a good tamper rate.
-It was also shown that the quality of the cover image after embedding the image reference content and the image quality after restoration differs depending on the cover image chosen.
+It was also shown that the quality of the image after embedding the image reference content and the image quality after reconstruction differs depending on the cover image chosen.
 This was attributed to the adaptive embedding algorithm used.
-It was also mentioned that no compression was used on the image reference content that was embedded into the cover image.
-If compression is used it may result in higher quality of the image after restoration as well as the cover image due to fewer modifications that will be made during embedding.
+It was also mentioned that no compression was used on the image reference content that was embedded into the original image.
+If compression is used it may result in higher quality of the image after reconstruction as well as the image after embedding due to fewer modifications that will be made during embedding.
 

### 2014-08-27 Paper/main.tex
Added a description of terms

@@
 \tableofcontents
+\section{Terms used}
+This paper makes use of several terms and acronyms.
+This section serves to make the meaning of those terms clear.
+
+\begin{itemize}
+  \item Original Image: This refers to the original image without any modifications.
+  \item Image after embedding: This refers to the the original image after the embedding process has been applied.
+  \item Image after reconstruction: This refers to the reconstructed version of the original image that was obtained by applying the reconstruction process to the image after embedding.
+  \item LSB: This refers to the least significant bit in a binary string.
+  \item MSB: This refers to the most significant bit/bits in a binary string.
+  \item Section, Image section, Pixel section: This refers to a section 8x8 pixels in an image.
+  \item Block: This refers to an individual bit plane of a specific section of the image. There are 8 such blocks in each section since each pixel is represented by 8 bits for each colour. 
+\end{itemize}
 

### 2014-10-06 Paper/main.tex
First draft
Chapter 1 changes applied as well as stub sections added

@@
 \usepackage{mathtools}
+\usepackage{setspace}
+\setstretch{1.0}
 
@@
 
-\iffalse
+\tableofcontents
+\section{Introduction}
 
-\fi
-\tableofcontents
-\section{Terms used}
+\subsection{Introduction}
+This paper proposes a novel method for self-recovering images.
+
+\hspace{0pt} \\
+Self-recovering images: Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. 
+This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that the image was damaged.
+
+\hspace{0pt} \\
+Current self-recovering image techniques generally have poor quality restoration capabilities, damage the original image greatly or does not allow a large amount of the original image to be damaged before recovery is no longer possible.
+The proposed method will focus on improving the quality of self-recovering images.
+
+\subsection{Problem statement}
+The proposed method attempts to achieve the following
+\begin{itemize}
+	\item The proposed method should achieve a high quality image after the self-embedding process as well as after the restoration process with a reasonable tamper rate(compared to currently available methods)
+	\item There should not be clear visual evidence that the image has been modified after embedding as well as after restoration and the image should still carry it's original semantic meaning
+\end{itemize}
+
+\subsection{Research methodology}
+Firstly a literature review was conducted to determine the currently available methods for self-recovering images. 
+After a shortcoming was identified the proposed method was designed and then implemented in the form of a Java software application in order to attempt to improve on the identified shortcoming. 
+The results of the proposed method were then compared to the results of other relevant self-recovering image methods.
+
+\subsection{Terminology}
 This paper makes use of several terms and acronyms.
@@
   \item Original Image: This refers to the original image without any modifications.
+  \item Embedding: Embedding in the context of this paper refers to the process of storing digital information in an image's content in such a way that the original image is still distinguishable.
   \item Image after embedding: This refers to the the original image after the embedding process has been applied.
@@
   \item MSB: This refers to the most significant bit/bits in a binary string.
-  \item Section, Image section, Pixel section: This refers to a section 8x8 pixels in an image.
+  \item Section, Image section, Pixel section: This refers to a section of 8x8 pixels in an image.
+  \item Bit plane: A bit plane is a 8x8 grid representation of a specific bit value's for a specific pixel section.
+Each pixel has 24 bits which in total represents each colour, 8 bits per colour.
+these bits are the 8 binary bits that represent the numerical value of the colour.
+These 8 bits are separated from each other and are each stored in a 8x8 grid in the same location as that of the pixel in the pixel section.
+This process is repeated for each pixel in the pixel section and the result is 8, 8x8 grids of binary numbers.
+Each one of these 8 grids represent a single bit plane.
   \item Block: This refers to an individual bit plane of a specific section of the image. There are 8 such blocks in each section since each pixel is represented by 8 bits for each colour.
+  \item BPCS Steganography: Bit-Plane Complexity Segmentation Steganography
 \end{itemize}
 
-\section{Introduction}
+\subsection{Conclusion}
+This chapter discussed the purpose behind self-recovering images as well as the aim of this research and the proposed method. 
+The research methodology followed was described. A list of terminologies used in this paper was also given.
+The next chapter will give a more detailed overview of all the components that make up self-recovering images.
+
+\section{Self-recovering images}
+
+\subsection{Introduction}
+//TODO
 
@@
 
+\subsection{Conclusion}
+//TODO
+
 \section{Current self recovering image schemes and algorithms}
+
+\subsection{Introduction}
+//TODO
 
@@
 
+\subsection{Conclusion}
+//TODO
+
 \section{Implementation}
 \label{Implementation}
+\subsection{Introduction}
+//TODO
 
@@
 
+\subsection{Conclusion}
+//TODO
+
 \section{Results} 
+\subsection{Introduction}
+//TODO
+
 In testing the proposed method a simple experiment was set up in which the original image was processed using the embedding process described in \ref{embedding}.
@@
 This is discussed further in  section \ref{interpretation}.
+\subsection{Conclusion}
+//TODO
 
 \section{Interpretation of results}
+\subsection{Introduction}
+//TODO
+
 \label{interpretation}
@@
 
+\subsection{Conclusion}
+//TODO
+
 \section{Conclusion}

### 2014-10-06 Paper/main.tex
First refactoring of chapter 2

@@
 //TODO
+Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. 
+This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that the image was damaged.
 
-This section gives a brief description of the concepts used in this report.
-The reasoning behind the proposed method will also be explained in \ref{introQualityIncrease} and \ref{introHighCap}.
-This will serve to to show the applicability of the proposed method as well as the shortcomings it attempts to address.
+\hspace{0pt} \\
+In order to understand the self-recovering system proposed in this dissertation, one has to understand the underlying technologies.
+This chapter will look at image steganography in more detail in section \ref{introSteganography} and at watermarking in section \ref{introFragWatermarking}  Self-embedding and recovery will be discussed in section \ref{introSelfEmbedRecovery} as well as the inherent quality trade off in section \ref{introQualityTrade} with a conclusion in section \ref{introConclusion}
 
-\subsection{Overview}
-Self recovering images (described in \ref{introSelfEmbedRecovery}) poses an interesting problem.
-There is an inherent trade-off (described in \ref{introQualityTrade}) between the quality of the image after embedding and the quality of the image after recovery.
+Self recovering images poses an interesting problem.
+\hspace{0pt} \\
+//TODO insert formal definition here
+\hspace{0pt} \\
+There is an inherent trade-off between the quality of the image after embedding and the quality of the image after recovery.
+
+\iffalse
+//TODO possibly remove this
 This report proposes a method in which a high capacity image steganography embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.
+\fi
 
@@
 \subsection{Conclusion}
+\label{introConclusion}
 //TODO

### 2014-10-07 Paper/main.tex
Completed most of ch2 changes only def's missing and one thing to move

@@
 \subsection{Introduction}
-//TODO
 Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. 
@@
 In order to understand the self-recovering system proposed in this dissertation, one has to understand the underlying technologies.
-This chapter will look at image steganography in more detail in section \ref{introSteganography} and at watermarking in section \ref{introFragWatermarking}  Self-embedding and recovery will be discussed in section \ref{introSelfEmbedRecovery} as well as the inherent quality trade off in section \ref{introQualityTrade} with a conclusion in section \ref{introConclusion}
+This chapter will look at image steganography in more detail in section \ref{introSteganography} and at watermarking in section \ref{introFragWatermarking}.
+Self-embedding and recovery will be discussed in section \ref{introSelfEmbedRecovery} with a conclusion in section \ref{introConclusion}
 
@@
 \hspace{0pt} \\
-//TODO insert formal definition here
+//TODO <add formal definition here>
 \hspace{0pt} \\
 There is an inherent trade-off between the quality of the image after embedding and the quality of the image after recovery.
-
-\iffalse
-//TODO possibly remove this
-This report proposes a method in which a high capacity image steganography embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.
-\fi
 
@@
 
+\hspace{0pt} \\
+The proposed method uses steganography to embed the information into the image in a way that is not easily visibly detectable by a human observer.
+A successful stegnographic method has certain characteristics:
+\begin{itemize}
+	\item Invisibility: How easy it is to detect that information has been embedded using steganography.
+	\item Robustness: How much of the image that is embedded into can be modified without compromising the embedded information.
+	\item Capacity: The maximal number of bits that can be embedded without introducing statistically detectable artifacts \cite{fridrich2009steganography}.
+It should also be added that the embedding must also not be visually detectable.
+\end{itemize}
+Least significant bit embedding (LSB) is a stegnographic method that can be used to embed information. 
+LSB works by replacing the least significant bit (or n least significant bits) of an image colour value with the binary bits from a message.
+The least significant bit of a colour value is the binary bit/s that carry the least value.
+
+\hspace{0pt} \\
+BPCS Steganography is another stegnographic embedding method \cite{beaullieubpcs}.
+
+\hspace{0pt} \\
+This method works with the following steps:
+\begin{enumerate}
+  \item Get the binary representation of the image
+  \item Convert the binary representation into Gray code
+  \item Divide the image into bit planes
+  \item Divide the bit planes into 8x8 pixel blocks
+  \item Calculate the complexity for each block
+  \item Divide the image reference content to be embedded into similar binary 8x8 blocks
+  \item Calculate the complexity for each image reference block and conjugate if not complex enough
+  \item for each image block that is complex enough, replace that block with the next image reference content block
+  \item Convert the blocks back to binary representation
+  \item reconstruct the image from the processed blocks 
+\end{enumerate}
+
+\hspace{0pt} \\
+The BPCS algorithm is a high capacity embedding algorithm. The goal of the BPCS algorithm is thus to embed as much data as possible into a cover image without detection \cite{beaullieubpcs}.
+This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this paper.
+The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding (similar to \ref{DynamicBlockOverview}).
+BPCS steg differs however in the fact that the blocks can be conjugated in a checker board pattern to increase complexity and decrease detectability if needs be.
+BPCS steg also differs in the way in which embedding takes place.
+Instead of always embedding into the 3-LSB planes as in \ref{DynamicBlockOverview}.
+Bit planes are dynamically allocated for embedding.
+One section may thus only embed into one bit plane while another may use all 7 available bit planes.
+
 \subsection{Fragile Watermarking}
+//TODO <add formal definition here> 
 \label{introFragWatermarking}
@@
 This is a necessary component in self recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so what parts of the image was modified.
+
+\iffalse 
+	//TODO this needs to move to a different section
 	The proposed method will use this information to determine which parts of the image should be recovered from the image reference content.
 	A fragile watermark is used for this purpose. 
+\fi
 
@@
 
-\subsection{Quality Trade-off}
-\label{introQualityTrade}
+\hspace{0pt} \\
 There is an inherent quality trade-off present within self embedding schemes.
 The trade-off exists between the image after embedding and the image after reconstruction.
-If an embedding algorith such as LSB(Least significan bit) embedding is used (as in \ref{ErasureChannelOverview}) the actual bit values of the original image are overwritten.
+If an embedding algorith such as LSB(Least significan bit) embedding is used the actual bit values of the original image are overwritten.
 Naturally the more bit values are overwritten the more noise is introduced into the image.
@@
 
-\subsubsection{Increasing quality with capacity}
-\label{introQualityIncrease}
+\hspace{0pt} \\
 It might be possible to increase the quality of the image after reconstruction while still keeping the quality after embedding high.
-It is proposed that applying an embedding algorithm designed for high capacity while retaining quality (as discussed in \ref{introHighCap}) to the problem of self recovering could possibly increase the quality of the image after embedding as well as after reconstruction.
-This is because such an algorithm should provide higher embedding capacity while producing less noise in the image.
-
-\subsubsection{High capacity embedding algorithms}
-\label{introHighCap}
-The proposed method in this paper attempts to apply the algorithm for BPCS Steganography (Bit-Plane Complexity Segmentation Steganography) \cite{beaullieubpcs} to the problem of self recovering images, specifically to increase overall quality.
+By using a high capacity embedding algorithm the overall embedding capacity is increased and a higher quality restoration image can be embedded.
 
 \hspace{0pt} \\
-The goal of the BPCS algorithm is to embed as much data as possible into a cover image without detection \cite{beaullieubpcs}.
-This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this paper.
-The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding (similar to \ref{DynamicBlockOverview}).
-BPCS steg differs however in the fact that the blocks can be conjugated in a checker board pattern to increase complexity and decrease detectability if needs be.
-BPCS steg also differs in the way in which embedding takes place.
-Instead of always embedding into the 3-LSB planes as in \ref{DynamicBlockOverview}.
-Bit planes are dynamically allocated for embedding.
-One section may thus only embed into one bit plane while another may use all 7 available bit planes.
-
-\hspace{0pt} \\
+The proposed method in this paper attempts to apply the algorithm for BPCS Steganography
+to the problem of self recovering images, specifically to increase overall quality.
 The BPCS algorithm can achieve a very high capacity while still remaining undetectable through human perception.
-This makes the BPCS algorithm a possible good choice to increase the capacity of a self recovering image scheme and possible increase the quality through this process.
+This makes the BPCS algorithm a good choice to increase the capacity of a self recovering image scheme and possibly increase the quality through this process.
 
@@
 \label{introConclusion}
-//TODO
+This chapter gave important background information regarding staganography in general as well as two stegnographic embedding methods, LSB embedding and BPCS steganography in section \ref{introSteganography}.
+Fragile watermarking was discussed in section \ref{introFragWatermarking} as well as self embedding and recovery in section \ref{introSelfEmbedRecovery}.
+The next chapter will discuss related work in existing self embedding techniques.
 
@@
 
-\subsubsection{BPCS Steg}
-\label{bpcsSteg}
-In order to be able to reconstruct the image after it has been tampered with the image needs to be embedded into itself. 
-For this embedding the proposed method used BPCS Steganography \cite{beaullieubpcs}.
-
-\hspace{0pt} \\
-This method works with the following steps:
-\begin{enumerate}
-  \item Get the binary representation of the image
-  \item Convert the binary representation into Gray code
-  \item Divide the image into bit planes
-  \item Divide the bit planes into 8x8 pixel blocks
-  \item Calculate the complexity for each block
-  \item Divide the image reference content to be embedded into similar binary 8x8 blocks
-  \item Calculate the complexity for each image reference block and conjugate if not complex enough
-  \item for each image block that is complex enough, replace that block with the next image reference content block
-  \item Convert the blocks back to binary representation
-  \item reconstruct the image from the processed blocks 
-\end{enumerate}
 The proposed method works with colour images which means that for each pixel there is a red, green and blue value. This means that each block effectively stores 3 bits for each pixel.
 
-\hspace{0pt} \\
+\subsubsection{BPCS steganography} 
+\label{bpcsSteg}
+
 BPCS Steg has an inherent property that if any part of the image is modified the embedded message will be lost.

### 2014-10-08 Paper/main.tex
Notation of where to add changes and some more minor revisions

@@
 \iffalse 
-	//TODO this needs to move to a different section
+	//TODO this already covered in section \ref{impFragileWatermark}
 	The proposed method will use this information to determine which parts of the image should be recovered from the image reference content.
@@
 
-This section compares current Content reconstruction algorithms using self embedding.
+This section compares current content reconstruction algorithms using self embedding.
 This serves to give an overview of what is currently available and to possibly highlight shortcomings of the current algorithms.
@@
 It would also help highlight strengths and shortcomings in the proposed method.
-The methods analyzed were chosen because they all provide good quality images after embedding as well as good quality images after reconstructed.
-They also each offer an unique approach or aspect to the self recovering image problem and would thus provide a good overview of the different approaches that have already been tested.
+The methods analysed were chosen because they all provide good quality images after embedding as well as good quality images after reconstructed.
+They also each offer an unique approach or aspect to the self recovering image problem.
+
+\hspace{0pt} \\
+There are 3 methods tested.
+An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation \ref{DynamicBlockOverview}.
+A comparison between these 3 methods are provided in section \ref{litStudyCamparison}
 
 \subsection{Overview}
+//TODO <All the terms that have not been defined yet in the paper that will be used in this section should be defined here>
 
@@
 \label{ErasureChannelOverview}
-The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
-The method uses LSB embedding to embed the image reference content into the image itself.
-The method also uses a global spreading technique to spread the image reference content across the image.
-They also propose that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after reconstruction.
+The method proposed in \cite {korus2013efficient} uses an erasure channel
+//TODO <define erasure channel> 
+as a model for the content reconstruction problem.
+The method uses LSB embedding to embed the image reference content into the image itself and uses a global spreading technique to spread the image reference content across the image.
+The method also proposes that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after reconstruction.
 
 \hspace{0pt} \\
-The method proposed in \cite {korus2013efficient} achieves good quality images after embedding with a PSNR \textgreater 35dB. 
+The method proposed in \cite {korus2013efficient} achieves good quality images after embedding with a PSNR 
+//TODO <define PSNR and why is it important, this is possibly explained in another section> 
+\textgreater 35dB. 
 The method also achieves an image after reconstruction quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with tamper rates of 50\% and 33\% respectively.
 The method does not let the quality of the image after reconstruction deteriorate much if the tampering rate is increased up to a value of 50\%.
-They do however note that they can only achieve minimal reconstruction performance increases by decreasing the amount of information in the image reference content.
-By using only 50\% of the available capacity the maximal tampering rate increases form 50\% to 59\%.
+They do however note that they can only achieve a minimal increase in reconstruction performance by decreasing the amount of information in the image reference content.
+By using only 50\% of the available capacity the maximal 
+//TODO <define tampering rate earlier>
+ tampering rate increases form 50\% to 59\%.
 
@@
 This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered with before reconstruction ability starts to deteriorate.
-The security for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
+The security //TODO <define security> for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
 The authors did not do any statistical analysis on the image.
@@
 \label{differenceExpansionOverview}
-\cite {tian2003high} Proposed a method that uses difference expansion and generalized LSB embedding.
-Difference expansion works by exploiting the high redundancy that are present in images.
+Another method \cite {tian2003high} uses difference expansion and generalized LSB embedding.
+Difference expansion works by exploiting the high redundancy that are present in images 
+//TODO <Reference this, basically this reference \cite {tian2003high}>.
 With difference expansion the payload is embedded in the difference of pixel values. 
-For a pair of pixel values (x,y). \cite {tian2002reversible}
-It should however be noted that image quality reduces rapidly as the payload size is increased when using difference expansion. 
-The method uses these two techniques in combination to achieve a high embedding capacity while keeping distortion relatively low.
+For a pair of pixel values (x,y) \cite {tian2002reversible}. 
+It should however be noted that image quality reduces rapidly as the  
+//TODO <define payload size>
+payload size is increased when using difference expansion. 
+The method uses difference expansion and to achieve a high embedding capacity while keeping distortion relatively low.
 The method achieves a PSNR \textgreater 35dB after embedding.
-The method achieves an embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
+The method achieves an 
+//TODO <define embedding capacity>
+embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
 
@@
 \label{DynamicBlockOverview}
-(Qian et al) \cite{qian2011image} proposes a method for fragile watermarking with good image restoration capabilities.
+Qian et al \cite{qian2011image} proposes a method for fragile watermarking with good image restoration capabilities.
 The proposed method differs from the other methods mentioned in \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} due to the fact that the method does not embed the information into all blocks uniformly.
@@
 \hspace{0pt} \\
-The advantage of using this dynamic scheme is that there would be less visual distortion to the image after embedding. 
-This is because if the specific block is already very rough (very busy visually) the human eye would not notice small changes.
+The advantage of using this dynamic scheme is that there is visual distortion to the image after embedding. 
+This is because if the specific block is already very rough (very busy visually) the human eye does not notice small changes.
 If however the specific block is very smooth (very uniform visually) the human eye is more likely to notice small changes.
@@
 \hspace{0pt} \\
-The method proposed by (Qian et al) \cite{qian2011image} uses the 3 LSB bit planes to embed the needed information in.
+The method proposed by Qian et al \cite{qian2011image} uses 3 LSB bit planes
+\iffalse 
+	//TODO possibly define bit planes here although it is already defined in the terminology
+\fi 
+to embed the needed information in.
 The method achieves good results in experimentation with a image after embedding PSNR \textgreater 37dB as well as a image after reconstruction PSNR = 35dB.
@@
 \subsection{Comparison}
-Each of the methods described in \ref{DynamicBlockOverview}, \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} provide good quality images after embedding as well as good quality images after reconstruction.
+\label{litStudyCamparison}
+Each of the methods described in \ref{ErasureChannelOverview}, \ref{differenceExpansionOverview} and \ref{DynamicBlockOverview} provide good quality images after embedding as well as good quality images after reconstruction.
 There are however important differences.
@@
 \subsection{Conclusion}
-//TODO
+This chapter looked at currently available methods for self-recovering images.
+An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation \ref{DynamicBlockOverview}.
+A comparison between these methods was also provided in section \ref{litStudyCamparison}.
+The next chapter will discuss the implementation of the of the self-recovering image method proposed in this paper.
 
@@
 \section{Conclusion}
+\subsection{Introduction}
+//TODO
+
 The proposed method described used an adaptive embedding algorithm described in \ref{bpcsSteg}.
@@
 
+\subsection{Future work}
+//TODO
+
 \bibliography{main}

### 2014-10-08 Paper/main.tex
Section 3 edits and reference adds

@@
 \hspace{0pt} \\
+\iffalse
 	//TODO <add formal definition here>
+	Already mentioned the definition in the intro so I am not really sure what sort of definition to put here
+\fi
 \hspace{0pt} \\
@@
 \subsection{Fragile Watermarking}
-//TODO <add formal definition here> 
 \label{introFragWatermarking}
+Fragile watermarks are used to determine if a piece of watermarked digital content has been tampered, and distinguish tampered areas from non-tampered areas without referring to the original digital content \cite{liu2007image}.
+
+\hspace{0pt} \\
 Fragile watermarking is a variation of traditional watermarking where a watermark is embedded into an image such that subsequent alterations to the watermarked image can be detected with high probability \cite{lin1999review}.
@@
 This is a necessary component in self recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so what parts of the image was modified.
-
-\iffalse 
-	//TODO this already covered in section \ref{impFragileWatermark}
-	The proposed method will use this information to determine which parts of the image should be recovered from the image reference content.
-	A fragile watermark is used for this purpose. 
-\fi
 
@@
 \subsection{Introduction}
-//TODO
-
 This section compares current content reconstruction algorithms using self embedding.
@@
 \hspace{0pt} \\
-There are 3 methods tested.
+There are 3 current methods discussed in this section.
 An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation \ref{DynamicBlockOverview}.
@@
 \subsection{Overview}
-//TODO <All the terms that have not been defined yet in the paper that will be used in this section should be defined here>
+\begin{itemize}
+	\item Erasure channel: An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or the bit or it receives a message that the bit was not received, ie the bit was erased.
+	\item Peak signal to noise ratio (PSNR): PSNR is an expression for the ratio between the maximum possible value (power) of a signal and the power of distorting noise that affects the quality of its representation.
+PSNR is represented as a logarithmic decibel scale.
+In terms of images PSNR can objectively measure the amount of noised introduced into an image when compared with the original image.
+	As the mean squared error between the two images approaches 0 the PSNR approaches infinity. A higher PSNR value thus provides a higher quality image. 
+	A small PSNR value implies a high numerical difference between the two images \cite{hore2010image}.  
+	The quality measures mentioned in the 3 methods discussed were measured using the PSNR method.
+\cite{huynh2008scope} However determined that the validity of PSNR is limited to modifications within the same image.
+	It is thus not reliable to compare PSNR values between two different images.
+	\item Tampering rate: tampering rate is the percentage of image content that can be modified in the image after embedding, while still being able to reconstruct all the modified parts of that image.
+	If too much of the image is modified the embedded image content would be lost and reconstruction would not be possible.
+	\item Security: security refers to how easy it is to detect that information has been embedded into the image using either visual or statistical methods.
+Good security implies that it is difficult to detect and poor security implies that it is simple t detect.
+	\item Payload size: Payload size is defined as the amount of bits that is embedded in to an image using steganographic embedding techniques. 
+	\item Embedding capacity: embedding capacity is defined as the maximum amount of bits that can be embedded into an image using steganographic embedding techniques.
+\end{itemize}
+//TODO <All the terms that have not been defined yet in the paper that will be used in this section should be defined here, query if this is indeed a correct assumption>
 
@@
 \label{ErasureChannelOverview}
-The method proposed in \cite {korus2013efficient} uses an erasure channel
-//TODO <define erasure channel> 
-as a model for the content reconstruction problem.
+The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
 The method uses LSB embedding to embed the image reference content into the image itself and uses a global spreading technique to spread the image reference content across the image.
@@
 \hspace{0pt} \\
-The method proposed in \cite {korus2013efficient} achieves good quality images after embedding with a PSNR 
-//TODO <define PSNR and why is it important, this is possibly explained in another section> 
-\textgreater 35dB. 
+The method proposed in \cite {korus2013efficient} achieves good quality images after embedding with a PSNR \textgreater 35dB. 
 The method also achieves an image after reconstruction quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with tamper rates of 50\% and 33\% respectively.
@@
 They do however note that they can only achieve a minimal increase in reconstruction performance by decreasing the amount of information in the image reference content.
-By using only 50\% of the available capacity the maximal 
-//TODO <define tampering rate earlier>
- tampering rate increases form 50\% to 59\%.
+By using only 50\% of the available capacity the maximal tampering rate increases form 50\% to 59\%.
 
@@
 This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered with before reconstruction ability starts to deteriorate.
-The security //TODO <define security> for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
+The security for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
 The authors did not do any statistical analysis on the image.
@@
 Another method \cite {tian2003high} uses difference expansion and generalized LSB embedding.
-Difference expansion works by exploiting the high redundancy that are present in images 
-//TODO <Reference this, basically this reference \cite {tian2003high}>.
+Difference expansion works by exploiting the high redundancy that are present in images \cite {tian2002reversible}.
 With difference expansion the payload is embedded in the difference of pixel values. 
 For a pair of pixel values (x,y) \cite {tian2002reversible}. 
-It should however be noted that image quality reduces rapidly as the  
-//TODO <define payload size>
-payload size is increased when using difference expansion. 
+It should however be noted that image quality reduces rapidly as the payload size is increased when using difference expansion. 
 The method uses difference expansion and to achieve a high embedding capacity while keeping distortion relatively low.
 The method achieves a PSNR \textgreater 35dB after embedding.
-The method achieves an 
-//TODO <define embedding capacity>
-embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
+The method achieves an embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
 
@@
 \hspace{0pt} \\
-The quality measures mentioned were measured using the PSNR method. \cite{huynh2008scope} However determined that the validity of PSNR is limited to modifications within the same image.
-It is thus not reliable to compare PSNR values between two different images.
-With that in mind the image from figures \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} was specifically chosen because it is well used in the literature and can serve to compare to proposed method to other methods available in the literature.
+The image from figures \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} was specifically chosen for the experiment because it is well used in the literature and can serve to compare the proposed method to other methods available in the literature.
 Such comparisons follow below.

### 2014-10-09 Paper/main.tex
Section 4 changes and diagrams added along with other minor changes

@@
 \usepackage{setspace}
-\setstretch{1.0}
+\setstretch{1.5}
 
@@
 
-\noindent Abstract of this paper and what I wrote in it.
-This will give the reader a short overview of what they can expect to find in this paper.
+\noindent Abstract of this dissertation and what I wrote in it.
+This will give the reader a short overview of what they can expect to find in this dissertation.
 
@@
 \subsection{Introduction}
-This paper proposes a novel method for self-recovering images.
+This dissertation proposes a novel method for self-recovering images.
 
@@
 \subsection{Terminology}
-This paper makes use of several terms and acronyms.
+This dissertation makes use of several terms and acronyms.
 This section serves to make the meaning of those terms clear.
@@
   \item Original Image: This refers to the original image without any modifications.
-  \item Embedding: Embedding in the context of this paper refers to the process of storing digital information in an image's content in such a way that the original image is still distinguishable.
+  \item Embedding: Embedding in the context of this dissertation refers to the process of storing digital information in an image's content in such a way that the original image is still distinguishable.
   \item Image after embedding: This refers to the the original image after the embedding process has been applied.
@@
 This chapter discussed the purpose behind self-recovering images as well as the aim of this research and the proposed method. 
-The research methodology followed was described. A list of terminologies used in this paper was also given.
+The research methodology followed was described. A list of terminologies used in this dissertation was also given.
 The next chapter will give a more detailed overview of all the components that make up self-recovering images.
@@
 The BPCS algorithm is a high capacity embedding algorithm. The goal of the BPCS algorithm is thus to embed as much data as possible into a cover image without detection \cite{beaullieubpcs}.
-This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this paper.
+This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this dissertation.
 The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding (similar to \ref{DynamicBlockOverview}).
@@
 \hspace{0pt} \\
-The proposed method in this paper attempts to apply the algorithm for BPCS Steganography
+The proposed method in this dissertation attempts to apply the algorithm for BPCS steganography
 to the problem of self recovering images, specifically to increase overall quality.
@@
 \end{itemize}
-//TODO <All the terms that have not been defined yet in the paper that will be used in this section should be defined here, query if this is indeed a correct assumption>
+//TODO <All the terms that have not been defined yet in the dissertation that will be used in this section should be defined here, query if this is indeed a correct assumption>
 
@@
 \hspace{0pt} \\
-All three methods thus provide good results and would serve as a good benchmark for comparing the method proposed in this paper.
+All three methods thus provide good results and would serve as a good benchmark for comparing the method proposed in this dissertation.
 
@@
 A comparison between these methods was also provided in section \ref{litStudyCamparison}.
-The next chapter will discuss the implementation of the of the self-recovering image method proposed in this paper.
+This information will be used to determine the success of the self-recovering image method proposed in this dissertation by comparing the results from the proposed method with the results achieved by the methods discussed in this chapter.
+The next chapter will discuss the implementation of the of the self-recovering image method proposed in this dissertation.
 
-\section{Implementation}
+\section{Overview of the proposed system}
 \label{Implementation}
 \subsection{Introduction}
-//TODO
+This chapter discusses the details of the implementation for the self-recovering image method proposed in this dissertation.
+Embedding is discussed under which BPCS staganography and fragile watermarking will also be discussed.
+The extraction and restoration process will be discussed under which authentication and restoration will also be discussed.
+Diagrams are also provided to visualize the embedding as well as the extraction process
+
+\subsection{Overview of proposed system}
+\label{impOverview}
+The self-recovering method proposed in this dissertation uses BPCS steganography to increase the payload capacity of the cover image in order to be able to embed more reference content into the image without introducing visual distortion.
+In addition a fragile watermark was used to detect which parts of the image was damaged and thus needs to be reconstructed.
 
@@
 \label{embedding}
+In the embedding phase BPCS steganography and fragile watermarks were used.  How these two technologies were implemented are discussed in sections \ref{bpcsSteg} and \ref{impFragileWatermark}
 
-The proposed method works with colour images which means that for each pixel there is a red, green and blue value. This means that each block effectively stores 3 bits for each pixel.
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.6]{"EmbeddingProcess"}%
+} %
+\caption{The embedding process of the proposed self-recovering method}
+\label{fig:embeddingProcess}
+\end{figure}
 
@@
 This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
-This serves to give random access to the embedded content which is an essential property of self embedding as defined by (Korus et al. \cite{korus2013efficient}).
+This serves to give random access to the embedded content which is an essential property of self embedding as defined by Korus et al. \cite{korus2013efficient}.
 This is essential in order for the reconstruction process to function properly.
+
+\hspace{0pt} \\
+The proposed method works with colour images which means that for each pixel there is a red, green and blue value. This means that each block effectively stores 3 bits for each pixel.
 
@@
 The image reference content that is embedded into the original image cannot be embedded with perfect quality due to space restrictions caused by the embedding algorithm. 
-The proposed method however does not utilize compression as it is beyond the scope of this paper.
+The proposed method however does not utilize compression as it is beyond the scope of this dissertation.
 The proposed method rather reduces the bit rate of the image from 24 bits to 16 which reduces the size of each pixel by 6 bits.
@@
 \hspace{0pt} \\
-The block complexity is calculated by using a border complexity method. \cite{beaullieubpcs}
+The block complexity is calculated by using a border complexity method. \cite{beaullieubpcs}.
 That is for each binary bit that has an adjacent binary bit that is different than itself the border count is increased. 
@@
 This method of conjugation is a simple method that makes a block more complex while still allowing the original values of the block to be retrieved.
+A conjugation map is also created to indicate which blocks have been conjugated.
+This is needed since the receiver of the image would not be able to determine if a block has been conjugated or no without such a map.
 
@@
 \label{extractRestore}
+In the extraction and reconstruction process of the proposed method the image is first authenticated, this process is discussed in section \ref{extractionAuthentication}. 
+The image reference content is then extracted and the image is restored to an approximation of the original image before embedding, this process is discussed in section \ref{extractionReconstruction}.
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.6]{"ExtractionProcess"}%
+} %
+\caption{The extraction process of the proposed self-recovering method}
+\label{fig:extractionProcess}
+\end{figure}
+
 \subsubsection{Image authentication}
+\label{extractionAuthentication}
 The first step for the image extraction and reconstruction process is to determine which, if any, parts of the image after embedding has been tampered with.
@@
 \subsubsection{Image reconstruction}
-\hspace{0pt} \\
+\label{extractionReconstruction}
 For each authentic block the 7 MSB planes have their complexity calculated.
@@
 \subsection{Conclusion}
-//TODO
+This chapter discussed the proposed self-recovering system. An overview was given of the proposed method in section \ref{impOverview}. 
+Embedding was discussed in section \ref{embedding} under which BPCS steganography as well as fragile watermarking was also discussed in sections \ref{bpcsSteg} and \ref{impFragileWatermark}.
+The extraction process was discussed in section \ref{extractRestore} under which authentication and reconstruction was also discussed in sections \ref{extractionAuthentication} and \ref{extractionReconstruction}.
+Diagrams were also provided to visualize the embedding process in figure \ref{fig:embeddingProcess} and the extraction process in figure \ref{fig:extractionProcess}.
+The next chapter will discuss the experimental results achieved using the proposed method.
 
-\section{Results} 
+\section{Experimental Results} 
 \subsection{Introduction}
@@
 
+\subsection{Experiments conducted}
 In testing the proposed method a simple experiment was set up in which the original image was processed using the embedding process described in \ref{embedding}.
@@
 This is discussed further in  section \ref{interpretation}.
-\subsection{Conclusion}
-//TODO
 
-\section{Interpretation of results}
-\subsection{Introduction}
-//TODO
+\subsection{Interpretation of results}
 

### 2014-10-12 Paper/main.tex
Revisions, Future work, intro and conclusion(ch5)

@@
 
-Self recovering images poses an interesting problem.
 \hspace{0pt} \\
+Self-recovering images pose an interesting problem.
 \iffalse
@@
 \section{Current self recovering image schemes and algorithms}
-
+\label{currentSelfRecoveringSchemes}
 \subsection{Introduction}
@@
 \paragraph{Block Spread}
-It is very important how the image reference content is spread across the image because this affects the tamper rate
-\hspace{0pt} \\
+It is very important how the image reference content is spread across the image because this affects the tamper rate.
 \cite{korus2013efficient} Has found that it is important that the image reference content should be uniformly distributed across the image during embedding and that each part of the image after should contain equal information about the image reference content.
@@
 For example image reference content that contains the bottom right part of the original image will now be embedded into the top left part of the original image during embedding.
-
 This creates an effect where the embedded image reference content is far away from the content that it is referencing.
@@
 \subsection{Introduction}
-//TODO
+This chapter discusses the experiments conducted to test the proposed method. 
+The results of the conducted experiments are also interpreted and evaluated.
 
 \subsection{Experiments conducted}
+\label{experimentsConducted}
 In testing the proposed method a simple experiment was set up in which the original image was processed using the embedding process described in \ref{embedding}.
@@
 The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced.
-
 As an experimental control the results from the experiment in the proposed method will be compared to other current methods for images with self recovering capabilities.
@@
 \subsection{Interpretation of results}
-
 \label{interpretation}
@@
 \subsection{Conclusion}
-//TODO
+This chapter discussed the experiments conducted to test the proposed method in section \ref{experimentsConducted}.
+Two implementations of the proposed method were tested, embedding the image reference content once and twice into the original image.
+The results of the experiments were evaluated in section \ref{interpretation}.
+The results achieved using the proposed method were compared with the results achieved by other currently available self-recovering image methods discussed in section \ref{currentSelfRecoveringSchemes}.
 
@@
 \subsection{Future work}
-//TODO
+The method proposed in this dissertation focused on the implementation of the BPCS steganography algorithm as well as the implementation of the fragile watermark.
+The focus was to combine these methods in order to create a high quality self-recovering image scheme.
+It could however be possible to increase the quality of the proposed method even further if compression is used on the image reference content that is embedded into the original image.
+By compressing the image reference content it would be possible to embed a higher quality reference image into the original image without increasing the payload size.
+It would also be possible to reduce the amount embedding capacity used of the original image, due to a smaller amount of bits that need to be embedded, which would result in less of the original image being changed and thus less noise being introduced into the original image.
+This could possibly lead to increasing the overall quality of the proposed self-recovering image scheme.
 

### 2014-10-12 Paper/main.tex
Abstract

@@
 
-\noindent Abstract of this dissertation and what I wrote in it.
-This will give the reader a short overview of what they can expect to find in this dissertation.
+\noindent 
+Many current self-recovering image methods exist, however few of the current methods provide good quality images after embedding as well as after reconstruction.
+This is due to an inherent trade off between the amount of information that can be embedded into an image and the quality of the image after embedding.
+This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in the self-recovering image problem using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
+The proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared with some of the best currently available self-recovering image methods.
 

### 2014-10-12 Paper/main.tex
More general changes and abstract

@@
 \usepackage{setspace}
-\setstretch{1.5}
+\setstretch{1.0}
 
@@
   \item Section, Image section, Pixel section: This refers to a section of 8x8 pixels in an image.
-  \item Bit plane: A bit plane is a 8x8 grid representation of a specific bit value's for a specific pixel section.
+  \item Bit plane: A bit plane is a 8x8 grid representation of a specific bit value for a specific pixel section.
 Each pixel has 24 bits which in total represents each colour, 8 bits per colour.
@@
 Self-recovering images pose an interesting problem.
-\iffalse
-	//TODO <add formal definition here>
-	Already mentioned the definition in the intro so I am not really sure what sort of definition to put here
-\fi
-\hspace{0pt} \\
 There is an inherent trade-off between the quality of the image after embedding and the quality of the image after recovery.
@@
 This means that if modifications are made to the watermarked image it would be possible to detect that modifications were made as well as what parts of the image were modified.
-This is a necessary component in self recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so what parts of the image was modified.
+This is a necessary component in self-recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so what parts of the image was modified.
 
@@
 The proposed method in this dissertation attempts to apply the algorithm for BPCS steganography
-to the problem of self recovering images, specifically to increase overall quality.
+to the problem of self-recovering images, specifically to increase overall quality.
 The BPCS algorithm can achieve a very high capacity while still remaining undetectable through human perception.
-This makes the BPCS algorithm a good choice to increase the capacity of a self recovering image scheme and possibly increase the quality through this process.
+This makes the BPCS algorithm a good choice to increase the capacity of a self-recovering image scheme and possibly increase the quality through this process.
 
@@
 
-\section{Current self recovering image schemes and algorithms}
+\section{Current self-recovering image schemes and algorithms}
 \label{currentSelfRecoveringSchemes}
@@
 The methods analysed were chosen because they all provide good quality images after embedding as well as good quality images after reconstructed.
-They also each offer an unique approach or aspect to the self recovering image problem.
+They also each offer an unique approach or aspect to the self-recovering image problem.
 
-\hspace{0pt} \\
+\subsection{Overview}
 There are 3 current methods discussed in this section.
 An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation \ref{DynamicBlockOverview}.
-A comparison between these 3 methods are provided in section \ref{litStudyCamparison}
+A comparison between these 3 methods are provided in section \ref{litStudyCamparison}.
+These 3 methods will be discussed based on their PSNR, tapering rate, security, payload size and embedding capacity.
 
-\subsection{Overview}
 \begin{itemize}
@@
 \end{itemize}
-//TODO <All the terms that have not been defined yet in the dissertation that will be used in this section should be defined here, query if this is indeed a correct assumption>
 
@@
 The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced.
-As an experimental control the results from the experiment in the proposed method will be compared to other current methods for images with self recovering capabilities.
+As an experimental control the results from the experiment in the proposed method will be compared to other current methods for images with self-recovering capabilities.
 This is discussed further in  section \ref{interpretation}.

### 2014-10-19 Paper/main.tex
Conclusion update

@@
 \subsection{Problem statement}
+\label{problemStatement}
 The proposed method attempts to achieve the following
@@
 \subsection{Introduction}
-//TODO
+This chapter summarizes the findings of the proposed method and relates those findings back to the problem statement in section \ref{problemStatement}.
+Possible future work with regards to the proposed method is also discussed.
 
-The proposed method described used an adaptive embedding algorithm described in \ref{bpcsSteg}.
+\subsection{Summary}
+The proposed method described used the BPCS steganaography algorithm, which is an adaptive embedding algorithm described in \ref{bpcsSteg}, and applied the algorithm to the self-embedding problem.
 The proposed method was shown to provide good quality as well as a good tamper rate.
-It was also shown that the quality of the image after embedding the image reference content and the image quality after reconstruction differs depending on the cover image chosen.
-This was attributed to the adaptive embedding algorithm used.
+It was also shown that the quality of the image after embedding the image reference content as well as the image quality after reconstruction differs depending on the cover image chosen.
+This was attributed to the adaptive embedding algorithm used due to the fact that the embedding differs depending on the cover image.
 It was also mentioned that no compression was used on the image reference content that was embedded into the original image.
 If compression is used it may result in higher quality of the image after reconstruction as well as the image after embedding due to fewer modifications that will be made during embedding.
+
+\hspace{0pt} \\
+The proposed method achieved a high quality image after the self-embedding process as well as after the restoration process with reasonable tamper rate in one set of the images tested.
+The quality though is dependent on the image used.
+It would thus not achieve high quality with all images.
+The proposed method did not introduce clear visual evidence that the image has been modified after embedding as well as after restoration and the image did still carry it's original meaning.
+The proposed method thus achieved most of what it attempted to achieve with the only problem being that the quality is dependent on the image used.
 

### 2014-10-22 Paper/main.tex
Changes needed annotated up until section 3

@@
 This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in the self-recovering image problem using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
-The proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared with some of the best currently available self-recovering image methods.
+The proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the best currently available self-recovering image methods.
 
@@
 \subsection{Introduction}
-This dissertation proposes a novel method for self-recovering images.
+//TODO <//DONE// Rewrite in a more story like fashion, mention the why, what are the problems, steganography, fragile watermarks, self embedding etc>
+
+During communication images can by modified either intentionally or unintentionally.
+These modifications can be small changes that does not change the meaning of the image, or bigger changes, for example the removal of key aspects from the image.
+Various techniques exist for authenticating images of which self-recovering is one technique. 
+Self-recovering techniques attempt to preserve image content by embedding the image within itself to enable the reconstruction of the image if the image was tampered with.
+Self-recovering techniques use steganography, a technology used to embed information in digital media \cite{johnson1998exploring}, to hide the image content within the image.
+Self-recovering techniques also use fragile watermarks which is a technology commonly used in image authentication, to determine which areas of an image was tampered with.
 
 \hspace{0pt} \\
-Self-recovering images: Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. 
-This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that the image was damaged.
+Most self-recovering techniques have a tradeoff trade-off concerning the quality of the image after embedding and the quality of the image after recovery.
+If the one's quality is increased the other's quality will be reduced.
 
 \hspace{0pt} \\
-Current self-recovering image techniques generally have poor quality restoration capabilities, damage the original image greatly or does not allow a large amount of the original image to be damaged before recovery is no longer possible.
-The proposed method will focus on improving the quality of self-recovering images.
+This dissertation proposes using a high capacity steganography algorithm called Bit-plane Complexity Segmentation (BPCS) steganography to increase the amount of data that can be embedded in an image to attempt to increase the quality of the embedded image.
 
@@
 \label{problemStatement}
-The proposed method attempts to achieve the following
+The proposed method aims to answer the following questions
 \begin{itemize}
-	\item The proposed method should achieve a high quality image after the self-embedding process as well as after the restoration process with a reasonable tamper rate(compared to currently available methods)
-	\item There should not be clear visual evidence that the image has been modified after embedding as well as after restoration and the image should still carry it's original semantic meaning
+	\item Can a method be proposed that will achieve a high quality image after the self-embedding and restoration process as well as a reasonable tamper rate?
+How does such a system compare to currently available methods?
+	\item Determining the quality of the resulting image should include, but are not limited to: 
+	\begin{itemize}
+		\item There should not be clear visual evidence that the image has been modified after embedding as well as after restoration
+		\item The image should still carry it's original semantic meaning
+	\end{itemize}
 \end{itemize}
@@
   \item Image after embedding: This refers to the the original image after the embedding process has been applied.
+  \item Reconstruction: This refers to the process of using the content that was embedded into the image to repair the image after embedding if it has been modified.
   \item Image after reconstruction: This refers to the reconstructed version of the original image that was obtained by applying the reconstruction process to the image after embedding.
@@
 Each pixel has 24 bits which in total represents each colour, 8 bits per colour.
-these bits are the 8 binary bits that represent the numerical value of the colour.
+These bits are the 8 binary bits that represent the numerical value of the colour.
 These 8 bits are separated from each other and are each stored in a 8x8 grid in the same location as that of the pixel in the pixel section.
@@
   \item Block: This refers to an individual bit plane of a specific section of the image. There are 8 such blocks in each section since each pixel is represented by 8 bits for each colour.
-  \item BPCS Steganography: Bit-Plane Complexity Segmentation Steganography
+\end{itemize}
+
+\subsection{Chapter layout}
+\begin{itemize}
+\item Chapter 1 serves as an introduction to the concept of self-recovering images
+\item Chapter 2 discusses self-recovering images and their different components
+\item Chapter 3 discusses currently available self-recovering image schemes, comparing their strengths and weaknesses
+\item Chapter 4 provides an overview of the system proposed in this dissertation
+\item Chapter 5 discusses the results achieved during experimentation with the proposed system.
+\item Chapter 6 Provides a conclusion, determining questions stated in section \ref{problemStatement} have been answered
 \end{itemize}
@@
 \subsection{Introduction}
-Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. 
+Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. //TODO <Reference> 
 This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that the image was damaged.
@@
 
-\hspace{0pt} \\
-Self-recovering images pose an interesting problem.
-There is an inherent trade-off between the quality of the image after embedding and the quality of the image after recovery.
-
 \subsection{Steganography}
 \label{introSteganography}
-Steganography is the process of hiding information in such a way that it does not get detected \cite{johnson1998exploring}.
+//TODO <Get better definition and reference> Steganography is the process of hiding information in such a way that it does not get detected \cite{johnson1998exploring}.
 Steganography, derived from Greek means "covered writing".
@@
 The proposed method uses steganography to embed the information into the image in a way that is not easily visibly detectable by a human observer.
-A successful stegnographic method has certain characteristics:
+A successful steganographic method has certain characteristics according to literature:
 \begin{itemize}
-	\item Invisibility: How easy it is to detect that information has been embedded using steganography.
-	\item Robustness: How much of the image that is embedded into can be modified without compromising the embedded information.
-	\item Capacity: The maximal number of bits that can be embedded without introducing statistically detectable artifacts \cite{fridrich2009steganography}.
-It should also be added that the embedding must also not be visually detectable.
+	\item Invisibility: How easy it is to visually detect that information has been embedded using steganography. //TODO <reference>
+	\item Robustness: How much of the image that is embedded into can be modified without compromising the embedded information. //TODO <definition and reference based on traditional stego concepts>
+	\item Capacity: The maximal number of bits that can be embedded without introducing statistically of visually detectable artifacts \cite{fridrich2009steganography}.
 \end{itemize}
-Least significant bit embedding (LSB) is a stegnographic method that can be used to embed information. 
-LSB works by replacing the least significant bit (or n least significant bits) of an image colour value with the binary bits from a message.
-The least significant bit of a colour value is the binary bit/s that carry the least value.
+Least significant bit embedding (LSB) is a steganographic method that can be used to embed information. 
+LSB works by replacing the least significant bit (or n least significant bits) of an image colour value with a binary bit from a message.
+The least significant bit of a colour value is the binary bit/s that carry the least value and thus the change in colour is not perceptible to the human eye.
+LSB is a very simple steganography algorithm and many methods exist for detecting the hidden information //TODO <Reference>
 
 \hspace{0pt} \\
-BPCS Steganography is another stegnographic embedding method \cite{beaullieubpcs}.
+Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in <year> by <authors> \cite{beaullieubpcs}. 
+The goal of the BPCS algorithm is to embed as much data as possible into a cover image while maintaining invisibility \cite{beaullieubpcs}.
 
 \hspace{0pt} \\
-This method works with the following steps:
+The BPCS algorithm consists of the following steps:
 \begin{enumerate}
@@
   \item Calculate the complexity for each block
-  \item Divide the image reference content to be embedded into similar binary 8x8 blocks
-  \item Calculate the complexity for each image reference block and conjugate if not complex enough
-  \item for each image block that is complex enough, replace that block with the next image reference content block
+  \item Divide the message to be embedded into similar binary 8x8 blocks
+  \item Calculate the complexity for each message and conjugate if not complex enough
+  \item For each image block that is complex enough, replace that block with the next message block
   \item Convert the blocks back to binary representation 
-  \item reconstruct the image from the processed blocks 
 \end{enumerate}
@@
 \hspace{0pt} \\
-The BPCS algorithm is a high capacity embedding algorithm. The goal of the BPCS algorithm is thus to embed as much data as possible into a cover image without detection \cite{beaullieubpcs}.
+The BPCS algorithm is a high capacity embedding algorithm. //TODO <reference>
 This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this dissertation.
-The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding (similar to \ref{DynamicBlockOverview}).
-BPCS steg differs however in the fact that the blocks can be conjugated in a checker board pattern to increase complexity and decrease detectability if needs be.
-BPCS steg also differs in the way in which embedding takes place.
-Instead of always embedding into the 3-LSB planes as in \ref{DynamicBlockOverview}.
+The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding.
+and blocks can be conjugated in a checkerboard pattern to increase complexity and decrease detectability if needs be.
 Bit planes are dynamically allocated for embedding.
@@
 \label{introFragWatermarking}
-Fragile watermarks are used to determine if a piece of watermarked digital content has been tampered, and distinguish tampered areas from non-tampered areas without referring to the original digital content \cite{liu2007image}.
+Fragile watermarks are used to determine if a piece of watermarked digital content has been tampered with.
+A fragile watermark system should be able to distinguish tampered areas from non-tampered areas without referring to the original digital content \cite{liu2007image}.
 
@@
 Fragile watermarking is a variation of traditional watermarking where a watermark is embedded into an image such that subsequent alterations to the watermarked image can be detected with high probability \cite{lin1999review}.
-This means that if modifications are made to the watermarked image it would be possible to detect that modifications were made as well as what parts of the image were modified.
-This is a necessary component in self-recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so what parts of the image was modified.
+This means that if modifications are made to the watermarked image it would be possible to detect that modifications were made as well as which parts of the image were modified.
+This is a necessary component in self-recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so which parts of the image was modified.
 
@@
 \label{introSelfEmbedRecovery}
-Self embedding is a scheme where image content is embedded into the image itself.
-This embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself \cite{fridrich1999images}.
-A self embedding and recovery scheme (Further referred to as reconstruction) such as the proposed method contains a couple of high level steps.
+Self embedding is a scheme where image content is embedded into the image itself //TODO <reference.
+The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself \cite{fridrich1999images}.
+A self embedding and recovery scheme (further referred to as reconstruction) such as the proposed method contains a couple of high level steps.
 Firstly the authentic image content is embedded into the original image along with a fragile watermark.
 The resulting image is referred to as the image after embedding
-This watermark will help determine later on which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
-When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which content was modified.
-An attempt is then made to extract the original content for the areas that were modified in the image after embedding.
+The watermark will help determine later on which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
+When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which content was modified, if any.
+An attempt is then made to extract the original content for the areas that were modified in the image.
 If this process is successful the user is left with a high quality reconstruction of the original image.
@@
 There is an inherent quality trade-off present within self embedding schemes.
-The trade-off exists between the image after embedding and the image after reconstruction.
-If an embedding algorith such as LSB(Least significan bit) embedding is used the actual bit values of the original image are overwritten.
+The trade-off exists between the quality of the  image after embedding and the quality of the image after reconstruction.
+If an embedding algorith such as LSB embedding is used the actual bit values of the original image are overwritten.
 Naturally the more bit values are overwritten the more noise is introduced into the image.
-This effectively reduces the quality of the image after embedding.
+This effectively reduces the quality of the image after embedding but increases the amount of data that can be stored in the image thus increasing the quality of the reconstructed image.
 
 \hspace{0pt} \\
-The solution to this would be to simply embed a small amount of information into the image to keep the noise low.
+On one hand one could simply embed a small amount of information into the image to keep the noise low.
 However this presents another problem.
-The quality of the image after reconstruction is dependent on the amount of authentic image data (further referred to as the image reference content) embedded into the image.
+The quality of the image after reconstruction is dependent on the amount of authentic image data (referred to as the image reference content) embedded into the image.
 
 \hspace{0pt} \\
-To achieve maximum quality after embedding the embedded information must be as little as possible.
+To achieve maximum quality after embedding the embedded information must be as small as possible.
 To achieve maximum quality after reconstruction the embedded image reference content must be as large as possible to be as close as possible to the original image.
-There exists then a trade-off between the two.
+There thus exists then a trade-off between the two.
 
 \hspace{0pt} \\
-It might be possible to increase the quality of the image after reconstruction while still keeping the quality after embedding high.
-By using a high capacity embedding algorithm the overall embedding capacity is increased and a higher quality restoration image can be embedded.
-
-\hspace{0pt} \\
-The proposed method in this dissertation attempts to apply the algorithm for BPCS steganography
+The proposed method attempts to apply the algorithm for BPCS steganography
 to the problem of self-recovering images, specifically to increase overall quality.
-The BPCS algorithm can achieve a very high capacity while still remaining undetectable through human perception.
+The BPCS algorithm can achieve a very high capacity while still remaining undetectable to human perception.
 This makes the BPCS algorithm a good choice to increase the capacity of a self-recovering image scheme and possibly increase the quality through this process.
@@
 \label{introConclusion}
-This chapter gave important background information regarding staganography in general as well as two stegnographic embedding methods, LSB embedding and BPCS steganography in section \ref{introSteganography}.
+This chapter gave important background information regarding steganography in general as well as two steganographic embedding methods, LSB embedding and BPCS steganography.
 Fragile watermarking was discussed in section \ref{introFragWatermarking} as well as self embedding and recovery in section \ref{introSelfEmbedRecovery}.
-The next chapter will discuss related work in existing self embedding techniques.
+The next chapter will discuss related work in existing self recovery techniques.
 
@@
 \subsection{Introduction}
-This section compares current content reconstruction algorithms using self embedding.
-This serves to give an overview of what is currently available and to possibly highlight shortcomings of the current algorithms.
+This chapter compares current content reconstruction algorithms using self recovery techniques serving as an overview of what is currently available and to possibly highlight shortcomings of the current algorithms.
 This would be useful to determine if the proposed method does indeed improve on existing methods. 
 It would also help highlight strengths and shortcomings in the proposed method.
-The methods analysed were chosen because they all provide good quality images after embedding as well as good quality images after reconstructed.
+The methods analysed were chosen because they all provide good quality images after embedding as well as good quality images after reconstruction.
 They also each offer an unique approach or aspect to the self-recovering image problem.
@@
 There are 3 current methods discussed in this section.
-An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation \ref{DynamicBlockOverview}.
+An erasure channel model utilizing the remaining authentic content is discussed in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation in \ref{DynamicBlockOverview}.
 A comparison between these 3 methods are provided in section \ref{litStudyCamparison}.
-These 3 methods will be discussed based on their PSNR, tapering rate, security, payload size and embedding capacity.
+These 3 methods will be discussed based on their PSNR, tapering rate, security, payload size and embedding capacity as follows.
 
 \begin{itemize}
-	\item Erasure channel: An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or the bit or it receives a message that the bit was not received, ie the bit was erased.
 	\item Peak signal to noise ratio (PSNR): PSNR is an expression for the ratio between the maximum possible value (power) of a signal and the power of distorting noise that affects the quality of its representation.
-PSNR is represented as a logarithmic decibel scale.
+//TODO <reference> PSNR is represented as a logarithmic decibel scale.
 In terms of images PSNR can objectively measure the amount of noised introduced into an image when compared with the original image.
@@
 	The quality measures mentioned in the 3 methods discussed were measured using the PSNR method. 
-\cite{huynh2008scope} However determined that the validity of PSNR is limited to modifications within the same image.
-	It is thus not reliable to compare PSNR values between two different images.
-	\item Tampering rate: tampering rate is the percentage of image content that can be modified in the image after embedding, while still being able to reconstruct all the modified parts of that image.
+	\item Tampering rate: Tampering rate is the percentage of image content that can be modified in the image after embedding, while still being able to reconstruct all the modified parts of that image.
+//TODO <reference>
 	If too much of the image is modified the embedded image content would be lost and reconstruction would not be possible.
-	\item Security: security refers to how easy it is to detect that information has been embedded into the image using either visual or statistical methods.
-Good security implies that it is difficult to detect and poor security implies that it is simple t detect.
-	\item Payload size: Payload size is defined as the amount of bits that is embedded in to an image using steganographic embedding techniques. 
-	\item Embedding capacity: embedding capacity is defined as the maximum amount of bits that can be embedded into an image using steganographic embedding techniques.
+	\item Security: Security refers to how easy it is to detect that information has been embedded into the image using either visual or statistical methods.
+Good security implies that it is difficult to detect and poor security implies that it is simple detect.
+//TODO <reference>
+	\item Payload size: Payload size is defined as the amount of bits that is embedded into an image using steganographic embedding techniques //TODO <reference>.
+Embedding capacity is defined as the \textbf{maximum} amount of bits that can be embedded into an image using steganographic embedding techniques before visual distortion occurs.
 \end{itemize}
@@
 The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
+An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or it receives a message that the bit was not received, ie the bit was erased.
+//TODO <reference>
 The method uses LSB embedding to embed the image reference content into the image itself and uses a global spreading technique to spread the image reference content across the image.
@@
 The method does not let the quality of the image after reconstruction deteriorate much if the tampering rate is increased up to a value of 50\%.
-They do however note that they can only achieve a minimal increase in reconstruction performance by decreasing the amount of information in the image reference content.
+The authors do however note that they can only achieve a minimal increase in reconstruction performance by decreasing the amount of information in the image reference content.
 By using only 50\% of the available capacity the maximal tampering rate increases form 50\% to 59\%.
@@
 \hspace{0pt} \\
-This method \cite {korus2013efficient} is thus quite robust since 50\% of the image may be tampered with before reconstruction ability starts to deteriorate.
-The security for this method is also very good since the quality of the cover image is not very susceptible to visual checks.
+This method \cite {korus2013efficient} is robust since 50\% of the image may be tampered with before reconstruction ability starts to deteriorate.
+The security for this method is also very good since the quality of the cover image is not susceptible to visual checks.
 The authors did not do any statistical analysis on the image.
-The embedding capacity of this method is also acceptable, but because the method uses some of the authentic image data to aid in the reconstruction process the quality of the image, before and after reconstruction, is still very good even without a very high embedding capacity.
+The embedding capacity of this method is acceptable because the method uses some of the authentic image data to aid in the reconstruction process.
+The quality of the image, before and after reconstruction, is thus good even though the method only has acceptable embedding capacity.
 
@@
 Difference expansion works by exploiting the high redundancy that are present in images \cite {tian2002reversible}.
-With difference expansion the payload is embedded in the difference of pixel values. 
-For a pair of pixel values (x,y) \cite {tian2002reversible}. 
-It should however be noted that image quality reduces rapidly as the payload size is increased when using difference expansion. 
-The method uses difference expansion and to achieve a high embedding capacity while keeping distortion relatively low.
+With difference expansion the payload is embedded in the difference of pixel values \cite {tian2002reversible}. 
+It should be noted that image quality reduces rapidly as the payload size is increased when using difference expansion due to the large amount of change that is introduced into the image. 
+The method achieves a high embedding capacity while keeping distortion relatively low.
 The method achieves a PSNR \textgreater 35dB after embedding.
-The method achieves an embedding capacity of 1.78bpp when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
+The method achieves an embedding capacity of 1.78 bits per pixel (bbp) when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image //TODO <define what the lena image is>.
 
@@
 This could possibly lead to better quality than what their experimental results achieved at the expense of complexity.
-Difference expansion thus seems a good solution to increase the embedding capacity while still keeping the distortion low.
 
 \hspace{0pt} \\ 
-The authors do not mention the image tamper rate that this method \cite {tian2003high} achieves.
+The authors did not mention the image tamper rate that this method \cite {tian2003high} achieves.
 
@@
 \label{DynamicBlockOverview}
-Qian et al \cite{qian2011image} proposes a method for fragile watermarking with good image restoration capabilities.
+Qian et al \cite{qian2011image} proposed a method for fragile watermarking with good image restoration capabilities.
 The proposed method differs from the other methods mentioned in \ref{ErasureChannelOverview} and \ref{differenceExpansionOverview} due to the fact that the method does not embed the information into all blocks uniformly.
@@
 \hspace{0pt} \\
-The advantage of using this dynamic scheme is that there is visual distortion to the image after embedding. 
+The advantage of using this dynamic scheme is that there is very little visual distortion introduced into the image after embedding. 
 This is because if the specific block is already very rough (very busy visually) the human eye does not notice small changes.
@@
 The method proposed by Qian et al \cite{qian2011image} uses 3 LSB bit planes
-\iffalse 
-	//TODO possibly define bit planes here although it is already defined in the terminology
-\fi 
-to embed the needed information in.
+to embed the necessary information in.
 The method achieves good results in experimentation with a image after embedding PSNR \textgreater 37dB as well as a image after reconstruction PSNR = 35dB.
 The method also allows for a tamper rate \textless 35\%.
-The authors do not analyze the security of the algorithm.
+The authors did not analyze the security of the algorithm.
 
@@
 There are however important differences.
-The method described in \ref{ErasureChannelOverview} offers a very good tamper rate of 50\% compared to the method described in \ref{DynamicBlockOverview} which has a tamper rate of 35\%.
+The erasure channel method described in \ref{ErasureChannelOverview} offers a very good tamper rate of 50\% compared to the difference expansion method described in \ref{DynamicBlockOverview} which has a tamper rate of 35\%.
 This means that a larger part of the image after embedding can be tampered with while still being able to reconstruct the image.
@@
 \hspace{0pt} \\
-The method described in \ref{differenceExpansionOverview} achieves an image after embedding with a PSNR \textgreater 35dB, the method described in \ref{ErasureChannelOverview} achieves similar results, however the method described in \ref{DynamicBlockOverview} achieves an image after embedding PSNR \textgreater 37dB.
-This means that the method described in \ref{DynamicBlockOverview} would have less noise in the image after embedding and would thus have better overall quality of the image after embedding.
+The difference expansion method described in \ref{differenceExpansionOverview} achieves an image after embedding with a PSNR \textgreater 35dB and the erasure channel method achieves similar results, however the dynamic block allocation method achieves an image after embedding PSNR \textgreater 37dB.
+This means that the dynamic block allocation method would have less noise in the image after embedding and would thus have better overall quality of the image after embedding.
 
 \hspace{0pt} \\
-At almost equal tamper rates of around 33\%-35\% the method described in \ref{ErasureChannelOverview} achieves an image after reconstruction PSNR \textgreater 40dB whereas the method described in \ref{DynamicBlockOverview} only achieves an image after reconstruction PSNR = 35dB.
-The method described in \ref{differenceExpansionOverview} only achieves an image after reconstruction quality of about 50\% the original image.
-This means that the method described in \ref{ErasureChannelOverview} would generally produce better quality reconstructed images than the methods described in \ref{DynamicBlockOverview} and \ref{differenceExpansionOverview}.
+At almost equal tamper rates of around 33\%-35\% the erasure channel method achieves an image after reconstruction PSNR \textgreater 40dB whereas the dynamic block allocation method only achieves an image after reconstruction PSNR = 35dB.
+The difference expansion method only achieves an image after reconstruction quality of about 50\% the original image.
+This means that the erasure channel method would generally produce better quality reconstructed images than the other two methods.
 
 \hspace{0pt} \\
-This means that the method described in \ref{ErasureChannelOverview} provides the best tamper rate and the best reconstructed image quality, and the method described in \ref{DynamicBlockOverview} provides the best image after embedding quality.
-The method described in \ref{differenceExpansionOverview} provides decent quality of the image after embedding as well as the image after reconstruction.
+The erasure channel method thus provides the best tamper rate and the best reconstructed image quality, and the dynamic block allocation method provides the best image after embedding quality.
+The difference expansion method provides decent quality of the image after embedding as well as the image after reconstruction.
 
@@
 This chapter looked at currently available methods for self-recovering images.
-An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation \ref{DynamicBlockOverview}.
-A comparison between these methods was also provided in section \ref{litStudyCamparison}.
+An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation in \ref{DynamicBlockOverview}.
+A comparison between these methods was provided in section \ref{litStudyCamparison}.
 This information will be used to determine the success of the self-recovering image method proposed in this dissertation by comparing the results from the proposed method with the results achieved by the methods discussed in this chapter.

### 2014-10-23 Paper/main.tex
Changes and annotations chapter 4

@@
 This chapter discusses the details of the implementation for the self-recovering image method proposed in this dissertation.
-Embedding is discussed under which BPCS staganography and fragile watermarking will also be discussed.
-The extraction and restoration process will be discussed under which authentication and restoration will also be discussed.
-Diagrams are also provided to visualize the embedding as well as the extraction process
+Embedding is discussed in section \ref{embedding} and BPCS steganography and fragile watermarking will also be discussed again.
+The extraction and restoration process is discussed in section \ref{extractRestore} under which authentication and restoration will also be discussed.
+Diagrams are provided to visualize the embedding as well as the extraction process.
 
@@
 \label{impOverview}
-The self-recovering method proposed in this dissertation uses BPCS steganography to increase the payload capacity of the cover image in order to be able to embed more reference content into the image without introducing visual distortion.
-In addition a fragile watermark was used to detect which parts of the image was damaged and thus needs to be reconstructed.
+The self-recovering method proposed in this dissertation uses BPCS steganography to increase the payload capacity of the cover image in order to be able to embed more image reference content into the image without introducing visual distortion.
+In addition a fragile watermark was used to detect which parts of the image is damaged and thus needs to be reconstructed.
 
@@
 
-BPCS Steg has an inherent property that if any part of the image is modified the embedded message will be lost.
+BPCS steganography has an inherent property that if any part of the image is modified the embedded message will be lost.
 This would obviously be a problem for the proposed method since the image will definitely be modified.
@@
 The proposed method uses a simple method for spreading the image reference content across the image.
-The image reference content to be embedded is first divided into blocks as per the BPCS steg algorithm.
+The image reference content to be embedded is first divided into blocks as per the BPCS steganography algorithm.
 These blocks are subsequently stored in a list. 
@@
 This process however produced a much lower tamper rate due to the fact that the image reference content was often embedded very close to the original image content that it was referencing.
-The result was a lowered tamper rate.
 The proposed method thus rather used the more successful method describe above.
@@
 \hspace{0pt} \\
-The block complexity is calculated by using a border complexity method. \cite{beaullieubpcs}.
-That is for each binary bit that has an adjacent binary bit that is different than itself the border count is increased. 
+The block complexity is calculated by using a border complexity method \cite{beaullieubpcs}. 
+For each binary bit that has an adjacent binary bit that is different than itself the border count is increased. 
 The final border count is then divided with the theoretical maximum border count, which would be the border count for a grid of the same size with a checkerboard pattern.
@@
 This is needed since the receiver of the image would not be able to determine if a block has been conjugated or no without such a map.
+The conjugation map is also embedded into the image.
 
@@
 \label{impFragileWatermark}
-In order to be able to detect which parts of the image have been tampered with a fragile watermark can be used.
+In order to be able to detect which parts of the image have been tampered with a fragile watermark was used.
 
@@
 This is because each block is treated as a separate embedding entity.
-This results in the fact that there is not always enough redundancy to be able to compress the bit streams for embedding.
+This resulted in the fact that there was not always enough redundancy to be able to compress the bit streams for embedding.
 
@@
 \hspace{0pt} \\
-The fragile watermark used in the proposed method embeds a calculated hash into the image that is used to authenticate the content when the image is reconstructed on the receiving end.
+The fragile watermark used in the proposed method thus embeds a calculated hash into the image that is used to authenticate the content when the image is reconstructed on the receiving end.
 
 \hspace{0pt} \\
-For each of the 8x8 pixel section in the image after embedding a hash is calculated by combining the binary of each of the 7 Most significant bit planes of that section.
+For each of the 8x8 pixel sections in the image after embedding a hash is calculated by combining the binary of each of the 7 Most significant bit planes of that section.
 This binary hash stream is then used as the input to the SHA-256 hash function.
@@
 However should this case arise, the proposed method would simply restore that section as well.
-Thus not having a major impact on the final result of the reconstruction.
+Thus it does not have a major impact on the final result of the reconstruction.
 
@@
 The extracted hash is then compared with the calculated hash and if they match the section is authentic.
-If they do not match then that section has been tampered with.
+If they do not match then that section has been tampered with and needs to be reconstructed.
 
@@
 The embedded image content is extracted at this point from the processed bit plane blocks and the embedded image is reconstructed.
-In order to know the location of the extracted pixels the embedding map that was embedded into the LSB bit plane of that image section is consulted \ref{bpcsSteg}.
+In order to know the location of the extracted pixels the embedding map that was embedded into the LSB bit plane of that image section is consulted.
 The reconstructed image is then scaled up back to it's original size of 512x512 pixels.
 The reconstructed image is then also split into bit plane blocks.
-This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
-The bit plane blocks generated from the image after embedding now get iterated and each block that was found not to be authentic is replaced by the corresponding reconstructed bit plane block.
+This is accomplished by first completing steps 1-4 of the BPCS steganography algorithm (\ref{bpcsSteg}).
+The bit plane blocks generated from the image after embedding are traversed and each block that was found not to be authentic is replaced by the corresponding reconstructed bit plane block.
 
@@
 It was however found that the tamper rate possible was quite low at \textless 3\%.
-To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the Image reference content was now being embedded twice.
+To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the image reference content was now being embedded twice.
 The results can be seen in figure \ref{fig:lenaEmbedTwiceEmbedding} and figure \ref{fig:lenaEmbedTwiceRestoration}
@@
 This experiment was also completed on the following image.
-First Embedding the Image reference content once (figure \ref{fig:treeEmbedOnceEmbedding} and figure \ref{fig:treeEmbedOnceRestoration}):
+First by embedding the image reference content once (figure \ref{fig:treeEmbedOnceEmbedding} and figure \ref{fig:treeEmbedOnceRestoration}):
 
@@
 The tamper rate, as was the case with the first image image (figure \ref{fig:lenaEmbedTwiceRestoration}), was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
+//TODO <Summarize all findings in an additional table>
 

### 2014-10-23 Paper/main.tex
Chapter 5 changes

@@
 \label{interpretation}
-The proposed method for self-recovering images using the BPCS Steg embedding algorithm described in the preceding sections was shown to be effective.
-According to Appendix B in \cite{korus2013efficient} the proposed method achieved Average to High quality reconstruction in the case of figure \ref{fig:lenaEmbedTwiceRestoration} and figure \ref{fig:lenaEmbedOnceRestoration} respectively.
-The proposed method achieved Low quality reconstruction in the case of figure \ref{fig:treeEmbedOnceRestoration} and figure \ref{fig:treeEmbedTwiceRestoration} according to \cite{korus2013efficient}.
+The proposed method for self-recovering images using the BPCS steganography embedding algorithm described in the preceding sections was shown to be effective.
+According to Appendix B in \cite{korus2013efficient} the proposed method achieved average to high quality reconstruction in the case of figure \ref{fig:lenaEmbedTwiceRestoration} and figure \ref{fig:lenaEmbedOnceRestoration} respectively.
+The proposed method achieved low quality reconstruction in the case of figure \ref{fig:treeEmbedOnceRestoration} and figure \ref{fig:treeEmbedTwiceRestoration} according to \cite{korus2013efficient}.
 
@@
 \hspace{0pt} \\
-The proposed method does not perform as well as the method described in \ref{ErasureChannelOverview}.
-The proposed method achieves PSNR values that are about 5dB worse than the method described in \ref{ErasureChannelOverview}.
-Compared to the method described in \ref{differenceExpansionOverview} the proposed method performs in a similar manner.
-The PSNR values achieved are worse than that of the method in \ref{differenceExpansionOverview} but the difference is around 1-2dB and is thus almost not noticeable to the human eye.
-It should also be mentioned that the proposed method uses no compression on the image reference content, similar to the method in \ref{differenceExpansionOverview}.
+The proposed method does not perform as well as the erasure channel method and achieves PSNR values that are about 5dB worse than the erasure channel method.
+Compared to the difference expansion method the proposed method performs in a similar manner.
+The PSNR values achieved are worse than that of the difference expansion method but the difference is around 1-2dB and is thus almost not noticeable to the human eye.
+It should also be mentioned that the proposed method uses no compression on the image reference content, similar to the difference expansion method.
 This method thus serves as a more equal comparison.
@@
 \hspace{0pt} \\
-\cite{wang2002image} Points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
-PSNR is a useful measure for objective image quality assessment to a certain degree however there are other important factors to consider. 
+Research in \cite{wang2002image} Points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
+PSNR is a useful measure for objective image quality assessment to a certain degree, however there are other important factors to consider. 
 The one important factor is how a person would perceive the image quality.
@@
 \hspace{0pt} \\
-It was found during experimentation that image quality can vary greatly among different image using the proposed method.
+It was found during experimentation that image quality can vary greatly among different images using the proposed method.
 This can be attributed to the fact that an adaptive embedding method is used and where the image reference content is embedded thus differs depending on the chosen original image.
@@
 The embedding rate and effects of the embedding rate seemed consistent across the different images used.
-The embedding rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the one described in \ref{DynamicBlockOverview}.
-However it was found that if the image reference content is embedded twice into the original image that the tamper rate compares equally to that of methods such as the one described in \ref{DynamicBlockOverview}.
+The embedding rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the dynamic block allocation method.
+However it was found that if the image reference content is embedded twice into the original image that the tamper rate compares equally to that of dynamic block allocation method.
 

### 2014-10-23 Paper/main.tex
Referencing issues fixed

@@
 \hspace{0pt} \\
-Most self-recovering techniques have a tradeoff trade-off concerning the quality of the image after embedding and the quality of the image after recovery.
+Most self-recovering techniques have a trade-off concerning the quality of the image after embedding and the quality of the image after recovery.
 If the one's quality is increased the other's quality will be reduced.
@@
 \subsection{Introduction}
-Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. //TODO <Reference> 
-This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that the image was damaged.
+Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques.
+This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that parts of the image was damaged without the need to access the original image \cite{fridrich1999images}.
 
@@
 \label{introSteganography}
-//TODO <Get better definition and reference> Steganography is the process of hiding information in such a way that it does not get detected \cite{johnson1998exploring}.
+Steganography is the science that involves communicating secret data in an appropriate multimedia carrier eg images.
+It comes under the assumption that if the feature is visible, the point of attack is evident, thus the goal is always to conceal the very existence of the embedded data \cite{cheddad2010digital}.
 Steganography, derived from Greek means "covered writing".
@@
 \begin{itemize}
-	\item Invisibility: How easy it is to visually detect that information has been embedded using steganography. //TODO <reference>
-	\item Robustness: How much of the image that is embedded into can be modified without compromising the embedded information. //TODO <definition and reference based on traditional stego concepts>
+	\item Invisibility: The invisibility of a steganographic algorithm is very important.
+The strength of steganography lies in its ability to be unnoticed by the human eye.
+If one can see that an image has been tampered with then invisibility has been lost and the algorithm has been compromised \cite{morkel2005overview}.
+	\item Robustness: The resistance to various image processing methods, compression and other image modifications.
+Thus how much of the image can be modified without destroying the embedded content \cite{cheddad2010digital}.
 	\item Capacity: The maximal number of bits that can be embedded without introducing statistically of visually detectable artifacts \cite{fridrich2009steganography}.
@@
 The least significant bit of a colour value is the binary bit/s that carry the least value and thus the change in colour is not perceptible to the human eye.
-LSB is a very simple steganography algorithm and many methods exist for detecting the hidden information //TODO <Reference>
+LSB embedding is the most common and easiest method for embedding messages in an image \cite{lee2000high}, and many methods exist for detecting the hidden information
 
 \hspace{0pt} \\
-Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in <year> by <authors> \cite{beaullieubpcs}. 
+Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason. \cite{kawaguchi1999principles}. 
 The goal of the BPCS algorithm is to embed as much data as possible into a cover image while maintaining invisibility \cite{beaullieubpcs}.
@@
 \hspace{0pt} \\
-The BPCS algorithm is a high capacity embedding algorithm. //TODO <reference>
+The BPCS algorithm is a high capacity embedding algorithm \cite{beaullieubpcs}.
 This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this dissertation.
@@
 \label{introSelfEmbedRecovery}
-Self embedding is a scheme where image content is embedded into the image itself //TODO <reference.
-The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself \cite{fridrich1999images}.
+Self embedding is a scheme where image content is embedded into the image itself \cite{fridrich1999images}.
+The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself.
 A self embedding and recovery scheme (further referred to as reconstruction) such as the proposed method contains a couple of high level steps.
@@
 \begin{itemize}
-	\item Peak signal to noise ratio (PSNR): PSNR is an expression for the ratio between the maximum possible value (power) of a signal and the power of distorting noise that affects the quality of its representation.
-//TODO <reference> PSNR is represented as a logarithmic decibel scale.
+	\item Peak signal to noise ratio (PSNR): PSNR is a commonly used metric for objective signal quality measurement.
+PSNR provides a quality measurement based on the squared error between the original and processed signal \cite{turaga2004no}.
+PSNR is represented as a logarithmic decibel scale.
 In terms of images PSNR can objectively measure the amount of noised introduced into an image when compared with the original image.

### 2014-10-23 Paper/main.tex
All issues fixed

@@
 \subsection{Introduction}
-//TODO <//DONE// Rewrite in a more story like fashion, mention the why, what are the problems, steganography, fragile watermarks, self embedding etc>
-
 During communication images can by modified either intentionally or unintentionally.
@@
 	The quality measures mentioned in the 3 methods discussed were measured using the PSNR method. 
-	\item Tampering rate: Tampering rate is the percentage of image content that can be modified in the image after embedding, while still being able to reconstruct all the modified parts of that image.
-//TODO <reference>
-	If too much of the image is modified the embedded image content would be lost and reconstruction would not be possible.
+	\item Tampering rate: Tampering rate is the percentage of image content that has been modified in the image after embedding \cite{qian2011image}.
+	If the tampering rate is too high the embedded image content would be lost and reconstruction would not be possible.
 	\item Security: Security refers to how easy it is to detect that information has been embedded into the image using either visual or statistical methods.
-Good security implies that it is difficult to detect and poor security implies that it is simple detect.
-//TODO <reference>
-	\item Payload size: Payload size is defined as the amount of bits that is embedded into an image using steganographic embedding techniques //TODO <reference>.
+Good security implies that it is difficult to detect and poor security implies that it is to simple detect \cite{fridrich2009steganography}.
+	\item Payload size: Payload size is defined as the amount of bits that is embedded into an image using steganographic embedding techniques \cite{chen2010high}.
 Embedding capacity is defined as the \textbf{maximum} amount of bits that can be embedded into an image using steganographic embedding techniques before visual distortion occurs.
@@
 The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
-An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or it receives a message that the bit was not received, ie the bit was erased.
-//TODO <reference>
+An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or it receives a message that the bit was not received, ie the bit was erased \cite{korus2013efficient}.
 The method uses LSB embedding to embed the image reference content into the image itself and uses a global spreading technique to spread the image reference content across the image.
@@
 The method achieves a PSNR \textgreater 35dB after embedding.
-The method achieves an embedding capacity of 1.78 bits per pixel (bbp) when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image //TODO <define what the lena image is>.
+The method achieves an embedding capacity of 1.78 bits per pixel (bbp) when using up to the 4th LSB on a 512x512 8bit gray-scale version of the Lena image.
+Lena is the name given to a standard test image widely used in the field of image processing since 1973 \cite{lenaOnlineArticle}.
 
@@
 \hspace{0pt} \\
-After the image (shown in figure \ref{fig:lenaEmbedOnceRestoration}) was reconstructed the PSNR of the image after reconstruction (figure \ref{fig:lenaEmbedOnceRestoration}) was calculated in relation to the Original Image (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+After the image (shown in figure \ref{fig:lenaEmbedOnceRestoration}) was reconstructed the PSNR of the image after reconstruction (figure \ref{fig:lenaEmbedOnceRestoration}) was calculated in relation to the original Image (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
 In this instance the PSNR after restoration was: 34.89dB.
@@
 The tamper rate, as was the case with the first image (figure \ref{fig:lenaEmbedOnceRestoration}), was also \textless 3\%.
-The experiment was also conducted by embedding the Image reference content twice (figure \ref{fig:treeEmbedTwiceEmbedding} and figure \ref{fig:treeEmbedTwiceRestoration}).
+The experiment was also conducted by embedding the image reference content twice (figure \ref{fig:treeEmbedTwiceEmbedding} and figure \ref{fig:treeEmbedTwiceRestoration}).
 
@@
 //TODO <Summarize all findings in an additional table>
+\begin{center}
+  \begin{tabular}{| l | l | l | l |}
+    \hline
+    \multicolumn{4}{|c|}{Experimental results summary} \\
+    \hline
+    Image & PSNR after embedding & PSNR after restoration & Tampering rate \\ \hline
+    Figure \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedOnceRestoration} (Embed once) & 34.92dB & 34.89dB & \textless 3\% \\ \hline
+    Figure \ref{fig:lenaEmbedTwiceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} (Embed twice) & 34.92dB & 32.52 dB & \textless 35\% \\ \hline
+    Figure \ref{fig:treeEmbedOnceEmbedding} - \ref{fig:treeEmbedOnceRestoration} (Embed once) & 27.94dB & 27.72dB & \textless 3\% \\ \hline
+    Figure \ref{fig:treeEmbedTwiceEmbedding} - \ref{fig:treeEmbedTwiceRestoration} (Embed twice) & 27.93dB & 26.05dB & \textless 35\% \\ \hline
+    \hline
+  \end{tabular}
+\end{center}
 

### 2014-10-23 Paper/main.tex
Minor modifications to the conclusion

@@
 \subsection{Summary}
-The proposed method described used the BPCS steganaography algorithm, which is an adaptive embedding algorithm described in \ref{bpcsSteg}, and applied the algorithm to the self-embedding problem.
+The proposed method described used the BPCS steganaography algorithm, which is an adaptive embedding algorithm described in \ref{bpcsSteg}, and applied the algorithm to the self recovering image problem.
 The proposed method was shown to provide good quality as well as a good tamper rate.
@@
 The proposed method did not introduce clear visual evidence that the image has been modified after embedding as well as after restoration and the image did still carry it's original meaning.
-The proposed method thus achieved most of what it attempted to achieve with the only problem being that the quality is dependent on the image used.
+The proposed method thus achieved most of what it attempted to achieve with the only exception being that the quality is dependent on the image used.
 
@@
 By compressing the image reference content it would be possible to embed a higher quality reference image into the original image without increasing the payload size.
-It would also be possible to reduce the amount embedding capacity used of the original image, due to a smaller amount of bits that need to be embedded, which would result in less of the original image being changed and thus less noise being introduced into the original image.
+It would also be possible to reduce the amount embedding capacity used, due to a smaller amount of bits that need to be embedded, which would result in less of the original image being changed and thus less noise being introduced into the original image.
 This could possibly lead to increasing the overall quality of the proposed self-recovering image scheme.
+
+\hspace{0pt} \\
+It was shown that the proposed method's quality is dependent on the cover image used.
+Further research can be conducted to determine which image characteristics impact the quality of the images produced by the proposed method
 

### 2014-10-29 Paper/main.tex
Section 1 Completed

@@
 
-\title{Self recovering capabilities in images using the BPCS Steganography algorithm}
+\title{Increasing quality of self-recovering images using BPCS Steganography}
 
@@
 This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in the self-recovering image problem using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
-The proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the best currently available self-recovering image methods.
+Experimental results show that the proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the currently available self-recovering image methods.
 
@@
 \subsection{Introduction}
-During communication images can by modified either intentionally or unintentionally.
+During communication images can be modified either intentionally or unintentionally.
 These modifications can be small changes that does not change the meaning of the image, or bigger changes, for example the removal of key aspects from the image.
@@
 Self-recovering techniques attempt to preserve image content by embedding the image within itself to enable the reconstruction of the image if the image was tampered with.
-Self-recovering techniques use steganography, a technology used to embed information in digital media \cite{johnson1998exploring}, to hide the image content within the image.
+Self-recovering techniques usually use steganography, a technology used to embed information in digital media \cite{johnson1998exploring}, to hide an approximation of the image within the image itself.
+If the image was tampered with, this embedded approximation can then be used to attempt to recover the original image.
  Self-recovering techniques also use fragile watermarks which is a technology commonly used in image authentication, to determine which areas of an image was tampered with.
@@
 Most self-recovering techniques have a trade-off concerning the quality of the image after embedding and the quality of the image after recovery.
-If the one's quality is increased the other's quality will be reduced.
+If the one's quality is increased the other's quality will be reduced since an increase in the amount of embedded information could lead to a decrease in image quality and vice versa..
 
@@
 \label{problemStatement}
-The proposed method aims to answer the following questions
+The proposed method aims to answer the following questions:
 \begin{itemize}
@@
 \end{itemize}
+These questions will be addressed in chapters to follow.
 
@@
 Firstly a literature review was conducted to determine the currently available methods for self-recovering images. 
-After a shortcoming was identified the proposed method was designed and then implemented in the form of a Java software application in order to attempt to improve on the identified shortcoming. 
+The proposed method was designed based on shortcomings that were found with currently available self-recovering methods. 
+The proposed method was then implemented in the form of a Java software application in order to attempt to improve on the identified shortcomings. 
 The results of the proposed method were then compared to the results of other relevant self-recovering image methods.
@@
   \item Original Image: This refers to the original image without any modifications.
-  \item Embedding: Embedding in the context of this dissertation refers to the process of storing digital information in an image's content in such a way that the original image is still distinguishable.
+  \item Embedding: Embedding in the context of this dissertation refers to the process of storing digital information in an image in such a way that the original image is still distinguishable.
   \item Image after embedding: This refers to the the original image after the embedding process has been applied.
@@
 \item Chapter 4 provides an overview of the system proposed in this dissertation
-\item Chapter 5 discusses the results achieved during experimentation with the proposed system.
-\item Chapter 6 Provides a conclusion, determining questions stated in section \ref{problemStatement} have been answered
+\item Chapter 5 discusses the results achieved during experimentation with the proposed system
+\item Chapter 6 provides a conclusion, to determine if the questions stated in section \ref{problemStatement} have been answered
 \end{itemize}
@@
 The research methodology followed was described. A list of terminologies used in this dissertation was also given.
-The next chapter will give a more detailed overview of all the components that make up self-recovering images.
+The next chapter will give a more detailed overview of all the components of self-recovering images.
 
@@
 The tamper rate, as was the case with the first image image (figure \ref{fig:lenaEmbedTwiceRestoration}), was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
-//TODO <Summarize all findings in an additional table>
 \begin{center}
@@
 \subsection{Summary}
-The proposed method described used the BPCS steganaography algorithm, which is an adaptive embedding algorithm described in \ref{bpcsSteg}, and applied the algorithm to the self recovering image problem.
+The proposed method described used the BPCS steganaography algorithm, which is an adaptive embedding algorithm described in \ref{bpcsSteg}, and applied the algorithm to the self-recovering image problem.
 The proposed method was shown to provide good quality as well as a good tamper rate.

### 2014-10-29 Paper/main.tex
section 2 done

@@
 \subsection{Introduction}
-Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques.
-This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that parts of the image was damaged without the need to access the original image \cite{fridrich1999images}.
+Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques \cite{fridrich1999images}.
+This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the event that parts of the image were damaged.
+Reconstruction can thus be done without the need to access the original image \cite{fridrich1999images}.
 
@@
 \label{introSteganography}
-Steganography is the science that involves communicating secret data in an appropriate multimedia carrier eg images.
-It comes under the assumption that if the feature is visible, the point of attack is evident, thus the goal is always to conceal the very existence of the embedded data \cite{cheddad2010digital}.
+Steganography is a science that involves communicating secret data in an appropriate multimedia carrier i.e.
+images.
+It operates under the assumption that if the embedded information is visible, the point of attack is evident, thus the goal is always to conceal the very existence of the embedded data \cite{cheddad2010digital}.
 Steganography, derived from Greek means "covered writing".
-This means it differs from cryptography which does not attempt to hide information but merely scrambles it so it cannot be understood.
+Steganography differs from cryptography which does not attempt to hide information but merely scrambles it so it cannot be understood.
 Steganography does not scramble the information but rather relies on the information to remain hidden.
@@
 \hspace{0pt} \\
-The proposed method uses steganography to embed the information into the image in a way that is not easily visibly detectable by a human observer.
+The proposed method uses steganography to embed the information into an image in a way that is not easily visibly detectable by a human observer.
 A successful steganographic method has certain characteristics according to literature:
@@
 Thus how much of the image can be modified without destroying the embedded content \cite{cheddad2010digital}.
-	\item Capacity: The maximal number of bits that can be embedded without introducing statistically of visually detectable artifacts \cite{fridrich2009steganography}.
+	\item Capacity: The maximum number of bits that can be embedded into an image without introducing statistically or visually detectable artifacts \cite{fridrich2009steganography}.
 \end{itemize}
 Least significant bit embedding (LSB) is a steganographic method that can be used to embed information. 
-LSB works by replacing the least significant bit (or n least significant bits) of an image colour value with a binary bit from a message.
-The least significant bit of a colour value is the binary bit/s that carry the least value and thus the change in colour is not perceptible to the human eye.
+LSB works by replacing the least significant bit (or \textit{n} least significant bits) of an image colour value with a binary bit from a message.
+The least significant bit of a colour value is the binary bit that carries the least value and thus the change in colour is not perceptible to the human eye.
 LSB embedding is the most common and easiest method for embedding messages in an image \cite{lee2000high}, and many methods exist for detecting the hidden information
@@
 \hspace{0pt} \\
-Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason. \cite{kawaguchi1999principles}. 
+Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason \cite{kawaguchi1999principles}. 
 The goal of the BPCS algorithm is to embed as much data as possible into a cover image while maintaining invisibility \cite{beaullieubpcs}.
@@
   \item Get the binary representation of the image
-  \item Convert the binary representation into Gray code
   \item Divide the image into bit planes
@@
   \item Divide the message to be embedded into similar binary 8x8 blocks
-  \item Calculate the complexity for each message and conjugate if not complex enough
+  \item Calculate the complexity for each message block and conjugate - that is, increase the complexity of the block - if not complex enough
   \item For each image block that is complex enough, replace that block with the next message block
@@
 The BPCS algorithm is a high capacity embedding algorithm \cite{beaullieubpcs}.
-This refers to detection by human perception as well as statistical analysis although the latter is not the focus of this dissertation.
-The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding.
-and blocks can be conjugated in a checkerboard pattern to increase complexity and decrease detectability if needs be.
+The BPCS algorithm uses an adaptive scheme to classify blocks that are suitable for embedding and blocks can be conjugated in a checkerboard pattern to increase complexity and decrease detectability if needs be.
 Bit planes are dynamically allocated for embedding.
-One section may thus only embed into one bit plane while another may use all 7 available bit planes.
+One section of the image may thus only use one bit plane for embedding while another may use all 7 available bit planes.
 
@@
 \label{introFragWatermarking}
-Fragile watermarks are used to determine if a piece of watermarked digital content has been tampered with.
+Fragile watermarks are used to determine if a piece of watermarked digital content has been tampered with \cite{liu2007image}.
 A fragile watermark system should be able to distinguish tampered areas from non-tampered areas without referring to the original digital content \cite{liu2007image}.
@@
 This means that if modifications are made to the watermarked image it would be possible to detect that modifications were made as well as which parts of the image were modified.
-This is a necessary component in self-recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and if so which parts of the image was modified.
+This is a necessary component in self-recovering images because in order to be able to recover image data it first needs to be determined if the image after embedding has been modified and, if so, which parts of the image were modified.
+A fragile watermark works by generating a hash of a specific image section and then embedding that hash into the image.
+To calculate if the image section is authentic the hash would be recalculated and compared with the embedded hash.
+If the two hashes are identical then the image section is authentic.
 
@@
 \label{introSelfEmbedRecovery}
-Self embedding is a scheme where image content is embedded into the image itself \cite{fridrich1999images}.
+Self-embedding is a scheme where image content is embedded into the image itself \cite{fridrich1999images}.
 The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself.
-A self embedding and recovery scheme (further referred to as reconstruction) such as the proposed method contains a couple of high level steps.
-Firstly the authentic image content is embedded into the original image along with a fragile watermark.
-The resulting image is referred to as the image after embedding
-The watermark will help determine later on which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
-When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which content was modified, if any.
-An attempt is then made to extract the original content for the areas that were modified in the image.
+self-embedding is also referred to as self-recovering
+A self-recovery scheme such as the proposed method contains a couple of high level steps.
+Firstly an approximation of the original image, referred to as the image reference content, is embedded into the original image along with a fragile watermark.
+The resulting image is referred to as the image after embedding.
+The watermark helps to determine which parts of the image after embedding was modified if any (see \ref{introFragWatermarking}).
+When the authentic image needs to be reconstructed, after modification, the fragile watermark is used to determine which areas of the image were modified.
+An attempt is then made to extract the areas that were modified from the original image and replace the tampered areas with the extracted information.
 If this process is successful the user is left with a high quality reconstruction of the original image.
@@
 \hspace{0pt} \\
-There is an inherent quality trade-off present within self embedding schemes.
+There is an inherent quality trade-off present within self-embedding schemes.
 The trade-off exists between the quality of the  image after embedding and the quality of the image after reconstruction.
-If an embedding algorith such as LSB embedding is used the actual bit values of the original image are overwritten.
+If an embedding algorithm such as LSB embedding is used the actual bit values of the original image are overwritten.
 Naturally the more bit values are overwritten the more noise is introduced into the image.
@@
 \hspace{0pt} \\
-On one hand one could simply embed a small amount of information into the image to keep the noise low.
-However this presents another problem.
-The quality of the image after reconstruction is dependent on the amount of authentic image data (referred to as the image reference content) embedded into the image.
-
-\hspace{0pt} \\
-To achieve maximum quality after embedding the embedded information must be as small as possible.
+To achieve maximum quality after embedding the embedded information must be as small as possible or the algorithm should allow as much as possible embedded information without visually changing the image.
 To achieve maximum quality after reconstruction the embedded image reference content must be as large as possible to be as close as possible to the original image.
-There thus exists then a trade-off between the two.
+There thus exists a trade-off between the two.
 
@@
 This chapter gave important background information regarding steganography in general as well as two steganographic embedding methods, LSB embedding and BPCS steganography.
-Fragile watermarking was discussed in section \ref{introFragWatermarking} as well as self embedding and recovery in section \ref{introSelfEmbedRecovery}.
+Fragile watermarking was discussed in section \ref{introFragWatermarking} as well as self-embedding and recovery in section \ref{introSelfEmbedRecovery}.
 The next chapter will discuss related work in existing self recovery techniques.
@@
 
-\subsubsection{Dynamic block allocation for self embedding}
+\subsubsection{Dynamic block allocation for self-embedding}
 \label{DynamicBlockOverview}
@@
 This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
-This serves to give random access to the embedded content which is an essential property of self embedding as defined by Korus et al. \cite{korus2013efficient}.
+This serves to give random access to the embedded content which is an essential property of self-embedding as defined by Korus et al. \cite{korus2013efficient}.
 This is essential in order for the reconstruction process to function properly.

### 2014-10-29 Paper/main.tex
Section 3 completed

@@
 Fragile watermarking was discussed in section \ref{introFragWatermarking} as well as self-embedding and recovery in section \ref{introSelfEmbedRecovery}.
-The next chapter will discuss related work in existing self recovery techniques.
+The next chapter will discuss related work in existing self-recovery techniques.
 
@@
 \subsection{Introduction}
-This chapter compares current content reconstruction algorithms using self recovery techniques serving as an overview of what is currently available and to possibly highlight shortcomings of the current algorithms.
+This chapter compares current content reconstruction algorithms using self-recovery techniques to serve as an overview of what is currently available and to possibly highlight shortcomings of the current algorithms.
 This would be useful to determine if the proposed method does indeed improve on existing methods. 
@@
 A comparison between these 3 methods are provided in section \ref{litStudyCamparison}.
-These 3 methods will be discussed based on their PSNR, tapering rate, security, payload size and embedding capacity as follows.
+These 3 methods will be discussed based on their PSNR, tampering rate, security, payload size and embedding capacity as follows:
 
@@
 PSNR is represented as a logarithmic decibel scale.
-In terms of images PSNR can objectively measure the amount of noised introduced into an image when compared with the original image.
+In terms of images PSNR can objectively measure the amount of noise introduced into an image when compared with the original image.
 	As the mean squared error between the two images approaches 0 the PSNR approaches infinity. A higher PSNR value thus provides a higher quality image. 
@@
 	\item Security: Security refers to how easy it is to detect that information has been embedded into the image using either visual or statistical methods.
-Good security implies that it is difficult to detect and poor security implies that it is to simple detect \cite{fridrich2009steganography}.
+Good security implies that it is difficult to detect and poor security implies that it is simple to detect \cite{fridrich2009steganography}.
 	\item Payload size: Payload size is defined as the amount of bits that is embedded into an image using steganographic embedding techniques \cite{chen2010high}.
-Embedding capacity is defined as the \textbf{maximum} amount of bits that can be embedded into an image using steganographic embedding techniques before visual distortion occurs.
+Embedding capacity is defined as the \textbf{maximum} amount of bits that can be embedded into an image using steganographic embedding techniques before visual distortion occurs \cite{chen2010high}.
 \end{itemize}
@@
 The method proposed in \cite {korus2013efficient} uses an erasure channel as a model for the content reconstruction problem.
-An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or it receives a message that the bit was not received, ie the bit was erased \cite{korus2013efficient}.
+An erasure channel is a channel that can transmit a bit of information and the receiver can either receive the bit or it receives a message that the bit was not received, in other words, the bit was erased \cite{korus2013efficient}.
 The method uses LSB embedding to embed the image reference content into the image itself and uses a global spreading technique to spread the image reference content across the image.
-The method also proposes that by using the remaining authentic content in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after reconstruction.
+The method also proposes that by using the remaining authentic content, that is the content that has not been modified, in the image it is possible to have a high tamper rate while at the same time achieving good quality images before and after reconstruction.
 
@@
 Another method \cite {tian2003high} uses difference expansion and generalized LSB embedding.
-Difference expansion works by exploiting the high redundancy that are present in images \cite {tian2002reversible}.
+Difference expansion works by exploiting the high redundancy that is present in images \cite {tian2002reversible}.
 With difference expansion the payload is embedded in the difference of pixel values \cite {tian2002reversible}. 
@@
 This is because if the specific block is already very rough (very busy visually) the human eye does not notice small changes.
-If however the specific block is very smooth (very uniform visually) the human eye is more likely to notice small changes.
+If however the specific block is very smooth (very uniform visually) the human eye is more likely to notice small changes and should be avoided.
 The method thus creates less distortion in the image after embedding than fixed size methods while still retaining good image after reconstruction quality \cite{qian2011image}.
@@
 All three methods thus provide good results and would serve as a good benchmark for comparing the method proposed in this dissertation.
+A summary of the comparison between the 3 methods is given in Table 1
+
+\begin{center}
+  \begin{tabular}{| l | l | l | l |}
+    \hline
+    \multicolumn{4}{|c|}{Table 1: Summary of the comparison between the 3 methods} \\
+    \hline
+    Method & PSNR after embedding & PSNR after reconstruction & Tampering rate \\ \hline
+    Erasure channel& \textgreater35dB & 35dB \textless PSNR\textgreater 40dB & 33\% \\ \hline
+    Difference expansion& \textgreater35dB & Not specified & Not specified \\ \hline
+    Dynamic block allocation& \textgreater37dB & 35dB & \textless 35\% \\ \hline
+    \hline
+  \end{tabular}
+\end{center}
 
@@
 This information will be used to determine the success of the self-recovering image method proposed in this dissertation by comparing the results from the proposed method with the results achieved by the methods discussed in this chapter.
-The next chapter will discuss the implementation of the of the self-recovering image method proposed in this dissertation.
+The next chapter will discuss the implementation of the self-recovering image method proposed in this dissertation.
 

### 2014-10-29 Paper/main.tex
section 5 done

@@
 The self-recovering method proposed in this dissertation uses BPCS steganography to increase the payload capacity of the cover image in order to be able to embed more image reference content into the image without introducing visual distortion.
-In addition a fragile watermark was used to detect which parts of the image is damaged and thus needs to be reconstructed.
+In addition a fragile watermark is used to detect which parts of the image is damaged and thus needs to be reconstructed.
 
@@
 The image reference content is first processed using the method explained later in this section.
-Each block has 12 pixels (with a bit depth of 16 bits) of the image reference content embedded into it.
-An embedding map containing the location of the first pixel to be embedded in the block is also created.
+Each block of the original image, which can store 192 bits, has 12 pixels (with a bit depth of 16 bits, in other words 192 bits) of the image reference content embedded into it.
+An embedding map containing the location of the first pixel to be embedded in the block is also created to keep track of which pixels of the original image contains image reference content.
 Since the individual image reference content pixels are embedded in order it is only necessary to know the location of the first pixel.
-This embedding map is then embedded into the LSB (Least significant bit) layer of that specific 8x8 block of pixels 
+This embedding map is then embedded into the LSB (Least significant bit) layer of that specific 8x8 section of pixels. 
 This allows the extractor to be able to identify where all the extracted pixels belong in the image even if the image has been modified.
-This serves to give random access to the embedded content which is an essential property of self-embedding as defined by Korus et al. \cite{korus2013efficient}.
+This serves to give random access to the embedded content which is an essential property of self-embedding \cite{korus2013efficient}.
 This is essential in order for the reconstruction process to function properly.
@@
 The proposed method rather reduces the bit rate of the image from 24 bits to 16 which reduces the size of each pixel by 6 bits.
+This means that the image size is reduced due to fewer bits being stored for each pixel.
+The quality of the image is reduced using this method by reducing the amount of colours that a pixel can represent.
 The image's size is also reduced according to the space available for embedding.
-When extracting the image reference content again the assembled image reference content is scaled up to it's original size of 512x512 pixels before completing the reconstruction.
+This is accomplished by calculating the amount of bits that can be embedded into in the original image.
+The image is scaled down to the largest possible size that can still be embedded into the original image(determined by the calculated embedding capacity).
+This means that the image reference content quality is at a maximum. 
+When extracting the image reference content again the assembled image reference content is scaled up to it's original size of 512x512 pixels, which is the standard image size for the proposed method, before completing the reconstruction.
+All image scaling was done by converting the image data to a Java image object, using the built in Java image scaling feature and then converting the resulting scaled image back to the required format.
 This is done to ensure that the pixels contained in the image reference content matches up (location wise) with the pixels in the original image.
@@
 It is very important how the image reference content is spread across the image because this affects the tamper rate.
-\cite{korus2013efficient} Has found that it is important that the image reference content should be uniformly distributed across the image during embedding and that each part of the image after should contain equal information about the image reference content.
-Due to the fact that the proposed method uses an adaptive embedding algorithm it is not possible for each part of the image after embedding to contain equal information about the image reference content.
+Researchers \cite{korus2013efficient} have found that it is important that the image reference content should be uniformly distributed across the image during embedding and that each part of the image after should contain equal information about the image reference content.
+Due to the fact that the proposed method uses an adaptive embedding algorithm it is not possible for each part of the image after embedding to contain equal amounts of the image reference content.
 The proposed method does however distribute the embedded image reference content evenly among the blocks that were identified as suitable for embedding.
@@
 \paragraph{Conjugation}
-If an image reference content block is found to not be complex enough that block needs to be conjugated before embedding.
+If an image reference content block is found to not be complex enough then that block needs to be conjugated before embedding.
 This is important because if a block is not complex enough it cannot be detected when extracting and it may cause visual distortions to the image since it is replacing a complex block in the original image.
@@
 A conjugation map is also created to indicate which blocks have been conjugated.
-This is needed since the receiver of the image would not be able to determine if a block has been conjugated or no without such a map.
+This is needed since the receiver of the image would not be able to determine if a block has been conjugated or not without such a map.
 The conjugation map is also embedded into the image.
@@
 \hspace{0pt} \\
-Another problem with this method was the large amount of noise that this method of watermarking introduces into the cover image since it also uses difference expansion as mentioned in \cite{tian2002reversible}.
+Another problem with this method was the large amount of noise that this method of watermarking introduced into the cover image since it also uses difference expansion as mentioned in \cite{tian2002reversible}.
 
@@
 This hash string is then truncated to a length of 57 bits.
+This effectively means that only the first 57 bits of the hash string are used and the rest is simply thrown away.
 This is done to enable the conjugation map as well as the embedding map that was generated when embedding the image content (\ref{bpcsSteg}) to be stored at the end of the stream.
@@
 However since the generated hash values are calculated from the 7 MSB planes of each section and then compared to the bits stored in the LSB plane of that section it is highly unlikely, but not impossible, that a false positive for tampering will occur.
-Extensive testing was conducted on a number of images and no situation was found where such a collision occurred within normal operation.
+Testing was conducted on a number of images and no situation was found where such a collision occurred within normal operation.
 However should this case arise, the proposed method would simply restore that section as well.
@@
 This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
-for each section (section refers here to 8x8 pixel section, thus a section here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
-The embedded hash is then extracted from the LSB plane of that block.
-The extracted hash is then compared with the calculated hash and if they match the section is authentic.
+For each section (section refers here to 8x8 pixel section, thus a section here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 
+The embedded hash is then extracted from the LSB plane of that block and compared to the calculated hash to determine if they match, in which case the section can be seen as tamper-free.
 If they do not match then that section has been tampered with and needs to be reconstructed.
@@
 \label{extractionReconstruction}
-For each authentic block the 7 MSB planes have their complexity calculated.
+The complexity of the 7 MSBs of each authentic block is calculated.
 If a bit plane block is found to be complex enough it is assumed that there is image information embedded into it.

### 2014-10-30 Paper/main.tex
section 6 completed

@@
 The results of that process can be seen in figure \ref{fig:lenaEmbedOnceEmbedding}, showing the original image and the image after the embedding process.
-Note that in this case the Image Reference content was only embedded once
 
@@
 \hspace{0pt} \\
-All images will be evaluated using Peak Signal to Noise Ratio (PSNR) because it is the most widely used measurement for objective image quality and is easily comparable with previous research.
-\cite{wang2002image}
 After the image after embedding was generated the PSNR of the image after embedding in relation to the original image was calculated.
-In this instance the PSNR after embedding was: 34.92dB
+In this instance the PSNR after embedding was: 34.92dB.
+This indicates that the difference in signal between the original image and the image after embedding is almost 35dB.
 
 \hspace{0pt} \\
-The next step in the experiment conducted was to modify the image after embedding (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+The next step in the experiment conducted was to modify the image after embedding.
+\begin{figure}[h]
+	\centerline{%
+	\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage - Copy"}%
+	}%
+	\caption{Image After Tampering}
+	\label{fig:lenaEmbedOnceTampered}
+\end{figure}
 After the image was modified it was reconstructed using the method described in \ref{extractRestore}.
-The results of this reconstruction can be seen in figure \ref{fig:lenaEmbedOnceRestoration}, showing the image after tampering and the image after reconstruction.
+The results of this reconstruction can be seen in figure \ref{fig:lenaEmbedOnceRestoredOriginal}, showing the original image and the image after reconstruction.
 
@@
 \centerline{%
-\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage - Copy"}%
+\includegraphics[scale=0.45]{"lena"}%
 \hspace{0.1cm}
@@
 }%
-\caption{Embedding Once. Left: Image After Tampering, Right: Image After Restoration}
-\label{fig:lenaEmbedOnceRestoration}
+\caption{Left: Original Image, Right: Image After Reconstruction}
+\label{fig:lenaEmbedOnceRestoredOriginal}
 \end{figure}
@@
 \hspace{0pt} \\
-After the image (shown in figure \ref{fig:lenaEmbedOnceRestoration}) was reconstructed the PSNR of the image after reconstruction (figure \ref{fig:lenaEmbedOnceRestoration}) was calculated in relation to the original Image (shown in figure \ref{fig:lenaEmbedOnceEmbedding}).
+After the image was reconstructed the PSNR of the image after reconstruction was calculated in relation to the original image.
 In this instance the PSNR after restoration was: 34.89dB.
@@
 \hspace{0pt} \\
-It was found in the experimentation process that if the image reference content is only embedded once into the original image that the quality of the Image after embedding as well as the quality of the image after reconstruction was relatively high.
+The experimentation process thus shows that if the image reference content is only embedded once into the original image that the quality of the image after embedding as well as the quality of the image after reconstruction is relatively high.
 It was however found that the tamper rate possible was quite low at \textless 3\%.
 To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the image reference content was now being embedded twice.
-The results can be seen in figure \ref{fig:lenaEmbedTwiceEmbedding} and figure \ref{fig:lenaEmbedTwiceRestoration}
+This increases the probability reconstruction will be possible since every piece of image reference content is contained twice in the image after embedding.
+A specific piece of the image reference content must thus be lost in two locations before reconstruction is no longer possible.
+The results can be seen in figure \ref{fig:lenaEmbedTwiceEmbedding}, figure \ref{fig:lenaEmbedTwiceTampered} and figure \ref{fig:lenaEmbedTwiceRestoration}
 
@@
 \includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage - Copy"}%
+}%
+\caption{Embedding Twice. Image After Tampering}
+\label{fig:lenaEmbedTwiceTampered}
+\end{figure}
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.45]{"lena"}%
 \hspace{0.1cm}
@@
 }%
-\caption{Embedding Twice. Left: Image After Tampering, Right: Image After Restoration}
+\caption{Embedding Twice. Left: Original image, Right: Image After Restoration}
 \label{fig:lenaEmbedTwiceRestoration}
@@
 This experiment was also completed on the following image.
-First by embedding the image reference content once (figure \ref{fig:treeEmbedOnceEmbedding} and figure \ref{fig:treeEmbedOnceRestoration}):
+First by embedding the image reference content once (figure \ref{fig:treeEmbedOnceEmbedding}, figure \ref{fig:treeEmbedOnceTamper} and figure \ref{fig:treeEmbedOnceRestore}):
 
@@
 \hspace{0pt} \\
-The PSNR of the image after embedding (show in figure \ref{fig:treeEmbedOnceEmbedding}) was 27.94dB.
+The PSNR of the image after embedding was 27.94dB.
 
@@
 \includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage - Copy"}%
+}%
+\caption{Embedding Once. Image After Tampering}
+\label{fig:treeEmbedOnceTamper}
+\end{figure}
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.3375]{"tree"}%
 \hspace{0.1cm}
@@
 }%
-\caption{Embedding Once. Left: Image After Tampering, Right: Image After Restoration}
-\label{fig:treeEmbedOnceRestoration}
+\caption{Embedding Once. Left: Original image, Right: Image After Restoration}
+\label{fig:treeEmbedOnceRestore}
 \end{figure}
@@
 \hspace{0pt} \\
-The PSNR of the image after reconstruction (show in figure \ref{fig:treeEmbedOnceRestoration}) was 27.72dB.
-The tamper rate, as was the case with the first image (figure \ref{fig:lenaEmbedOnceRestoration}), was also \textless 3\%.
-The experiment was also conducted by embedding the image reference content twice (figure \ref{fig:treeEmbedTwiceEmbedding} and figure \ref{fig:treeEmbedTwiceRestoration}).
+The PSNR of the image after reconstruction was 27.72dB.
+The tamper rate, as was the case with the first image, was also \textless 3\%.
+The experiment was also conducted by embedding the image reference content twice (figure \ref{fig:treeEmbedTwiceEmbedding}, figure \ref{fig:treeEmbedTwiceTamper} and figure \ref{fig:treeEmbedTwiceRestore}).
 
@@
 \hspace{0pt} \\
-The PSNR of the image after embedding (show in figure \ref{fig:treeEmbedTwiceEmbedding}) was 27.93dB.
+The PSNR of the image after embedding was 27.93dB.
 
@@
 \includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage - Copy"}%
+}%
+\caption{Embedding Twice. Image After Tampering}
+\label{fig:treeEmbedTwiceTamper}
+\end{figure}
+
+\begin{figure}[h]
+\centerline{%
+\includegraphics[scale=0.3375]{"tree"}%
 \hspace{0.1cm}
@@
 }%
-\caption{Embedding Twice. Left: Image After Tampering, Right: Image After Restoration}
-\label{fig:treeEmbedTwiceRestoration}
+\caption{Embedding Twice. Left: Original image, Right: Image After Restoration}
+\label{fig:treeEmbedTwiceRestore}
 \end{figure}
@@
 \hspace{0pt} \\
-The PSNR of the image after reconstruction (show in figure \ref{fig:treeEmbedOnceRestoration}) was 26.05dB.
+The PSNR of the image after reconstruction was 26.05dB.
 The tamper rate, as was the case with the first image image (figure \ref{fig:lenaEmbedTwiceRestoration}), was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
@@
     Image & PSNR after embedding & PSNR after restoration & Tampering rate \\ \hline
-    Figure \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedOnceRestoration} (Embed once) & 34.92dB & 34.89dB & \textless 3\% \\ \hline
+    Figure \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedOnceRestoredOriginal} (Embed once) & 34.92dB & 34.89dB & \textless 3\% \\ \hline
     Figure \ref{fig:lenaEmbedTwiceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} (Embed twice) & 34.92dB & 32.52 dB & \textless 35\% \\ \hline
-    Figure \ref{fig:treeEmbedOnceEmbedding} - \ref{fig:treeEmbedOnceRestoration} (Embed once) & 27.94dB & 27.72dB & \textless 3\% \\ \hline
-    Figure \ref{fig:treeEmbedTwiceEmbedding} - \ref{fig:treeEmbedTwiceRestoration} (Embed twice) & 27.93dB & 26.05dB & \textless 35\% \\ \hline
+    Figure \ref{fig:treeEmbedOnceEmbedding} - \ref{fig:treeEmbedOnceRestore} (Embed once) & 27.94dB & 27.72dB & \textless 3\% \\ \hline
+    Figure \ref{fig:treeEmbedTwiceEmbedding} - \ref{fig:treeEmbedTwiceRestore} (Embed twice) & 27.93dB & 26.05dB & \textless 35\% \\ \hline
     \hline
@@
 The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced.
-As an experimental control the results from the experiment in the proposed method will be compared to other current methods for images with self-recovering capabilities.
+This is due to the fact that the embedding algorithm used dynamically determines where to embed the image reference content depending on the original image.
+Areas in the second image like the grass and tree leaves are detected by the embedding algorithm as noisy and suitable for embedding, the second image thus has more space to embed information in without introducing noticeable visual distortion than the first image.
+The PSNR method used to objectively measure the quality of the images gives a lower quality rating due to more of the image being different from the original image even though when observed visually the image does not appear to have undergone such a big change.
+  As an experimental control the results from the experiment in the proposed method is compared to other current methods for images with self-recovering capabilities.
 This is discussed further in  section \ref{interpretation}.
@@
 The proposed method for self-recovering images using the BPCS steganography embedding algorithm described in the preceding sections was shown to be effective.
-According to Appendix B in \cite{korus2013efficient} the proposed method achieved average to high quality reconstruction in the case of figure \ref{fig:lenaEmbedTwiceRestoration} and figure \ref{fig:lenaEmbedOnceRestoration} respectively.
-The proposed method achieved low quality reconstruction in the case of figure \ref{fig:treeEmbedOnceRestoration} and figure \ref{fig:treeEmbedTwiceRestoration} according to \cite{korus2013efficient}.
+According to Appendix B in \cite{korus2013efficient} the proposed method achieved average to high quality reconstruction in the case of figure \ref{fig:lenaEmbedOnceRestoredOriginal}  and figure \ref{fig:lenaEmbedTwiceRestoration} respectively.
+The proposed method achieved low quality reconstruction in the case of figure \ref{fig:treeEmbedOnceRestore} and figure \ref{fig:treeEmbedTwiceRestore} according to \cite{korus2013efficient}.
 
@@
 It should also be mentioned that the proposed method uses no compression on the image reference content, similar to the difference expansion method.
-This method thus serves as a more equal comparison.
+Compression would mean that less noise would be introduced during embedding or that a higher quality reference image could be embedded.
 
 \hspace{0pt} \\
-Research in \cite{wang2002image} Points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
+Research in \cite{wang2002image} points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
 PSNR is a useful measure for objective image quality assessment to a certain degree, however there are other important factors to consider. 

### 2014-10-30 Paper/main.tex
Done with everything

@@
 \subsection{Introduction}
-This chapter summarizes the findings of the proposed method and relates those findings back to the problem statement in section \ref{problemStatement}.
-Possible future work with regards to the proposed method is also discussed.
-
-\subsection{Summary}
-The proposed method described used the BPCS steganaography algorithm, which is an adaptive embedding algorithm described in \ref{bpcsSteg}, and applied the algorithm to the self-recovering image problem.
-The proposed method was shown to provide good quality as well as a good tamper rate.
+The method proposed in this dissertation used the BPCS steganography algorithm, which is an adaptive embedding algorithm, and applied the algorithm to self-recovering images.
+Experimental results showed that the proposed method provided good quality images, measured as PSNR, as well as a good tamper rate.
 It was also shown that the quality of the image after embedding the image reference content as well as the image quality after reconstruction differs depending on the cover image chosen.
@@
 \hspace{0pt} \\
-The proposed method achieved a high quality image after the self-embedding process as well as after the restoration process with reasonable tamper rate in one set of the images tested.
-The quality though is dependent on the image used.
-It would thus not achieve high quality with all images.
 The proposed method did not introduce clear visual evidence that the image has been modified after embedding as well as after restoration and the image did still carry it's original meaning.
@@
 The focus was to combine these methods in order to create a high quality self-recovering image scheme.
-It could however be possible to increase the quality of the proposed method even further if compression is used on the image reference content that is embedded into the original image.
+It could however be possible to increase the quality of the proposed method even further by applying compression on the image reference content that is embedded into the original image.
 By compressing the image reference content it would be possible to embed a higher quality reference image into the original image without increasing the payload size.
-It would also be possible to reduce the amount embedding capacity used, due to a smaller amount of bits that need to be embedded, which would result in less of the original image being changed and thus less noise being introduced into the original image.
+Due to a smaller amount of bits that need to be embedded, it would result in less of the original image being changed and thus less noise being introduced into the original image.
 This could possibly lead to increasing the overall quality of the proposed self-recovering image scheme.

### 2014-11-03 Paper/main.tex
Chapter 1 proof read

@@
 This is due to an inherent trade off between the amount of information that can be embedded into an image and the quality of the image after embedding.
-This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in the self-recovering image problem using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
+This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in self-recovering images using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
 Experimental results show that the proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the currently available self-recovering image methods.
@@
 During communication images can be modified either intentionally or unintentionally.
-These modifications can be small changes that does not change the meaning of the image, or bigger changes, for example the removal of key aspects from the image.
+These modifications can be small changes that do not change the meaning of the image, or bigger changes, for example the removal of key aspects from the image.
 Various techniques exist for authenticating images of which self-recovering is one technique. 
@@
 If the image was tampered with, this embedded approximation can then be used to attempt to recover the original image.
- Self-recovering techniques also use fragile watermarks which is a technology commonly used in image authentication, to determine which areas of an image was tampered with.
+ Self-recovering techniques also use fragile watermarks, which is a technology commonly used in image authentication, to determine which areas of an image was tampered with.
 

### 2014-11-03 Paper/main.tex
Section 2 proof read

@@
 This is due to an inherent trade off between the amount of information that can be embedded into an image and the quality of the image after embedding.
-This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in self-recovering images using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
+This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in self-recovering images using the BPCS steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
 Experimental results show that the proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared to some of the currently available self-recovering image methods.
@@
 The least significant bit of a colour value is the binary bit that carries the least value and thus the change in colour is not perceptible to the human eye.
-LSB embedding is the most common and easiest method for embedding messages in an image \cite{lee2000high}, and many methods exist for detecting the hidden information
+LSB embedding is the most common and easiest method for embedding messages in an image \cite{lee2000high}, and many methods exist for detecting the hidden information.
 
 \hspace{0pt} \\
-Bit plane complexity steganography (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason \cite{kawaguchi1999principles}. 
+Bit plane complexity segmentation (BPCS) is another steganographic embedding method that was developed in 1999 by E. Kawaguchi and R.O. Eason \cite{kawaguchi1999principles}. 
 The goal of the BPCS algorithm is to embed as much data as possible into a cover image while maintaining invisibility \cite{beaullieubpcs}.
@@
 The embedded content can then later be used to recover damaged or modified parts of the image without accessing the original image itself.
-self-embedding is also referred to as self-recovering
+self-embedding is also referred to as self-recovering.
 A self-recovery scheme such as the proposed method contains a couple of high level steps.
@@
 The first step for the image extraction and reconstruction process is to determine which, if any, parts of the image after embedding has been tampered with.
-This is accomplished by first completing steps 1-4 of the BPCS steg algorithm (\ref{bpcsSteg}).
+This is accomplished by first completing steps 1-4 of the BPCS steganography algorithm (\ref{bpcsSteg}).
 For each section (section refers here to 8x8 pixel section, thus a section here contains all 8 bit planes) the authentication hash string is calculated as described in \ref{impFragileWatermark}. 

### 2014-11-04 Paper/main.tex
Chapter 3 proop read

@@
 The method proposed in \cite {korus2013efficient} achieves good quality images after embedding with a PSNR \textgreater 35dB. 
-The method also achieves an image after reconstruction quality of 35dB \textless PSNR \textgreater 40dB and 40dB \textless PSNR with tamper rates of 50\% and 33\% respectively.
+The method also achieves an image after reconstruction quality of 35dB \textless PSNR \textless 40dB and 40dB \textless PSNR with tamper rates of 50\% and 33\% respectively.
 The method does not let the quality of the image after reconstruction deteriorate much if the tampering rate is increased up to a value of 50\%.
@@
     Method & PSNR after embedding & PSNR after reconstruction & Tampering rate \\ \hline
-    Erasure channel& \textgreater35dB & 35dB \textless PSNR\textgreater 40dB & 33\% \\ \hline
+    Erasure channel& \textgreater35dB & 35dB \textless PSNR\textless 40dB & 33\% \\ \hline
     Difference expansion& \textgreater35dB & Not specified & Not specified \\ \hline
@@
 This chapter looked at currently available methods for self-recovering images.
-An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation in \ref{DynamicBlockOverview}.
+An erasure channel model utilizing the remaining authentic content in section \ref{ErasureChannelOverview}, a method using difference expansion in section \ref{differenceExpansionOverview} and a method using dynamic block allocation in section \ref{DynamicBlockOverview}.
 A comparison between these methods was provided in section \ref{litStudyCamparison}.

### 2014-11-04 Paper/main.tex
Chapter 4 proof read

@@
 The SHA-256 hash used is truncated to a 57 bit hash. 
-This means that the hash has y possible unique values 
-\[ y = 57^2 = 3249 \]
+This means that the hash has \textit{y} possible unique values 
+\[ \textit{y} = 57^2 = 3249 \]
 The image has 512x512 pixels that are divided into 8x8 sections.
-This means that there are k amount of unique sections in the image
-\[x = \frac{512}{8} = 64 \]
-\[k = x^2 =64^2 = 4096 \]
-Since k \textgreater y the proposed method is subject to the pigeonhole principle \cite{cook1976short}.
-The pigeonhole principle states that since the input for the hash function (k) is greater than the amount of unique outputs of the hash function (y) there will be duplicate hash values produced.
+This means that there are \textit{k} amount of unique sections in the image
+\[\textit{x} = \frac{512}{8} = 64 \]
+\[\textit{k} = \textit{x}^2 =64^2 = 4096 \]
+Since \textit{k} \textgreater \textit{y} the proposed method is subject to the pigeonhole principle \cite{cook1976short}.
+The pigeonhole principle states that since the input for the hash function (\textit{k}) is greater than the amount of unique outputs of the hash function (\textit{y}) there will be duplicate hash values produced.
 However since the generated hash values are calculated from the 7 MSB planes of each section and then compared to the bits stored in the LSB plane of that section it is highly unlikely, but not impossible, that a false positive for tampering will occur.
@@
 The conjugation map is appended to the truncated hash string to create a binary string of 192 bits.
-These 192 bits are finally embedded into the LSB plane of that specific section of the image after embedding effectively replacing all the bits in that bit plane with the generated bit stream.
+These 192 bits are finally embedded into the LSB plane of that specific section of the image after embedding, effectively replacing all the bits in that bit plane with the generated bit stream.
 

### 2014-11-04 Paper/main.tex
Section 5 proof read

@@
 }%
-\caption{Embedding Once. Left: Original Image, Right: Image After embedding}
+\caption{Left: Original image, Right: Image after embedding}
 \label{fig:lenaEmbedOnceEmbedding}
@@
 \hspace{0pt} \\
-The next step in the experiment conducted was to modify the image after embedding.
+The next step in the experiment conducted was to modify the image after embedding (figure \ref{fig:lenaEmbedOnceTampered}).
 \begin{figure}[h]
@@
 	}%
-	\caption{Image After Tampering}
+	\caption{Image after tampering}
 	\label{fig:lenaEmbedOnceTampered}
 \end{figure}
-After the image was modified it was reconstructed using the method described in \ref{extractRestore}.
+After the image was modified it was reconstructed using the method described in section \ref{extractRestore}.
 The results of this reconstruction can be seen in figure \ref{fig:lenaEmbedOnceRestoredOriginal}, showing the original image and the image after reconstruction.
@@
 }%
-\caption{Left: Original Image, Right: Image After Reconstruction}
+\caption{Left: Original image, Right: Image after reconstruction}
 \label{fig:lenaEmbedOnceRestoredOriginal}
@@
 To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the image reference content was now being embedded twice.
-This increases the probability reconstruction will be possible since every piece of image reference content is contained twice in the image after embedding.
+This increases the probability that reconstruction will be possible since every piece of image reference content is contained twice in the image after embedding.
 A specific piece of the image reference content must thus be lost in two locations before reconstruction is no longer possible.
@@
 }%
-\caption{Embedding Twice. Left: Original Image, Right: Image After embedding}
+\caption{Embedding twice. Left: Original image, Right: Image after embedding}
 \label{fig:lenaEmbedTwiceEmbedding}
@@
 }%
-\caption{Embedding Twice. Image After Tampering}
+\caption{Embedding twice. Image after tampering}
 \label{fig:lenaEmbedTwiceTampered}
@@
 }%
-\caption{Embedding Twice. Left: Original image, Right: Image After Restoration}
+\caption{Embedding twice. Left: Original image, Right: Image after reconstruction}
 \label{fig:lenaEmbedTwiceRestoration}
@@
 }%
-\caption{Embedding Once. Left: Original Image, Right: Image After embedding}
+\caption{Embedding once. Left: Original image, Right: Image after embedding}
 \label{fig:treeEmbedOnceEmbedding}
@@
 }%
-\caption{Embedding Once. Image After Tampering}
+\caption{Embedding once. Image after tampering}
 \label{fig:treeEmbedOnceTamper}
@@
 }%
-\caption{Embedding Once. Left: Original image, Right: Image After Restoration}
+\caption{Embedding once. Left: Original image, Right: Image after reconstruction}
 \label{fig:treeEmbedOnceRestore}
@@
 }%
-\caption{Embedding Twice. Left: Original Image, Right: Image After embedding}
+\caption{Embedding twice. Left: Original image, Right: Image after embedding}
 \label{fig:treeEmbedTwiceEmbedding}
@@
 }%
-\caption{Embedding Twice. Image After Tampering}
+\caption{Embedding twice. Image after tampering}
 \label{fig:treeEmbedTwiceTamper}
@@
 }%
-\caption{Embedding Twice. Left: Original image, Right: Image After Restoration}
+\caption{Embedding twice. Left: Original image, Right: Image after reconstruction}
 \label{fig:treeEmbedTwiceRestore}
@@
     \hline
-    Image & PSNR after embedding & PSNR after restoration & Tampering rate \\ \hline
+    Image & PSNR after embedding & PSNR after restoration & Tamper rate \\ \hline
     Figure \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedOnceRestoredOriginal} (Embed once) & 34.92dB & 34.89dB & \textless 3\% \\ \hline
@@
 This is due to the fact that the embedding algorithm used dynamically determines where to embed the image reference content depending on the original image.
-Areas in the second image like the grass and tree leaves are detected by the embedding algorithm as noisy and suitable for embedding, the second image thus has more space to embed information in without introducing noticeable visual distortion than the first image.
+Areas in the second image like the grass and tree leaves are detected by the embedding algorithm as noisy and suitable for embedding. 
+The second image thus has more space than the first image to embed information in without introducing noticeable visual distortion.
 The PSNR method used to objectively measure the quality of the images gives a lower quality rating due to more of the image being different from the original image even though when observed visually the image does not appear to have undergone such a big change.
@@
 \hspace{0pt} \\
-Research in \cite{wang2002image} points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
+Research in \cite{wang2002image} points out several shortcomings of measuring and comparing image quality using methods such as PSNR. 
 PSNR is a useful measure for objective image quality assessment to a certain degree, however there are other important factors to consider. 
@@
 \hspace{0pt} \\
-The embedding rate and effects of the embedding rate seemed consistent across the different images used.
-The embedding rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the dynamic block allocation method.
+The tamper rate seemed consistent across the different images used.
+The tamper rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the dynamic block allocation method.
 However it was found that if the image reference content is embedded twice into the original image that the tamper rate compares equally to that of dynamic block allocation method.

### 2014-11-05 Paper/main.tex
section 6 proof read
Added title page and plagiarism form
minor changes

--- 2014-11-04 Paper/main.tex
@@
 Each block of the original image, which can store 192 bits, has 12 pixels (with a bit depth of 16 bits, in other words 192 bits) of the image reference content embedded into it.
-An embedding map containing the location of the first pixel to be embedded in the block is also created to keep track of which pixels of the original image contains image reference content.
+An embedding map containing the location of the first pixel to be embedded in the block is also created to keep track of which pixels of the original image contains which pixels of the image reference content.
 Since the individual image reference content pixels are embedded in order it is only necessary to know the location of the first pixel.
@@
 All image scaling was done by converting the image data to a Java image object, using the built in Java image scaling feature and then converting the resulting scaled image back to the required format.
-This is done to ensure that the pixels contained in the image reference content matches up (location wise) with the pixels in the original image.
+This scaling up is done to ensure that the pixels contained in the image reference content matches up (location wise) with the pixels in the original image.
 

### 2014-11-05 Paper/main.tex

--- 2014-11-04 Paper/main.tex
@@
 \begin{document}
+\begin{titlepage}
+	\begin{center}
+		{\Huge \textbf{COS 700 Year Project}}
+		\hspace{0pt} \\
+		\hspace{0pt} \\
+		{\LARGE  \textbf{Hendrik Johannes Kolver}}
+		\hspace{0pt} \\
+		{\Large \textit{\textbf{11058103}}}
+		\hspace{0pt} \\
+		\hspace{0pt} \\
+		{\LARGE  \textbf{Supervisor: Ms Tayana Morkel}}
+	\end{center}
+	\begin{figure}[h]
+		\centerline{%
+		\includegraphics[scale=0.08]{"plag"}%
+		}%
+	\end{figure}
+
+\end{titlepage}
+
 \maketitle
@@
 It was also shown that the quality of the image after embedding the image reference content as well as the image quality after reconstruction differs depending on the cover image chosen.
-This was attributed to the adaptive embedding algorithm used due to the fact that the embedding differs depending on the cover image.
+This was attributed to the adaptive embedding algorithm used due to the fact that the embedding differs depending on the original image.
 It was also mentioned that no compression was used on the image reference content that was embedded into the original image.
